### 2025-04-07 draft.tex
initial commit

\documentclass[a4paper,11pt]{amsart}

\usepackage{/home/thiago/.config/dot-files/latex/globaldef}
\input{/home/thiago/.config/dot-files/latex/definitions.tex}

\bibliography{/home/thiago/Sync/wiki/database/bib-database.bib}

%% Extra packages 
\usepackage{amsaddr}                % Affiliation in the first page
\usepackage{slashed}                % Feynman slash notation
\usepackage{simplewick}             % Wick contractions
\usepackage{fontawesome}
\usepackage{tikz-cd}
\usepackage[textwidth=20mm]{todonotes}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Slavnov products and KP tau functions}

\author{Thiago Araujo}

\address{\noindent 
Instituto de Ciências Exatas, Departamento de Física\\
Universidade Federal Fluminense\\
Rua Des. Ellis Hermydio Figueira, 783, Aterrado\\
27213-145 Volta Redonda, RJ, Brazil
}

\email{\texttt{\href{thiaraujo@id.uff.br}{thiaraujo@id.uff.br}}}

\begin{abstract}
  ...
\end{abstract}

\date{\today}
\keywords{Integrability, Bethe states, Schur, Hall-Littlewood, Toda, KP}
\subjclass[2020]{82B20, 82B23}

\maketitle

\setcounter{tocdepth}{1}
\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Scalar products and determinant formulas}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

One important ingredient in the Algebraic Bethe Ansatz is the scalar
product of Bethe states.  The is many important results on this topic,
see~\cite{Korepin:1993kvr} and references therein. Here we focus on
the scalar product between an on-shell and an off-shell Bethe vectors,
the so called \emph{Slavnov product}.

It is known that scalars products in the algebraic Bethe ansatz 
can be written as determinants. In~\cite{Belliard:2019bfz}, the
authors show the reason behind this fact. Let us start
with a short review of this work.

Let us start with a set of arbitrary complex numbers
\(\bm{u} = \{u_j\}_{j=1}^{n+1}\), and we define \(n+1\) sets
\(\bm{u}_j=\bm{u}\setminus \{u_j\}\) so that we can define
\(n+1\) off-shell Bethe vectors \(\ket{\Psi(\bm{u}_j)}\).

Consider now a set of Bethe roots \(\bm{v} = \{ v_k \}_{k=1}^n\),
so that we have the on-shell Bethe vectors \(\ket{\Psi(\bm{v})}\). 
In fact, let us consider the action of the transfer matrix \(\mathcal{T}(z)\)
on the dual Bethe vector, that is 
\begin{equation}
\label{eq:eigenvalue-bethe}
\bra{\Psi(\bm{v})}\mathcal{T}(z) = \Lambda(z; \bm{v}) \bra{\Psi(\bm{v})} \; , 
\end{equation}
where \(\Lambda(z; \bm{v}) \) is the eigenvalue of the transfer matrix.

From these definitions, we now introduce \(n+1\) Slavnov products 
\begin{equation}
  \bm{\zeta}_j = \bracket{\Psi(\bm{v})}{\Psi(\bm{u}_j)}\qquad j =1, \dots, n+1\; .
\end{equation}
We want to show that \(\bm{\zeta}_j\) satisfy a system of linear equations.

In order to see this, we calculate
\begin{equation}
  \bra{\Psi(\bm{v})} {\color{violet}\left(\mathcal{T}(u_j)\ket{\Psi(\bm{u}_j)} \right)} =
  {\color{violet}\left(\bra{\Psi(\bm{v})}\mathcal{T}(u_j)\right)}\ket{\Psi(\bm{u}_j)} 
  \qquad j =1, \dots, n+1\; .
\end{equation}
The right-hand side of this equation can be simplified with the eigenvalue
expression~(\ref{eq:eigenvalue-bethe}), that is
\begin{equation}
  {\color{violet}\left(\bra{\Psi(\bm{v})}\mathcal{T}(u_j)\right)}\ket{\Psi(\bm{u}_j)}  =
\Lambda(u_j; \bm{v}) \bracket{\Psi(\bm{v})}{\Psi(\bm{u}_j)} = 
\Lambda(u_j; \bm{v}) \bm{\zeta}_j\; . 
\end{equation}

In order to simmplify the left-hand side, we expand the action of the transfer matrix on
the off-shell as
\todo{\tiny This point seems to be the most delicate. It does not work for
  elliptic cases}
\begin{equation}
  \mathcal{T}(u_j)\ket{\Psi(\bm{u}_j)}  = \sum_{k=1}^{n+1} L_{jk} \ket{\Psi(\bm{u}_k)} \; ,
\end{equation}
where \(L_{jk}\) are numerical coefficients. Observe that the terms \(L_{jk}\) with
\(j\neq k\) contain the unwanted terms. In the particular case where the algebraic
Bethe equations are satisfied, these unwanted terms vanish and only the diagonal
coefficient survives, that is \(L_{jj}\), and it is equal to the eigenvalue of the
tranfer matrix.

Therefore, we have
\begin{equation}
  \bra{\Psi(\bm{v})} {\color{violet}\left(\mathcal{T}(u_j)\ket{\Psi(\bm{u}_j)} \right)} =
  \sum_{k=1}^{n+1} L_{jk} \bm{\zeta}_k \; .
\end{equation}

Puttting all these facts together, we get
\begin{equation}
  \sum_{k=1}^{n+1} L_{jk} \bm{\zeta}_k  = 
  \Lambda(u_j; \bar{v}) \bm{\zeta}_j\quad \Rightarrow \quad
  \sum_{k=1}^{n+1} M_{jk} \bm{\zeta}_k = 0 \; ,
\end{equation}
where
\begin{equation}
  M_{jk} = L_{jk} - \delta_{jk}\Lambda(u_j; \bm{v})\; . 
\end{equation}
Here is the system we were looking for. We can write this system in
a matrix form as 
\begin{equation}
  \left(\bm{L} - \bm{\Lambda} \right) \cdot \bm{\zeta} = \bm{0}\; ,
\end{equation}
where
\begin{subequations}
  \begin{equation}
    \bm{L} = 
 \begin{pmatrix}
   L_{1,1} & \cdots & L_{1,n+1}\\
   L_{2,1} & \cdots & L_{2,n+1}\\
   \vdots & \vdots & \vdots\\
   L_{n+1, 1} & \cdots & L_{n+1, n+1}\\
 \end{pmatrix}  \quad , \quad
    \bm{\Lambda} = \mathrm{diag}(\Lambda_1, \Lambda_2, \dots, \Lambda_{n+1})
\end{equation}
where we have written \( \Lambda_j \equiv \Lambda(u_j; \bm{v})\), and also
\begin{equation}
  \bm{\zeta} = (\bm{\zeta}_1, \dots , \bm{\zeta}_{n+1})^T\qquad \, 
  \bm{0} = (0, \dots , 0)^T\; .
\end{equation}
\end{subequations}

The whole point now is that if this system has a solution,
it will be written as minors of the matrix \(M\).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Rational models}

We will now consider some concrete models. In the original
work~\cite{Belliard:2019bfz}, the authors consider solutions with a
rational R-mnatrix with periodic boundary conditions. Here we want to
review the main results of this work. 
\todo{\tiny Extend these results to the trigonometric case}

We start with an R-matrix of the form
\begin{equation}
  R(u,v) = \mathbb{1} + g(u,v) \mathcal{P}\; , \qquad
  g(u,v) = \frac{c}{u - v}
\end{equation}
where \(c\) is a constant. Moreover \(\mathbb{1}\) is the identity operator and
\(\mathcal{P}\) is the permutation operator.

In the models with rational R-matrix, the eigenvalues of the transfer matrix
have the form 
\begin{equation}
  \Lambda(z, \bm{v}) = g(z, \bm{v}) \mathcal{Y}(z; \bm{v})\; ,
\end{equation}
where the function \(\mathcal{Y}(z; \bm{v})\) is symmetric over the
Bethe roots \(\bm{v}\), and linearly depends on every
\(v_j\). Generically, it is written as
\begin{equation}
  \mathcal{Y}(z; \bm{v}) = \sum_{p=0}^n \alpha_p(z) \sigma_p^{(n)}(\bm{v})\; , 
\end{equation}
where \(\sigma_p^{(n)}(\bm{v})\) are elementary symmetric polynomials
in \(\bm{v}\) and where \(\alpha_p(z)\) are free functional
parameters. In fact, in the XXX discussed in~\cite{Belliard:2019bfz},
these functions all \(\alpha_p(z)\) are polynomials of degree \(2n\). 
The important point for us is that \(\alpha_p(z)\) is not
singular when we consider the limit \(z \to v_j \in \bm{v}\),
so does the function \(\mathcal{Y}(z; \bm{v})\).

Furthermore, we have
\begin{equation}
  g(z, \bm{v}) = \prod_{v_i\in \bm{v}} g(z; v_i)\; , 
\end{equation}
and that means that each Bethe root \( v_i \in \bm{v}\) of this expression
is a pole of \(g(z;\bm{v})\). Therefore, if \(\gamma_j\) is a contour
containing the point \(v_j\), we have 
\begin{equation}
  \frac{1}{2 \pi i}\oint_{\gamma_j} \mathrm{d}z g(z; \bm{v}) = \prod_{v_i \in \bm{v}\setminus \{u_j\}} g(z, v_i)\; .
\end{equation}

The coefficients \(L_{jk}\) are given by \todo{\tiny Check references
  1, 2 of the paper to see the trigonometric case.}
\begin{equation}
  L_{jk} = g(u_k, \bm{u}_k) \mathcal{Y}(u_k; \bm{u}_j)
\end{equation}
and from this expression one can calculate the matrix \(\bm{M}\).
Finally, the authors also show that if \(\det (\bm{M}) = 0 \) and
\(\mathrm{rank}(\bm{M}) = n\), then, the Slavnov products are given by
\begin{equation}
 \bm{\zeta}_\ell = \phi(\bm{v}) \tilde{\Delta}(\bm{u}_\ell)\hat{\Omega}_\ell\; ,
\end{equation}
where \(\phi(\bm{v})\) is a function of the Bethe roots, and also
\begin{equation}
  \tilde{\Delta}(\bm{u}_\ell) = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{c}{u_j - u_k}\; . 
\end{equation}
Therefore, we can absorb the product of the constant \(c\) into
a unique constant \(c_0\) so that 
\begin{equation}
  \frac{\tilde{\Delta}(\bm{u}_\ell)}{c_0} = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{1}{u_j - u_k}\; , 
\end{equation}
that is the inverse of the Vandermonde determinant
\(\Delta(\bm{u}_\ell)\).
Finally, we have  that \(\hat{\Omega}_\ell\) are minors of the matrix \(\bm{\Omega}\) with the \(\ell\)-th
column excluded, that is 
\begin{equation}
 \hat{\Omega}_\ell = \det_{k\neq \ell} \Omega_{jk}\; ,
\end{equation}
where
\begin{equation}
  \Omega_{jk} = g(u_k, v_j) \mathcal{Y}(u_k; \{u_k, \bm{v}_j\})
  \qquad j= 1, \dots, n\; , \quad k =1, \dots, n+1
\end{equation}

All in all, we have an expression of the
form
\begin{equation}
  \bm{\tau}_\ell(\bm{u}_\ell; \bm{v}) \equiv \frac{1}{c_0}\frac{\bm{\zeta}_\ell}{\phi(\bm{v})}
  = \frac{\det_{k\neq \ell} \Omega_{jk}}{\Delta(\bm{u}_\ell)}
\end{equation}

Let us now simplify these thing a little bit. First of all, we need to
observe that we can define \(n\) functions \(\Omega_j(z)\) of the form 
\begin{equation}
\begin{split}
  \Omega_{j}(z; \bm{v}) & = g(z, v_j) \mathcal{Y}(z; \{z, \bm{v}_j\})\qquad j =1, \dots, n\\
   & = \frac{c}{z - v_j} \mathcal{Y}(z; \{z, \bm{v}_j\})\; .
\end{split}
\end{equation}
Moreover, we have the expansion 
\begin{equation}
  \mathcal{Y}(z; \{z,\bm{v}_j\}) = \sum_{p=0}^n \alpha_p(z) \sigma_p^{(n)}(\{z,\bm{v}_j\})\; , 
\end{equation}
and using that the elementary symmetric polynomials decompose as
\begin{equation}
  \sigma_p^{(n)}(\{z,\bm{v}_j\}) = \sigma_p^{(n-1)}(\bm{v}_j) + z \sigma_{p-1}^{(n-1)}(\bm{v}_j) \; , 
\end{equation}
Therefore,
\begin{equation}
  \label{eq:y-functions-alpha}
  \mathcal{Y}_j(z)  = 
\sum_{p=0}^{n} \alpha_p(z)
  \left(\sigma_p^{(n-1)}(\bm{v}_j) + z \sigma_{p-1}^{(n-1)}(\bm{v}_j) \right) 
\end{equation}
where we have denoted \( \mathcal{Y}(z; \{z,\bm{v}_j\}) \equiv \mathcal{Y}_j(z)\). 
Observe that what defines the functions \(\mathcal{Y}_j(z)\) is the absence of the
\(j\)-th Bethe root \(v_j\).

Using that the elementary symmetric polynomials also satisfy \(\sigma_n^{(n-1)}(\bm{v}_j)=0\)
and \(\sigma_{-1}^{(n)}(\bm{v}_j)= 0\), we can write
\begin{equation}
  \label{eq:y-functions}
  \mathcal{Y}_j(z)  = 
  \sum_{p=0}^{n-1} 
   \left(\alpha_p(z) + z \alpha_{p+1}(z) \right) \sigma_p^{(n-1)}(\bm{v}_j) 
\end{equation}

Let us write the \(p\) functions \(\sigma_p\) in terms of a linearly
\todo{Not sure if I need this!!!}
independent basis \(\{\phi_j\}_{j=1}^n\). In this case, we have that the functions
\(\mathcal{Y}_j(z)\) are also linearly independent and have the expansion
\begin{equation}
  \mathcal{Y}_j(z) = \sum_{k=1}^n \rho_k(\bm{v}_j) \phi_k(z)\; ,
\end{equation}
where the coefficients \( \rho_k(\bm{v}_j)\) depend on the Bethe roots \(\bm{v}_j\). 
The functional structure of the coefficients \(\rho_k\), when written, in terms of the
Bethe roots are the same.

For example, in the case of the XXX model, \(\alpha_p(z)\sim z^{2n} + \cdots\), so
that one can take \(\phi_j \sim z^{2j} + \cdots\), and the coefficients depend on the
Bethe roots and inhomogeneities.

We finally have 
\begin{equation}
  \Omega_{j}(z; \bm{v}) = -\frac{c}{v_j - z} \mathcal{Y}_j(z) \; .
\end{equation}
where we have denoted \( \mathcal{Y}(z; \{z,\bm{v}_j\}) \equiv \mathcal{Y}_j(z)\).
It is also convenient to consider \(c=1\).

%Finally, let us now consider this function in the neighborhood of the Bether root \(v_j\). We find 
%\begin{equation}
%  \Omega_j(z; \bm{v}) \simeq \frac{c}{z - v_j}
%\mathcal{Y}(v_j; \bm{v})\qquad j =1, \dots, n\; .
%\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Tau functions}

Therefore, we can write the matrix \(\bm{\Omega}\) as 
\begin{equation}
  \bm{\Omega} =
  \begin{pmatrix}
    \Omega_1(u_1) & \dots & \Omega_1(u_n) & \Omega_1(u_{n+1}) \\
    \Omega_2(u_1) & \dots & \Omega_2(u_n) & \Omega_2(u_{n+1}) \\
    \vdots & \vdots & \vdots & \vdots \\
    \Omega_n(u_1) & \dots & \Omega_n(u_n) & \Omega_n(u_{n+1})
  \end{pmatrix}
\end{equation}
and we also define the \(n\times n\) matrices \(\bm\Omega^{(\ell)}(\bm{u}_\ell; \bm{v})\),
\(\ell = 1, \dots, n+1\), removing the \(\ell\)-th column of
\(\bm{\Omega}\), that is
\begin{equation}
  \bm{\Omega}^{(\ell)} =
  \begin{pmatrix}
    \Omega_1(u_1) & \dots & \Omega_1(u_{\ell-1}) & \Omega_1(u_{\ell+1})&\dots & \Omega_1(u_{n+1}) \\
    \vdots & \dots & \vdots & \vdots & \dots & \vdots \\
    \Omega_n(u_1) & \dots & \Omega_n(u_{\ell-1}) & \Omega_n(u_{\ell+1})&\dots & \Omega_n(u_{n+1})\; .
  \end{pmatrix}
\end{equation}

Putting these facts together, we write the functions
\begin{equation}
\label{eq:slavnov-tau-functions}
  \bm{\tau}_\ell(\bm{u}_\ell; \bm{v}) = \frac{\det [\Omega_j((\bm{u}_\ell)_k)]|_{j,k=1}^n }{\Delta(\bm{u}_\ell)} 
\end{equation}
where \((\bm{u}_\ell)_k \) is the k-th component of the vector
\(\bm{u}_\ell\). These functions are tau functions of the KP
hierarchy.  We have also omitted the dependence on the Bethe roots
\(\bm{v}\). The most important aspect now is that the poles of this
tau function are exactly the Bethe roots of the integrable model.

It is well documented that the functions defined as
in~(\ref{eq:slavnov-tau-functions}) are tau functions of the
KP-hierachy, see~\cite{Araujo:2021ghu} and references therein, in
particular~\cite{Kharchev:1991cy}.

In fact, we can focus all our attention on a particular function. Therefore,
for a fixed \(\ell\), we define the vector \( \bm{z} \equiv \bm{u}_\ell\).
Consequently, 
\begin{equation}
\begin{split}
  \bm{\tau}(\bm{z}, \bm{v})
  & = \frac{1}{\Delta(\bm{z})} \det[\Omega_j(z_k) ]_{j,k=1}^n \\
  & = \frac{1}{\Delta(\bm{z})} \det\left[\frac{\mathcal{Y}_j(z_k)}{z_k - v_j} \right]_{j,k=1}^n  \\
\end{split}
\end{equation}
All these tau functions have the form of an
\emph{alternant determinant} \footnote{see definition~(\ref{def:alt-determinant})
in the appendix~\ref{app:mathematical}.}

\subsection{Pole structure}

We now want to analyse the pole structure of
\(\Delta(\bm{z})\tau(\bm{z}, \bm{v})\).  First of all, one should
observe that the Bethe roots \(\bm{v}\) appear as poles of the
coefficients \(\bm{z}\). Moreover, lets us consideer here that the
Bethe roots are not degenerate, that is, if \(j \neq k\), then \(v_j
\neq v_k\). In that case, the poles \(v_j\) are simple poles.

Let us now consider a particular coefficient \(\bm{z}\), say \(z_l\), and
make a Laplace expansion in the column \(l\), that is
\begin{equation}
\begin{split}
  \bm{\tau}(\bm{z}, \bm{v})
  & = \frac{1}{\Delta(\bm{z})} \det[\bm{\Omega}(\bm{z}) ] \\
  & = \frac{1}{\Delta(\bm{z})} \sum_{j=1}^n (-1)^{j + l} \frac{\mathcal{Y}_j(z_l)}{z_l - v_j  } 
  \det[\hat{\Omega}_{j, l}]\; ,
\end{split}
\end{equation}
where \(\hat{\Omega}_{j,l} \) is the \((j, l)\) minor of \(\bm{\Omega}\).

Now, we can extract the residue of the tau function for \(z_l\) at the point \(v_j\), that is
\begin{equation}
  \Res_{(z_l, v_j)}(\Delta(\bm{z})\tau(\bm{z}, \bm{v})) = (-1)^{j+l} \mathcal{Y}_j(v_j) \det[\hat{\Omega}_{j, l}]
\end{equation}

Let us now decompose the Vandermonde determinant as
\begin{equation}
  \Delta(\bm{z}) = \prod_{j>k}(z_j - z_k) = \Delta(\bm{z}_l) \prod_{r<l}(z_l - z_r) \prod_{s>l}(z_s - z_l)\; ,
\end{equation}
where \(\bm{z}_l = \bm{z}\setminus \{z_l\} = (z_1, \dots, z_{l-1}, z_{l+1}, \dots, z_n) \).
\todo[inline]{I wand to verify that this is correct}
We can define the function
\begin{equation}
  \Xi_l(z_l,\bm{z}_l) = \prod_{r<l}(z_l - z_r) \prod_{r>l}(z_r - z_l)\; , 
\end{equation}
then 
\begin{equation}
  \Delta(\bm{z}) = \Xi_l(z_l, \bm{z}_l) \Delta(\bm{z}_l) \; .
\end{equation}

Let us now write
\begin{equation}
  \bm{\tau}(\bm{z}, \bm{v})
   = \frac{1}{\Xi_l(z_l, \bm{z}_l)} \sum_{j=1}^n (-1)^{j + l} \frac{\mathcal{Y}_j(z_l)}{z_l - v_j} 
\left(\frac{1}{\Delta(\bm{z}_l)} \det[\hat{\Omega}_{j, l}]\right)\; .
\end{equation}

When we define the set of functions
\begin{equation}
  \begin{split}
  \hat{\bm{\Omega}}_{(j)}(z) & = \left(\Omega_1(z), \dots, \Omega_{j-1}(z), \Omega_{j+1}(z), \dots, \Omega_n(z) \right)\; ,
  \end{split}
\end{equation}
we can simplify the tau function expansion even further. Then
\begin{equation}
\begin{split}
  \bm{\tau}(\bm{z}, \bm{v})
  & = \frac{1}{\Xi_l(z_l, \bm{z}_l)} \sum_{j=1}^n (-1)^{j + l} \frac{\mathcal{Y}_j(z_l)}{z_l - v_j} 
    \left(\frac{1}{\Delta(\bm{z}_l)} \det[\hat{\bm{\Omega}}_{(j) r}(\bm{z}_{(l) s} ]_{r, s=1}^n\right)\\ 
  & = \frac{1}{\Xi_l(z_l, \bm{z}_l)} \sum_{j=1}^n (-1)^{j + l} \frac{\mathcal{Y}_j(z_l)}{z_l - v_j} 
    \tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v})\; ,
\end{split}
\end{equation}
where 
\begin{equation}
  \label{eq:basis-tau}
    \tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v}) = 
\frac{1}{\Delta(\bm{z}_l)} \det[\hat{\bm{\Omega}}_{(j)}(\bm{z}_{(l)} ]\; .
\end{equation}
The curious aspect of this expression is that it easy to see that each term  
\(\tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v})\) is a tau function itself, and that
it acts as a basis for the Slavnov's product. 
Additionally, these basis tau functions \(\tilde{\tau}_j(\bm{z}_l,
\bm{v})\) are, by construction, completely independent of \(z_l\).

Finally, we have
\begin{equation}
  \Res_{(z_l, v_j)}(\tau(\bm{z}, \bm{v}))
  = \frac{(-1)^{j + l} \mathcal{Y}_j(v_j)}{\Xi_l(v_j, \bm{z}_l)}
  \tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v})
\end{equation}

In order to avoid cluttering, let us order the parameters \(\bm{z}\) and
consider these points close to the corresponding \(\bm{v}\), that is,
we consider just the residues \(z_j \to v_j\), then
\begin{subequations}
\begin{equation}
  \Res_{(z_j, v_j)}(\tau(\bm{z}, \bm{v}))
  = \frac{\mathcal{Y}_j(v_j)}{\Xi_j(v_j, \bm{z}_j)}
  \tilde{\bm{\tau}}_j(\bm{z}_j, \bm{v})
\end{equation}
or yet 
\begin{equation}
  \tilde{\bm{\tau}}_j(\bm{z}_j, \bm{v})
  = \frac{\Xi_j(v_j, \bm{z}_j)}{\mathcal{Y}_j(v_j)}
  \Res_{(z_j, v_j)}(\tau(\bm{z}, \bm{v}))
\end{equation}
\end{subequations}
Evidently, one can repeat the same ideas and take \(z_k \in \bm{z}_j\)
close to \(v_k \in \bm{v}_j\).

\subsection{Examples} Let us now consider the cases \(n=2, 3\) (the case \(n=1\) is trivial)
to gain some understanding of the problem.

\subsubsection{n=2} In this case, we have \(\mathcal{Y}_j\) for \(j=1,2\) and two Bethe roots
\(\bm{v} = (v_1, v_2)\). Moreover, we have the two sets \(\bm{v}_1 =
\{v_2\}\) and \(\bm{v}_2 = \{v_1\}\). From (\ref{eq:y-functions}), we have
\begin{subequations}
\begin{equation}
  \begin{split}
    \mathcal{Y}_j(z) =
    \alpha_0(z) \sigma_0^{(1)}(\bm{v}_j) +  
    \alpha_1(z)( \sigma_1^{(1)}(\bm{v}_j) + z \sigma_0^{(1)}(\bm{v}_j)) +
    \alpha_2(z) z \sigma_1^{(1)}(\bm{v}_j) \; , 
  \end{split}
\end{equation}
finally, the explicit formulas for the elementary symmetric polynomials are \(\sigma_0^{(1)}(x) =1\)
and \(\sigma_1^{(1)}(x) = x\).

Therefore
\begin{equation}
  \begin{split}
    \mathcal{Y}_1(z) & = \alpha_0(z) + z \alpha_1(z)  + v_2 \left( \alpha_1(z) + z \alpha_2(z) \right) \\ 
    \mathcal{Y}_2(z) & = \alpha_0(z) + z \alpha_1(z)  + v_1 \left( \alpha_1(z) + z \alpha_2(z) \right) ; .
  \end{split}
\end{equation}
Thefore, we find
\begin{equation}
  \bm{\tau}(z_1, z_2; v_1 , v_2) = \frac{1}{z_2 - z_1}
  \left(\frac{\mathcal{Y}_1(z_1) \mathcal{Y}_2(z_2)}{(z_1 - v_1)(z_2 - v_2)} - 
  \frac{\mathcal{Y}_1(z_2) \mathcal{Y}_2(z_1)}{(z_1 - v_2)(z_2 - v_1)} 
  \right)
\end{equation}
\end{subequations}
One interesting case happens for \(z_2 \to z_1\equiv w\), in this case
it is easy to show that
\begin{equation}
  \bm{\tau}(w; v_1 , v_2) =
  \frac{1}{(w- v_1)(w- v_2)}\mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2](w)\; , 
\end{equation}
where \(\mathcal{W}[\mathcal{Y}_1, \dots, \mathcal{Y}_n](w)\) denotes the
Wronskian of the functions \(\{\mathcal{Y}_j(w)\}_{j=1}^n\), in our
case, we have \(n=2\). In this case, one can observe that these
functions are linearly independent as long as \(v_2 \neq v_1\), what
is guaranteed by the hypothesis that the Bethe roots are different.

\subsubsection{n=3} Now we have \(\mathcal{Y}_j\) for \(j=1,2,3\) and three Bethe roots
\(\bm{v} = (v_1, v_2, v_3)\). Moreover, we have the sets \(\bm{v}_1 = (v_2, v_3)\), \(\bm{v}_2 = (v_1, v_3)\)
and \(\bm{v}_3 = (v_1, v_2)\). Then, it is easy to see that
\begin{equation}
\begin{split}
  \mathcal{Y}_j(z)
  & = (\alpha_0(z) + z \alpha_1(z))\sigma_0^{(2)}(\bm{v}_j)   + (\alpha_1(z) + z \alpha_2(z))\sigma_1^{(2)}(\bm{v}_j)  + \\
  & \quad + (\alpha_2(z) + z \alpha_3(z))\sigma_2^{(2)}(\bm{v}_j) 
\end{split}
\end{equation}
Moreover, one can also use the explicit expressions 
\begin{equation}
  \sigma_0^{(2)}(x, y) = 1\; ,\qquad 
  \sigma_1^{(2)}(x, y) = x + y\; ,\qquad 
  \sigma_2^{(2)}(x, y) = x^2 + xy  + y^2\; , 
\end{equation}
to determine the functions \(\mathcal{Y}_j(z)\) for \(j=1,2,3\).

Then, we have
\begin{subequations}
\begin{equation}
  \begin{split}
    \bm{\tau} & (z_1, z_2, z_3 ; v_1 , v_2, v_3)  =
    \frac{1}{(z_2 - z_1)(z_3 - z_1)(z_3 - z_2)}\times \\
    & \times \left[
      \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
        \end{bmatrix}
        -  
      \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2}
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
        \end{bmatrix} \right.\\
        & \qquad + \left.
      \frac{\mathcal{Y}_3(z_1)}{z_1 - v_2}
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}
        \end{bmatrix} 
  \right]
  \end{split}
\end{equation}
That we can organize as
\begin{equation}
  \begin{split}
    \bm{\tau} (z_1, z_2, z_3 ; v_1 , v_2, v_3)  & =
    \frac{1}{(z_2 - z_1)(z_3 - z_1)}
    \left[
      \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}
      \left(
      \frac{1}{(z_3 - z_2)}
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
        \end{bmatrix}
        \right) - \right. \\
        & - 
      \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2}
      \left(
      \frac{1}{(z_3 - z_2)}
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
        \end{bmatrix} \right) \\
        & +
        \left.
      \frac{\mathcal{Y}_3(z_1)}{z_1 - v_2}
      \left(
      \frac{1}{(z_3 - z_2)}
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}
        \end{bmatrix} 
        \right)
  \right]\; .
  \end{split}
\end{equation}
\end{subequations}

Finally, we conclude that
\begin{subequations}
  \begin{equation}
	\tilde{\bm{\tau}}_1(\bm{z}_1) = \frac{1}{(z_3 - z_2)} 
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
        \end{bmatrix} 
  \end{equation}
  \begin{equation}
	\tilde{\bm{\tau}}_2(\bm{z}_1) = \frac{1}{(z_3 - z_2)} 
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_3(z_2)}{(z_2 - v_3)} & \frac{\mathcal{Y}_3(z_3)}{(z_3 - v_3)}
       \end{bmatrix}
  \end{equation}
  \begin{equation}
	\tilde{\bm{\tau}}_3(\bm{z}_1) = \frac{1}{(z_3 - z_2)} 
        \det\begin{bmatrix}
        \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)} & \frac{\mathcal{Y}_1(z_3)}{(z_3 - v_1)}\\
        \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}
        \end{bmatrix} 
  \end{equation}
\end{subequations}

With these expressions, we can consider the case where \(z_1, z_2 z_3
\to w\). Consider first the case \(z_3 \to z_2 = w\), then  
we know that 
\begin{equation}
  \begin{split}
  \tilde{\bm{\tau}}_1(w; v_1 , v_2, v_3) & = \frac{1}{(w - v_2)(w - v_3)}\mathcal{W}[\mathcal{Y}_2, \mathcal{Y}_3](w)\\
  \tilde{\bm{\tau}}_2(w; v_1 , v_2, v_3) & = \frac{1}{(w - v_2)(w - v_3)}\mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_3](w)\\
  \tilde{\bm{\tau}}_3(w; v_1 , v_2, v_3) & = \frac{1}{(w - v_1)(w - v_2)}\mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2](w)
  \end{split}\; .
\end{equation}
and now, it is easy to see that if we also take the limit \(z_1\to w\), we have
\begin{equation}
  \bm{\tau}(w; v_1 , v_2, v_3)
  \frac{1}{(w - v_1)(w - v_2)(w - v_3)} \mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2, \mathcal{Y}_3](w)\; .
\end{equation}

\subsubsection{Homogeneous limit and Wronskian formula}

We now want to consider the limit where \(z_k\to z_1\), \(k=2,\dots, n\). 
Let us first consider the case \(z_2 \to z_1\), then
\begin{subequations}
\begin{equation}
  \bm{\tau}(\bm{z}, \bm{v}) = \frac{1}{\Delta(\bm{z})}
  \det
  \begin{pmatrix}
    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}  & \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1} + (z_2 - z_1) \frac{\mathcal{Y}_1^{(1)}(z_1)}{z_1 - v_1}
    + \mathcal{O}(\delta^2) &
    \frac{\mathcal{Y}_1(z_3)}{z_3 - v_1} & \dots & \frac{\mathcal{Y}_1(z_n)}{z_n - v_1}\\
    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} & \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} + (z_2 - z_1) \frac{\mathcal{Y}_2^{(1)}(z_1)}{z_1 - v_2} 
    + \mathcal{O}(\delta^2) &
    \frac{\mathcal{Y}_2(z_3)}{z_3 - v_2} &  \dots & \frac{\mathcal{Y}_2(z_n)}{z_n - v_2}\\
    &  \vdots & & \\
    \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} & \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} + (z_2 - z_1) \frac{\mathcal{Y}_n^{(1)}(z_1)}{z_1 - v_n} 
    + \mathcal{O}(\delta^2) &
    \frac{\mathcal{Y}_n(z_3)}{z_3 - v_n} &  \dots & \frac{\mathcal{Y}_n(z_n)}{z_n - v_n}
  \end{pmatrix}
\end{equation}
where we have written \(z_2 - z_1 = \delta \to 0\). Moreover, we write
\(\mathcal{Y}^{(n)}(z)\) as the nth derivative with respect its
argument. Now one can immediatelly see that the second column is the
first column plus terms multiplied by the factor \(\delta = z_2 -
z_1\). Using elementary operations on the column, we find
\begin{equation}
  \bm{\tau}_h(\bm{z}, \bm{v}) = \lim_{z_2 \to z_1}\frac{(z_2 - z_1)}{\Delta(\bm{z})}
  \det
  \begin{pmatrix}
    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}  & \frac{\mathcal{Y}_1^{(1)}(z_1)}{z_1 - v_1} &
    \frac{\mathcal{Y}_1(z_3)}{z_3 - v_1} & \dots & \frac{\mathcal{Y}_1(z_n)}{z_n - v_1}\\
    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} & \frac{\mathcal{Y}_2^{(1)}(z_1)}{z_1 - v_2} &
    \frac{\mathcal{Y}_2(z_3)}{z_3 - v_2} &  \dots & \frac{\mathcal{Y}_2(z_n)}{z_n - v_2}\\
    &  \vdots & & \\
    \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} & \frac{\mathcal{Y}_n^{(1)}(z_1)}{z_1 - v_n} &
    \frac{\mathcal{Y}_n(z_3)}{z_3 - v_n} &  \dots & \frac{\mathcal{Y}_n(z_n)}{z_n - v_n}
  \end{pmatrix}\; .
\end{equation}
We can now repeat the same ideas for \(z_3\to z_1=z_2\). We find that
the third column is the first plus the second and the derivatives
multiplied by the factor \(\delta^2\sim (z_3 - z_2)(z_3 - z_1)\). All in all, we have
\begin{equation}
  \bm{\tau}_h(\bm{z}, \bm{v}) = \lim_{z_2, z_3 \to z_1}\frac{(z_2 - z_1)(z_3 - z_1)(z_3 - z_2)}{\Delta(\bm{z})}
  \det
  \begin{pmatrix}
    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}  & \frac{\mathcal{Y}_1^{(1)}(z_1)}{z_1 - v_1} &
    \frac{\mathcal{Y}^{(2)}_1(z_1)}{z_1 - v_1} & \dots & \frac{\mathcal{Y}_1(z_n)}{z_n - v_1}\\
    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} & \frac{\mathcal{Y}_2^{(1)}(z_1)}{z_1 - v_2} &
    \frac{\mathcal{Y}_2^{(2)}(z_1)}{z_1 - v_2} &  \dots & \frac{\mathcal{Y}_2(z_n)}{z_n - v_2}\\
    &  \vdots & & \\
    \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} & \frac{\mathcal{Y}_n^{(1)}(z_1)}{z_1 - v_n} &
    \frac{\mathcal{Y}_n^{(2)}(z_1)}{z_1 - v_n} &  \dots & \frac{\mathcal{Y}_n(z_n)}{z_n - v_n}
  \end{pmatrix}\; .
\end{equation}
Repeating the same idea for all columns, we get that the multiplicative factor cancels out, and
that the homogeneous limit gives 
\begin{equation}
  \bm{\tau}_h(z_1, \bm{v}) =
  \det
  \begin{pmatrix}
    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}  & \frac{\mathcal{Y}_1^{(1)}(z_1)}{z_1 - v_1} &
    \frac{\mathcal{Y}^{(2)}_1(z_1)}{z_1 - v_1} & \dots & \frac{\mathcal{Y}_1^{(n-1)}(z_1)}{z_1 - v_1}\\
    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} & \frac{\mathcal{Y}_2^{(1)}(z_1)}{z_1 - v_2} &
    \frac{\mathcal{Y}_2^{(2)}(z_1)}{z_1 - v_2} &  \dots & \frac{\mathcal{Y}_2^{(n-1)}(z_1)}{z_1 - v_2}\\
    &  \vdots & & \\
    \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} & \frac{\mathcal{Y}_n^{(1)}(z_1)}{z_1 - v_n} &
    \frac{\mathcal{Y}_n^{(2)}(z_1)}{z_1 - v_n} &  \dots & \frac{\mathcal{Y}^{(n-1)}_n(z_1)}{z_1 - v_n}
  \end{pmatrix}\; .
\end{equation}

Finally, let we write \(z_1 \equiv w\) and using elementary row operations we find
\begin{equation}
  \bm{\tau}_h(w, \bm{v}) =
  \frac{1}{\prod_{k=1}^n(w - v_k)}
  \mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2, \dots, \mathcal{Y}_n](w)
  \; .
\end{equation}
that agrees with the results we obtained above.

\end{subequations}

\subsection{Problems}
Here are some important comments and problems to discuss.

It seems that we can consider a basis of functions \(\mathcal{Y}_j(z)\) for the Baker-Akhiezer
functions. I think that this object might say something interesting. In particular, we can
explicitly build solutions of the KP equation. In fact, the functions \(\mathcal{Y}_j\)
above have poles at the Bethe roots, it is interesting. 
\begin{itemize}
\item[\faCheck] What is the pole and root structure of the tau and Baker-Akhiezer (BA) functions?
  In particular, what happens at the Bethe roots?
\item[\faCheck] Basis tau functions
\item[\faCheck] Write the cases n=2 and n=3
\item[\faCheck] What the general case for all \(z_k\) approaching to a single
  value \(w\). 
\item Write these tau functions in terms of Miwa coordinates
\item It turns out that the Baker-Akhiezer function is the appropriate object to discuss
  the Bethe roots. 
  \item I think that these tau functions come from algebro geometric tau functions. 
  \item I can try to study the dynamics closer to the Bethe roots, I think that the
    \(\Omega\)'s will have some interesting expansions, some of them might vanish. 
  \item This might become a Riemann Hilbert problem
  \item Are these tau functions associated to the Calogero-Moser model??
  \item Elliptic case - see slavnov, zabrodin's paper
\end{itemize}

\subsubsection*{Acknowledgments}
I would like to thank...

\printbibliography

\end{document}

### 2025-04-08 draft.tex
add tau function in terms of Miwa coordinates

@@
 
-\subsection{Tau functions}
+\section{Tau functions}
 
@@
 \begin{split}
+\label{eq:tau-function}
   \bm{\tau}(\bm{z}, \bm{v})
@@
 All these tau functions have the form of an
-\emph{alternant determinant} \footnote{see definition~(\ref{def:alt-determinant})
-in the appendix~\ref{app:mathematical}.}
+\emph{alternant determinant}.
 
@@
 that agrees with the results we obtained above. 
+\end{subequations}
 
-\end{subequations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Miwa coordinates}
+
+We now want to write the Slavnov products we defined above in terms of the following 
+coordinates
+\begin{equation}
+  t_p = \frac{1}{p}\sum_{j=1}^n z_j^p\; ,
+\end{equation}
+the so called, Miwa coordinates.
+
+We can show, see~\cite{Araujo:2021ghu} for a detailed proof of this
+statement, that the tau function~\ref{eq:tau-function} admits an
+integral representation of the form (ignoring the signs dependence on
+the length \(n\) of the spin chain)
+\begin{equation}
+  \label{eq:tau-function-miwa}
+  \bm{\tau}(\bm{t}, \bm{v}) = 
+    \det_{j,k}\left(
+    \oint \frac{d w}{2\pi i} e^{\bm{\xi}(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \; ,
+    \right)
+\end{equation}
+where 
+\begin{equation}
+  \bm{\xi}(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p}\; .
+\end{equation}
+One of the advantages of this representation is that now it makes
+sense to consider the limit of the infinite chain, \(n\to \infty\).
 
@@
   value \(w\). 
-\item Write these tau functions in terms of Miwa coordinates
+\item[\faCheck] Write these tau functions in terms of Miwa coordinates
 \item It turns out that the Baker-Akhiezer function is the appropriate object to discuss

### 2025-04-11 draft.tex
start calculating the BA function

@@
 the length \(n\) of the spin chain)
+\todo{\tiny I need to do this calculation carefully now. The contour that gives the
+  representation below should avoid the Bethe root \(v_k\), otherwise, we pick
+poles we want to avoid.}
 \begin{equation}
@@
 \item[\faCheck] Write these tau functions in terms of Miwa coordinates
+\item I need to calculate the Baker-Akhiezer function for this model using the Japanese formula
+  in terms of tau functions. The tau functions above is know. I think that this BA function
+  will be similar to the soliton-like solution discussed in section 3.6.2 (page 41) of~\cite{Zabrodin2018}. 
+  My functions seem to have a pole of order \(N\) at infinity. And \(N\) zeros at the Bethe roots. 
 \item It turns out that the Baker-Akhiezer function is the appropriate object to discuss

### 2025-04-11 draft.tex
add more details on tau functions

@@
 
-We can show, see~\cite{Araujo:2021ghu} for a detailed proof of this
-statement, that the tau function~\ref{eq:tau-function} admits an
-integral representation of the form (ignoring the signs dependence on
-the length \(n\) of the spin chain)
-\todo{\tiny I need to do this calculation carefully now. The contour that gives the
-  representation below should avoid the Bethe root \(v_k\), otherwise, we pick
-poles we want to avoid.}
+It is easy to show that that the tau function~(\ref{eq:tau-function})
+admits an integral representation of the form
 \begin{equation}
@@
     \det_{j,k}\left(
-    \oint \frac{d w}{2\pi i} e^{\bm{\xi}(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \; ,
+    \oint_{\gamma_k} \frac{d w}{2\pi i} e^{\bm{\xi}(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \; ,
     \right)
@@
 \begin{equation}
-  \bm{\xi}(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p}\; .
+  \bm{\xi}(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p}\; ,
 \end{equation}
+and the integration contour \(\gamma_k\) encloses all points
+\(\{z_j\}_{j=1}^n\) but avoids the Bethe root \(v_k\).  For a detailed
+proof of this statement, one may check the
+reference~\cite{Araujo:2021ghu}.  The only difference now is that now
+we need to be carefull with the integration contour \(\gamma_k\).
+
 One of the advantages of this representation is that now it makes

### 2025-04-14 draft.tex
add baker-akhiezer function

@@
 
-\section{Miwa coordinates}
+\section{Baker-Akhiezer function}
 
@@
     \det_{j,k}\left(
-    \oint_{\gamma_k} \frac{d w}{2\pi i} e^{\bm{\xi}(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \; ,
+    \oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \; ,
     \right)
@@
 \begin{equation}
-  \bm{\xi}(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p}\; ,
+  \xi(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p}\; ,
 \end{equation}
@@
 we need to be carefull with the integration contour \(\gamma_k\).
-
 One of the advantages of this representation is that now it makes
 sense to consider the limit of the infinite chain, \(n\to \infty\).
+
+For later convencience, let us also define an invertible matrix
+\(\mathcal{K}\) by its components
+\begin{equation}
+    \mathcal{K}_{jk} = 
+\oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k}\;,  
+\end{equation}
+so that the tau function is simply \(\bm{\tau}(\bm{t}, \bm{v}) = \det\mathcal{K}\).
+
+The Baker-Akhiezer funcion is defined in terms of the Japanese formula~\cite{Zabrodin2018}
+\begin{equation}
+  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
+  \frac{\bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v})}{\bm{\tau}(\bm{t}, \bm{v})}
+\end{equation}
+where 
+\begin{equation}
+  \bm{t} - [\lambda^{-1}] = 
+  \{t_1 - \lambda^{-1}, t_2 - \lambda^{-2}/ 2 ,  t_2 - \lambda^{-3}/3, \dots,  t_p - \lambda^{-p}/p, \dots \}\; .
+\end{equation}
+
+Using the expression~(\ref{eq:tau-function-miwa}), we can write the
+Baker-Akhiezer function in terms of the \(z\)-coordinates.
+Let us first write
+\begin{subequations}
+\begin{equation}
+  \begin{split}
+    e^{\xi(\bm{t}, \lambda)} & = \exp\left( \sum_{p=1}^\infty t_p \lambda^p \right)
+    = \exp\left( \sum_{p=1}^\infty \sum_{j=1}^n \frac{1}{p} z^p \lambda^p \right) \\
+    & = \exp\left( \sum_{j=1}^n \sum_{p=1}^\infty  \frac{1}{p} z_j^p \lambda^p \right)
+    = \exp\left( - \sum_{j=1}^n \ln( 1 -  z_j \lambda ) \right) \\
+    & =  \prod_{j=1}^n \frac{1}{1 -  z_j \lambda} 
+  \end{split}
+\end{equation}
+and we see that these functions have simple poles at \( \lambda = z_j\).
+
+Moreover, 
+\begin{equation}
+  t_p - \lambda^{-p}/p = \frac{1}{p} \sum_{j=1}^n z_j^ p - \lambda^{-p}/p \; , 
+\end{equation}
+and we can write
+\begin{equation}
+  \begin{split}
+    e^{\xi(\bm{t} - [\lambda^{-1}], w^{-1})} & = \exp\left[ \sum_{p=1}^\infty \left(t_p  - \frac{\lambda^{-p}}{p}\right) w^{-p} \right]\\
+    & = e^{\xi(\bm{t}, w^{-1})} \exp\left[ - \sum_{p=1}^\infty \frac{\lambda^{-p}}{p} w^{-p} \right] \\
+    & = e^{\xi(\bm{t}, w^{-1})} \exp\left[ \ln ( 1 - 1 / (\lambda w)) \right]\\
+    & = \left( 1 - \frac{1}{\lambda w}\right)  \prod_{j=1}^n \frac{1}{1 -  z_j /w} \; .
+  \end{split}
+\end{equation}
+\end{subequations}
+
+Using these expressions, we can write 
+\begin{equation}
+  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v}) =
+  \det_{j,k}\left[
+  \oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \left( 1 - \frac{1}{\lambda w} \right) \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} 
+  \right]\; .
+\end{equation}
+Now, we define the matrix \(\widetilde{\mathcal{K}}(\lambda)\) by its components
+\begin{equation}
+    \widetilde{\mathcal{K}}_{jk}(\lambda)  = -  \frac{1}{\lambda} 
+  \oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{- 1})} \frac{w^{-j -1 }\mathcal{Y}_k(w)}{w - v_k} \; ,
+\end{equation}
+and we then have 
+\begin{equation}
+  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v}) =
+  \bm{\tau}(\bm{t}, \bm{v})
+  \det \left( \mathbb{1} +  \mathcal{K}^{-1} \widetilde{\mathcal{K}}(\lambda) \right)\; .
+\end{equation}
+
+We finally conclude that the Bakher-Akhiezer function can be written as
+\begin{equation}
+  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
+  \det \left( \mathbb{1} +  \mathcal{K}^{-1} \widetilde{\mathcal{K}}(\lambda) \right)\; .
+\end{equation}
 
@@
 \item[\faCheck] Write these tau functions in terms of Miwa coordinates
-\item I need to calculate the Baker-Akhiezer function for this model using the Japanese formula
-  in terms of tau functions. The tau functions above is know. I think that this BA function
-  will be similar to the soliton-like solution discussed in section 3.6.2 (page 41) of~\cite{Zabrodin2018}. 
+\item[\faCheck] I need to calculate the Baker-Akhiezer function for this model using the Japanese formula
+  in terms of tau functions.
+\item Write some explicit expressions for \(N=2\) and \(N=3\). 
+\item Better investigate these functions. See Fredholm determinant. 
+  I think that this BA function will be similar to the soliton-like solution discussed in section 3.6.2 (page 41) of~\cite{Zabrodin2018}. 
   My functions seem to have a pole of order \(N\) at infinity. And \(N\) zeros at the Bethe roots. 

### 2025-04-15 draft.tex
correct integral representation of the tau function

@@
 that is the inverse of the Vandermonde determinant
-\(\Delta(\bm{u}_\ell)\).
+\(\Delta(\bm{u}_\ell) = \prod_{j>k}(u_j - u_k)\).
 Finally, we have  that \(\hat{\Omega}_\ell\) are minors of the matrix \(\bm{\Omega}\) with the \(\ell\)-th
@@
   & = \frac{1}{\Delta(\bm{z})} \det[\Omega_j(z_k) ]_{j,k=1}^n \\
-  & = \frac{1}{\Delta(\bm{z})} \det\left[\frac{\mathcal{Y}_j(z_k)}{z_k - v_j} \right]_{j,k=1}^n  \\
+  & = \frac{1}{\Delta(\bm{z})} \det\left[\frac{\mathcal{Y}_j(z_k)}{z_k - v_j} \right]_{j,k=1}^n  \; .
 \end{split}
 \end{equation}
-All these tau functions have the form of an
-\emph{alternant determinant}.
+All these tau functions have the form of an \emph{alternant
+determinant}.  Henceforth, we will only refer to the matrix
+\(\bm{\Omega}\) defined by the components
+\begin{equation}
+  \label{eq:omega-matrix}
+  \Omega_{jk} = \frac{\mathcal{Y}_j(z_k)}{z_k - v_j}\; .
+\end{equation}
 
@@
 
-It is easy to show that that the tau function~(\ref{eq:tau-function})
-admits an integral representation of the form
+Let us also define
+\begin{equation}
+  \begin{split}
+    e^{\xi(\bm{t}, \lambda)} & = \exp\left( \sum_{p=1}^\infty t_p \lambda^p \right)
+    = \exp\left( \sum_{p=1}^\infty \sum_{j=1}^n \frac{1}{p} z^p \lambda^p \right) \\
+    & = \exp\left( \sum_{j=1}^n \sum_{p=1}^\infty  \frac{1}{p} z_j^p \lambda^p \right)
+    = \exp\left( - \sum_{j=1}^n \ln( 1 -  z_j \lambda ) \right) \\
+    & =  \prod_{j=1}^n \frac{1}{1 -  z_j \lambda} 
+  \end{split}
+\end{equation}
+where \(\lambda\) is a complex parameter. 
+and we see that these functions have simple poles at \( \lambda = z_j^{-1}\).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Integral representation of the tau functions}
+
+It is easy to show, see~\cite{Araujo:2021ghu} and references therein,
+that that the tau function~(\ref{eq:tau-function}) admits an integral
+representation of the form
 \begin{equation}
@@
 \begin{equation}
-  \xi(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p}\; ,
+  \xi(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p} \quad \Leftrightarrow \quad
+  \xi(\bm{z}, w^{-1}) = w^n \prod_{j=1}^n (w - z_j)^{-1} \; ,
 \end{equation}
 and the integration contour \(\gamma_k\) encloses all points
-\(\{z_j\}_{j=1}^n\) but avoids the Bethe root \(v_k\).  For a detailed
-proof of this statement, one may check the
-reference~\cite{Araujo:2021ghu}.  The only difference now is that now
-we need to be carefull with the integration contour \(\gamma_k\).
-One of the advantages of this representation is that now it makes
-sense to consider the limit of the infinite chain, \(n\to \infty\).
+\(\{z_j\}_{j=1}^n\) but avoids the Bethe root \(v_k\).
+One of the advantages of this representation is
+that now it makes sense to consider the limit of the infinite chain,
+\(n\to \infty\).
 
-For later convencience, let us also define an invertible matrix
-\(\mathcal{K}\) by its components
+There are some minor differences between our calculations and the
+original references. First, we need to be carefull with the
+integration contour \(\gamma_k\). For this reason, we want to
+show explicitly this result.
+
+Let us define the invertible matrix \(\bm{\mathcal{K}}^T\) by its components
 \begin{equation}
-    \mathcal{K}_{jk} = 
-\oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k}\;,  
+    \mathcal{K}_{kj} = 
+\oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{z}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k}\;. 
 \end{equation}
-so that the tau function is simply \(\bm{\tau}(\bm{t}, \bm{v}) = \det\mathcal{K}\).
+Explicitly, we have 
+\begin{equation}
+  \begin{split}
+    \mathcal{K}_{kj}
+    = & \oint_{\gamma_k} \frac{d w}{2\pi i} \frac{w^{n-j}}{\prod_{j} (w - z_j)}
+    \frac{\mathcal{Y}_k(w)}{w - v_k} = \sum_{\ell =1}^n \frac{z_l^{n-j}}{\prod_{j\neq \ell} (z_\ell - z_j)}
+    \frac{\mathcal{Y}_k(z_\ell)}{z_\ell - v_k}\\
+    & = \sum_{\ell = 1}^n  \Omega_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{j\neq \ell} (z_\ell - z_j)} \right)
+  \end{split}
+\end{equation}
+where in the second line we have used the
+\(\bm{\Omega}\)-matrix defined in~(\ref{eq:omega-matrix}).
+
+It is easy to see that
+\begin{equation}
+  \begin{split}
+  \det \bm{\mathcal{K}} & = \det(\bm{\Omega}) \det_{l,j}\left( \frac{z_l^{n-j}}{\prod_{j\neq l} (z_l - z_j)}\right) \\
+  & = \det(\bm{\Omega}) \det_{l, j}(z_l^{n-j}) \prod_{\substack{j, l =1 \\ j \neq l}}^n (z_l - z_j)^{-1} \; .
+  \end{split}
+\end{equation}
+We also have the identities 
+\begin{subequations}
+  \begin{equation}
+	\det_{l,j}(z_l^{n-j}) = (-1)^{n(n-1)/2} \Delta(\bm{z})\; ,
+  \end{equation}
+  and
+  \begin{equation}
+	\prod_{\substack{j, l = 1 \\ j \neq l}}^n (z_l - z_j) = (-1)^{n(n-1)/2} \Delta(\bm{z})^2\; . 
+  \end{equation}
+\end{subequations}
+
+Putting all these facts together, we finally see that 
+\(\bm{\tau}(\bm{z}, \bm{v}) = \det\bm{\mathcal{K}}\).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Baker-Akhiezer function}
 
@@
 Baker-Akhiezer function in terms of the \(z\)-coordinates.
-Let us first write
-\begin{subequations}
-\begin{equation}
-  \begin{split}
-    e^{\xi(\bm{t}, \lambda)} & = \exp\left( \sum_{p=1}^\infty t_p \lambda^p \right)
-    = \exp\left( \sum_{p=1}^\infty \sum_{j=1}^n \frac{1}{p} z^p \lambda^p \right) \\
-    & = \exp\left( \sum_{j=1}^n \sum_{p=1}^\infty  \frac{1}{p} z_j^p \lambda^p \right)
-    = \exp\left( - \sum_{j=1}^n \ln( 1 -  z_j \lambda ) \right) \\
-    & =  \prod_{j=1}^n \frac{1}{1 -  z_j \lambda} 
-  \end{split}
-\end{equation}
-and we see that these functions have simple poles at \( \lambda = z_j\).
-
 Moreover, 
@@
 \end{equation}
-\end{subequations}
 

### 2025-04-16 draft.tex
calculate the ba function -- probably wrong

@@
 representation of the form
+\todo{Zero is not a pole of this expression}
 \begin{equation}
@@
 Using these expressions, we can write 
+\todo{Zero is a pole of this expression}
 \begin{equation}
@@
 \end{equation}
+We can now  calculate this integral.
+
+\subsubsection{Regular case}
+Let \(D_k\) be a domain defined by \(\partial D = \gamma_k\). We can
+see that the function
+\begin{equation}
+  \widetilde{\mathcal{Y}}_k(w)
+  = \left( 1 - \frac{1}{\lambda w} \right) \mathcal{Y}_k(w) \; ,
+\end{equation}
+is holomorphic in \(D_k\) and has a zero at \(\lambda = z_k^{-1}\). Therefore, we can repeat the previous arguments
+to calculate the shifted tau functions. The final result is 
+\begin{subequations}
+\begin{equation}
+  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v})\ \Rightarrow \
+  \bm{\tau}(\lambda^{-1};\bm{z},\bm{v}) = 
+  \frac{1}{\Delta(\bm{z})}
+  \det_{j,k}\left[
+  \left( 1 - \frac{1}{\lambda z_j} \right) \frac{\mathcal{Y}_j(z_k)}{z_k - v_j} 
+  \right]\; , 
+\end{equation}
+and elementary column operations, we find
+\begin{equation}
+  \begin{split}
+    \bm{\tau}(\lambda^{-1};\bm{z},\bm{v})
+    & = \bm{\tau}(\bm{z},\bm{v}) \prod_{j=1}^n\left( 1 - \frac{1}{\lambda z_j} \right) \\ 
+    & = \bm{\tau}(\bm{z},\bm{v}) (-1)^n \prod_{j=1}^n \frac{1 - \lambda z_j}{\lambda z_j} \; . 
+  \end{split}
+\end{equation}
+\end{subequations}
+
+Putting all these facts together, we find that the Baker-Akhiezer function is given by
+\begin{equation}
+  \psi(\lambda, \bm{z}) =  \frac{(-1)^n}{\lambda^n}\prod_{j=1}^n \frac{1}{z_j}\; ,
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Fredholm determinant}
+
 Now, we define the matrix \(\widetilde{\mathcal{K}}(\lambda)\) by its components

### 2025-04-17 draft.tex
improve calculations of the BA functions

--- 2025-04-15 draft.tex
@@
 representation of the form
+\begin{subequations}
 \begin{equation}
@@
     \det_{j,k}\left(
-    \oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \; ,
-    \right)
+    \oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \right)\; ,
 \end{equation}
@@
   \xi(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p} \quad \Leftrightarrow \quad
-  \xi(\bm{z}, w^{-1}) = w^n \prod_{j=1}^n (w - z_j)^{-1} \; ,
+  \xi(\bm{z}, w^{-1}) = w^n \prod_{j=1}^n (w - z_j)^{-1} \; . 
 \end{equation}
-and the integration contour \(\gamma_k\) encloses all points
-\(\{z_j\}_{j=1}^n\) but avoids the Bethe root \(v_k\).
-One of the advantages of this representation is
+In the above integral, we consider that integration curve \(\gamma_k\)
+encloses all poles except the Bethe root \(v_k\).
+
+In terms of the \(z\)-coordinates, we have
+\begin{equation}
+  \label{eq:tau-function}
+  \bm{\tau}(\bm{z}, \bm{v}) =
+    \det_{j,k}\left(
+    \oint_{\gamma_k} \frac{d w}{2\pi i}
+    \prod_{l=1}^n \frac{1}{w - z_l} \frac{w^{n-j}\mathcal{Y}_k(w)}{w - v_k} \right) \; . 
+\end{equation}
+\end{subequations}
+Now, it is easy to see that \(w =0\) is not a pole.
+
+All in all, the integration curve \(\gamma_k\) encloses all poles
+\(\{z_j\}_{j=1}^n\).  One of the advantages of this representation is
 that now it makes sense to consider the limit of the infinite chain,
@@
     \mathcal{K}_{kj}
-    = & \oint_{\gamma_k} \frac{d w}{2\pi i} \frac{w^{n-j}}{\prod_{j} (w - z_j)}
-    \frac{\mathcal{Y}_k(w)}{w - v_k} = \sum_{\ell =1}^n \frac{z_l^{n-j}}{\prod_{j\neq \ell} (z_\ell - z_j)}
+    = & \oint_{\gamma_k} \frac{d w}{2\pi i} \frac{w^{n-j}}{\prod_{s} (w - z_s)}
+    \frac{\mathcal{Y}_k(w)}{w - v_k} = \sum_{\ell =1}^n \frac{z_l^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)}
     \frac{\mathcal{Y}_k(z_\ell)}{z_\ell - v_k}\\
-    & = \sum_{\ell = 1}^n  \Omega_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{j\neq \ell} (z_\ell - z_j)} \right)
+    & = \sum_{\ell = 1}^n  \Omega_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
   \end{split}
 \end{equation}
-where in the second line we have used the
-\(\bm{\Omega}\)-matrix defined in~(\ref{eq:omega-matrix}).
+where in the second line we have used the \(\bm{\Omega}\)-matrix
+defined in~(\ref{eq:omega-matrix}).
 
@@
     & = e^{\xi(\bm{t}, w^{-1})} \exp\left[ - \sum_{p=1}^\infty \frac{\lambda^{-p}}{p} w^{-p} \right] \\
-    & = e^{\xi(\bm{t}, w^{-1})} \exp\left[ \ln ( 1 - 1 / (\lambda w)) \right]\\
-    & = \left( 1 - \frac{1}{\lambda w}\right)  \prod_{j=1}^n \frac{1}{1 -  z_j /w} \; .
+    & = e^{\xi(\bm{t}, w^{-1})} \exp\left[ \ln ( 1 - 1 / (\lambda w)) \right]
+      = \left( 1 - \frac{1}{\lambda w}\right)  \prod_{j=1}^n \frac{1}{1 -  z_j /w} \\
+    & = \frac{w^{n-1}}{\lambda } \left( \lambda w - 1 \right)  \prod_{j=1}^n \frac{1}{w -  z_j} \\
   \end{split}
@@
   \det_{j,k}\left[
-  \oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \left( 1 - \frac{1}{\lambda w} \right) \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} 
+  \oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{- j -1} ( \lambda w - 1) \mathcal{Y}_k(w)}{\lambda(w - v_k)} 
   \right]\; .
 \end{equation}
+that in terms of the \(z\)-coordinates becomes
+\begin{equation}
+\begin{split}
+  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v})
+  & = \det_{j,k}\left[\oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}  
+    \frac{( \lambda w - 1) w^{n-j-1}\mathcal{Y}_k(w)}{\lambda(w - v_k)} \right]\\
+  & = \det_{j,k}\left[
+    \oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}  
+    \frac{w^{n-j-1}\widetilde{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}
+    \right]
+\end{split}
+\end{equation}
+where we have defined the function 
+\begin{equation}
+  \widetilde{\mathcal{Y}}_k(w; \lambda)
+  = \frac{( \lambda w - 1)}{\lambda} \mathcal{Y}_k(w) \; ,
+\end{equation}
+From these expressions, it is easy to see that for \(j=n\), then \(w =
+0\) is a pole and we must pick this term in the integration curve
+\(\gamma_k\).
+
+Let us define the components
+\begin{equation}
+  \begin{split}
+    \widetilde{\mathcal{K}}_{kj} = &
+    \oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}
+    \frac{w^{n-j-1}\widetilde{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}
+    + \delta_{nj} F_k(\lambda) \\
+    & = \sum_{\ell = 1}^n  \widetilde{\Omega}_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
+    + \delta_{nj} F_k(\lambda) \\
+  \end{split}
+\end{equation}
+where
+\begin{equation}
+  \widetilde{\Omega}_{k\ell}
+  = \frac{1}{z_\ell} \frac{\widetilde{\mathcal{Y}}_k(\lambda, z_\ell)}{z_\ell - v_k}
+  = \frac{(\lambda z_\ell -1)}{\lambda z_\ell} {\Omega}_{k\ell} 
+\; , \qquad 
+ F_k(\lambda) = (-1)^n \frac{\widetilde{\mathcal{Y}}_k(\lambda; 0)}{v_k }  \prod_{s=1}^n z_s^{-1} \; .
+\end{equation}
+We conclude that we are basically adding a constant vector
+\(\bm{F} = (F_1, \dots , F_n)\) to the \(n\)-th line of a matrix with components...
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Fredholm determinant}
+
 Now, we define the matrix \(\widetilde{\mathcal{K}}(\lambda)\) by its components

### 2025-04-17 draft.tex
add more details on the calculation of the BA function

@@
     & = \sum_{\ell = 1}^n  \widetilde{\Omega}_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
-    + \delta_{nj} F_k(\lambda) \\
+    + F_k(\lambda)\delta_{nj}  \\
   \end{split}
@@
 \end{equation}
-We conclude that we are basically adding a constant vector
-\(\bm{F} = (F_1, \dots , F_n)\) to the \(n\)-th line of a matrix with components...
+
+In order to simplify our analysis, let us define one more matrix
+\(\widehat{\mathcal{K}}\) by its components
+\begin{equation}
+    \widehat{\mathcal{K}}_{kj} = 
+    \oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}
+    \frac{w^{n-j-1}\widetilde{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}\; .
+\end{equation}
+We conclude that \(\widetilde{\mathcal{K}}\) can be obtained from 
+\(\widehat{\mathcal{K}}\) by adding to each component of the \(n\)-th row
+the corresponding component of the vector \(\bm{F} = (F_1, \dots , F_n)\). 
+Let us write this operation as 
+\begin{equation}
+  \widetilde{\mathcal{K}} = \widehat{\mathcal{K}} + \bm{F}_{[\rightarrow n-row]}\; ,
+\end{equation}
 

### 2025-04-18 draft.tex
calculate the BA in the z-coordinate system

@@
     \oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}  
-    \frac{w^{n-j-1}\widetilde{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}
+    \frac{w^{n-j-1}\widehat{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}
     \right]
@@
 \begin{equation}
-  \widetilde{\mathcal{Y}}_k(w; \lambda)
+  \widehat{\mathcal{Y}}_k(w; \lambda)
   = \frac{( \lambda w - 1)}{\lambda} \mathcal{Y}_k(w) \; ,
@@
     \oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}
-    \frac{w^{n-j-1}\widetilde{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}
+    \frac{w^{n-j-1}\widehat{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}
     + \delta_{nj} F_k(\lambda) \\
-    & = \sum_{\ell = 1}^n  \widetilde{\Omega}_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
+    & = \sum_{\ell = 1}^n  \widehat{\Omega}_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
     + F_k(\lambda)\delta_{nj}  \\
@@
 \begin{equation}
-  \widetilde{\Omega}_{k\ell}
+  \widehat{\Omega}_{k\ell}
   = \frac{1}{z_\ell} \frac{\widetilde{\mathcal{Y}}_k(\lambda, z_\ell)}{z_\ell - v_k}
@@
 \; , \qquad 
- F_k(\lambda) = (-1)^n \frac{\widetilde{\mathcal{Y}}_k(\lambda; 0)}{v_k }  \prod_{s=1}^n z_s^{-1} \; .
+ F_k(\lambda) = (-1)^n \frac{\widehat{\mathcal{Y}}_k(\lambda; 0)}{v_k }  \prod_{s=1}^n z_s^{-1} \; .
 \end{equation}
@@
     \widehat{\mathcal{K}}_{kj} = 
-    \oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}
-    \frac{w^{n-j-1}\widetilde{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}\; .
+    \sum_{\ell = 1}^n  \widehat{\Omega}_{k \ell}
+    \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
+    \; .
 \end{equation}
@@
 \begin{equation}
-  \widetilde{\mathcal{K}} = \widehat{\mathcal{K}} + \bm{F}_{[\rightarrow n-row]}\; ,
+  \widetilde{\mathcal{K}} = \widehat{\mathcal{K}} + \bm{0}_{[ \bm{F} \to n-row]}\; . 
+\end{equation}
+Where we use the notation \(\mathcal{A}_{[ \bm{F} \to j-row]} \) to denote
+the replacement of the \(j-th\) row of the matrix with the vector \(\bm{F}\).
+Above we have considered this operation with the zero matrix \(\bm{0}\).
+
+By the multilinearity of the determinant, we can write
+\begin{equation}
+  \det \widetilde{\mathcal{K}} = 
+    \det \widehat{\mathcal{K}} + 
+    \det \widehat{\mathcal{K}}_{[\bm{F} \to n-row]}\; .
+\end{equation}
+
+It is now easy to see that \(\det \widehat{\mathcal{K}}\) is
+proportional to the tau functions (Slavnov products), that is
+\begin{equation}
+    \det \widehat{\mathcal{K}}  = 
+    \det(\widehat{\Omega})
+    \det_{l,j}
+    \left( \frac{z_l^{n-j}}{\prod_{s\neq l} (z_l - z_s)} \right)\\
+    = \frac{\det(\widehat{\Omega})}{\Delta(\bm{z})}
+\end{equation}
+where \(\widehat{\Omega}\) is the matrix formed by the components
+\(\widehat{\Omega}_{i,j}\). The above determinant is itself a tau function,
+but we can also write is as
+\begin{equation}
+    \det \widehat{\mathcal{K}} = 
+    \frac{\det(\Omega)}{\Delta(\bm{z})}
+    \prod_{l=1}^n \left( 1 - \frac{1}{\lambda z_l} \right) 
+    = \bm{\tau}(\bm{z}, \bm{v}) \prod_{l=1}^n \left( 1 - \frac{1}{\lambda z_l} \right) \; .
+\end{equation}
+
+Finally, using the elementary symmetric polynomials \(\sigma_p^{(n)}\), we write
+\begin{equation}
+  \prod_{l=1}^n \left( 1 - \frac{1}{\lambda z_l} \right) = 1 + 
+  \sum_{p=1}^n (-1)^p \lambda^{-p} \sigma_p^{(n)}(\bm{z}^{-1})\; .
+\end{equation}
+where \( \bm{z}^{-1} = \{z_1^{-1}, z_2^{-1}, \dots , z_n^{-1}\}\).
+
+Putting all these facts together, we write the Baker-Akhiezer function
+as 
+\begin{equation}
+  \psi(\lambda; \bm{z}, \bm{v}) =
+  e^{\xi(\bm{t}, \lambda)}  \left[ 1 + 
+  \sum_{p=1}^n (-1)^p \lambda^{-p} \sigma_p^{(n)}(\bm{z}^{-1})
+    + \frac{1}{\bm{\tau}(\bm{z}, \bm{v})}
+    \det \widehat{\mathcal{K}}_{[\bm{F} \to n-row]}
+  \right]\; .
 \end{equation}

### 2025-04-21 draft.tex
conclude first draft of the paper... refine it

@@
     \widetilde{\mathcal{K}}_{kj} = &
-    \oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}
+    \oint_{\tilde \gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}
     \frac{w^{n-j-1}\widehat{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}
@@
 \end{equation}
-where
+where \(\tilde{\gamma}_k\) is a contour that does not pick
+the point \(w=0\); and
 \begin{equation}
@@
 \end{equation}
-Where we use the notation \(\mathcal{A}_{[ \bm{F} \to j-row]} \) to denote
-the replacement of the \(j-th\) row of the matrix with the vector \(\bm{F}\).
-Above we have considered this operation with the zero matrix \(\bm{0}\).
+Where we use the notation \(\mathcal{A}_{[ \bm{F} \to j-row]} \) to
+denote the replacement of the \(j-th\) row of the matrix with the
+vector \(\bm{F}\).  Above we have considered this operation with the
+zero matrix \(\bm{0}\).
 
@@
 
+%%% Maybe I should calculate some examples
+%\subsection{Examples} Let us now consider the cases \(n=2, 3\).
+%We have calculated the tau functions for these objets. The
+%elementary symmetric polynomials are also known. Therefore,
+%the only detail we need to complete now is the calculation of
+%the matrix \(\widehat{\mathcal{K}}\). 
+%
+%\subsubsection{n=2} We
+%we have \(\mathcal{Y}_j\) for \(j=1,2\) and two Bethe roots
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Now, we define the matrix \(\widetilde{\mathcal{K}}(\lambda)\) by its components
-\begin{equation}
-    \widetilde{\mathcal{K}}_{jk}(\lambda)  = -  \frac{1}{\lambda} 
-  \oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{- 1})} \frac{w^{-j -1 }\mathcal{Y}_k(w)}{w - v_k} \; ,
-\end{equation}
-and we then have 
+We now want to consider the above calculations in the Miwa
+coordinates. This allows us to consider the infinite chain limit.
+
+We define the matrix \(\check{\mathcal{K}}(\lambda)\) by its components
+\begin{equation}
+    \check{\mathcal{K}}_{jk}  = -  
+    \oint_{\gamma_k} \frac{dw}{2\pi i}
+    e^{\xi(\bm{t}, w^{- 1})} \frac{w^{-j -1 }\mathcal{Y}_k(w)}{w - v_k} \; .
+\end{equation}
+
+Therefore, we have that 
+\begin{equation}
+  \widetilde{\mathcal{K}}_{kj} = 
+  \mathcal{K}_{kj}  + \frac{1}{\lambda}
+  \check{\mathcal{K}}_{kj}
+  \ \Leftrightarrow \
+  \widetilde{\mathcal{K}} = 
+  \mathcal{K}  + \frac{1}{\lambda}
+  \check{\mathcal{K}}\; , 
+\end{equation}
+and since \(\mathcal{K}\) is invertible, we get
+\begin{equation}
+  \widetilde{\mathcal{K}} = 
+  \mathcal{K}\left( \mathbb{1}  +
+  \frac{1}{\lambda}\mathcal{K}^{-1}\check{\mathcal{K}} \right)\; .
+\end{equation}
+
+Putting all these facts together, we find that the shifted
+tau-functions are
 \begin{equation}
@@
   \bm{\tau}(\bm{t}, \bm{v})
-  \det \left( \mathbb{1} +  \mathcal{K}^{-1} \widetilde{\mathcal{K}}(\lambda) \right)\; .
+  \det \left( \mathbb{1} + \frac{1}{\lambda}
+  \mathcal{K}^{-1} \check{\mathcal{K}} \right)\; .
 \end{equation}
@@
   \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
-  \det \left( \mathbb{1} +  \mathcal{K}^{-1} \widetilde{\mathcal{K}}(\lambda) \right)\; .
-\end{equation}
+  \det \left( \mathbb{1} +
+    \frac{1}{\lambda} \mathcal{T}
+  \right)\; .
+\end{equation}
+where \(\mathcal{T} = \mathcal{K}^{-1} \check{\mathcal{K}}\).
 
@@
   in terms of tau functions.
-\item Write some explicit expressions for \(N=2\) and \(N=3\). 
-\item Better investigate these functions. See Fredholm determinant. 
+\item[\faCheck]  Write some explicit expressions for \(N=2\) and \(N=3\). 
+\item See the Limit \(L \to \infty\) and \(N \to \infty\) but sufficiently slower than \(L\). 
+  I think that the matrix \(\mathcal{T}\) is a trace class operator and we write the BA function
+  as a Fredholm determinant. 
+\item Better investigate these functions in Miwa coordinates. See Fredholm determinant. 
   I think that this BA function will be similar to the soliton-like solution discussed in section 3.6.2 (page 41) of~\cite{Zabrodin2018}. 

### 2025-04-25 draft.tex
start introduction

@@
 
+One important ingredient in the Algebraic Bethe Ansatz is the scalar
+product of Bethe states.  There are many important results on this
+topic, see~\cite{Korepin:1993kvr} and references therein, but here we
+turn our attention to the well known fact that scalars products in
+the algebraic Bethe ansatz can be written as determinants.
+
+More specifically, we will investigate a particular type of
+correlation functions in quantum integrable spin chains, the so called
+\emph{Slavnov product}~\cite{Slavnov1989}. These objects can be seen as building blocks
+of more sofisticated correlation functions and are instrumental in the
+study of norms of Bethe wave functions~\cite{Korepin:1993kvr}.  But
+more importantly for our present discussion, Slavnov products seem to
+be a bridge connecting quantum and classical integrable system.
+
+The study of connections between classical and quantum integrable
+systems is an old subject, and has been addressed from a wide range of
+perspectives~\cite{Wu:1975mw, Its:1992bj, korepin2000the, Foda2009,
+  Alexandrov:2011aa}.  In~\cite{Foda:2009zz}, the authors started the
+analysis of the connections between the Slavnov products of the
+Heisenberg XXZ spin chain, and the Kadomtsev–Petviashvili (KP)
+classical integrable hierarchy. This analysis has been extended to
+some directions and applications, for example~\cite{Wheeler:2010vmq,
+  Foda:2010, Takasaki:2010qm, Foda:2012wn, Foda:2012wf}.
+
+In (my papers)
+the author of the current paper started studying some other cases of
+this interesting connection, in particular, in the case of the Temperley-Lieb spin chains
+and the Q-Boson model. In all these cases, although the specific details of he
+Slavnov product are radically different, the general functional structure
+are basically the same, modulo some multiplicative terms.
+
+In~\cite{Belliard:2019bfz}, the authors show
+the reason behind this fact.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-One important ingredient in the Algebraic Bethe Ansatz is the scalar
-product of Bethe states.  The is many important results on this topic,
-see~\cite{Korepin:1993kvr} and references therein. Here we focus on
-the scalar product between an on-shell and an off-shell Bethe vectors,
-the so called \emph{Slavnov product}.
-
-It is known that scalars products in the algebraic Bethe ansatz 
-can be written as determinants. In~\cite{Belliard:2019bfz}, the
-authors show the reason behind this fact. Let us start
-with a short review of this work.
+This section reviews the main arguments in~\cite{Belliard:2019bfz}.
 

### 2025-04-28 draft.tex
improve draft

@@
-\documentclass[a4paper,11pt]{amsart}
-
-\usepackage{/home/thiago/.config/dot-files/latex/globaldef}
-\input{/home/thiago/.config/dot-files/latex/definitions.tex}
+\documentclass[a4paper,12pt]{amsart}
+
+\usepackage{globaldef}
+\input{definitions.tex}
 
@@
   Foda:2010, Takasaki:2010qm, Foda:2012wn, Foda:2012wf}.
-
-In (my papers)
-the author of the current paper started studying some other cases of
-this interesting connection, in particular, in the case of the Temperley-Lieb spin chains
-and the Q-Boson model. In all these cases, although the specific details of he
-Slavnov product are radically different, the general functional structure
-are basically the same, modulo some multiplicative terms.
-
-In~\cite{Belliard:2019bfz}, the authors show
-the reason behind this fact.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Scalar products and determinant formulas}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This section reviews the main arguments in~\cite{Belliard:2019bfz}.
-
-Let us start with a set of arbitrary complex numbers
-\(\bm{u} = \{u_j\}_{j=1}^{n+1}\), and we define \(n+1\) sets
-\(\bm{u}_j=\bm{u}\setminus \{u_j\}\) so that we can define
-\(n+1\) off-shell Bethe vectors \(\ket{\Psi(\bm{u}_j)}\).
-
-Consider now a set of Bethe roots \(\bm{v} = \{ v_k \}_{k=1}^n\),
-so that we have the on-shell Bethe vectors \(\ket{\Psi(\bm{v})}\). 
-In fact, let us consider the action of the transfer matrix \(\mathcal{T}(z)\)
-on the dual Bethe vector, that is 
+In~\cite{Araujo:2021ghu, Araujo:2024klz}, the author of the current
+paper also investigated some developments of this research field. In
+particular, the relation between integrable hierarchies and quantum
+integrable systems such as the Q-Boson integrable system and in the
+Temperley-Lieb open spin chains.
+
+Although the specific details of he Slavnov product are radically
+different, In all these cases discussed in the previous paragraph, the
+general functional structure of the Slavnov products of different
+models are basically the same. More specifically, module some
+multiplicative terms, all these expressions are determinant, and it is
+the fact that allows us to manipulate these objects to show that thesy
+are KP and Toda tau functions.
+
+Belliard and Slavnov~\cite{Belliard:2019bfz} have addressed precisely
+this property: \emph{Why scalar products in the algebraic Bethe ansatz
+have determinant representations}.  Using their results, we now want
+to understand \emph{why and how (some) scalar products in the
+algebraic Bethe ansatz are KP and Toda tau functions}. In the current
+show that as long as the integrable system satisfies the conditions
+established in~\cite{Belliard:2019bfz} -- and some additional
+restrictions -- the Slavnov product is guaranteed to satisfy the KP
+integrable hiearchy. Moreover, we also discuss some immediate
+consequences of this result.
+
+In section 2 we review the main aspects of the
+work~\cite{Belliard:2019bfz} and fix the main notation we use in the
+remainder of this work. (...)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Scalar products as determinants}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In order to make the paper as self-contained as possible, this section
+reviews the main arguments in~\cite{Belliard:2019bfz}. Let us start
+with a set of arbitrary complex numbers \(\bm{u} =
+\{u_j\}_{j=1}^{n+1}\), and we set \(n+1\) sets
+\(\bm{u}_j=\bm{u}\setminus \{u_j\}\). In the algebraic Bethe ansatz
+setting~\cite{Korepin:1993kvr}, we can now define \(n+1\) off-shell
+Bethe vectors \(\ket{\Psi(\bm{u}_j)}\), i.e. Bethe states where the
+algebraic Bethe equations are not imposed on
+\(\bm{u}_j\). Additionally, we also consider a set of Bethe roots
+\(\bm{v} = \{ v_k \}_{k=1}^n\), and the on-shell Bethe vectors
+\(\ket{\Psi(\bm{v})}\).
+
+\subsection{Determinant representation}
+The action of the transfer matrix \(\mathcal{T}(z)\), that is an
+Hermitian operator, on the dual Bethe vector is given by
 \begin{equation}
@@
 
-From these definitions, we now introduce \(n+1\) Slavnov products 
-\begin{equation}
-  \bm{\zeta}_j = \bracket{\Psi(\bm{v})}{\Psi(\bm{u}_j)}\qquad j =1, \dots, n+1\; .
-\end{equation}
-We want to show that \(\bm{\zeta}_j\) satisfy a system of linear equations.
-
-In order to see this, we calculate
-\begin{equation}
-  \bra{\Psi(\bm{v})} {\color{violet}\left(\mathcal{T}(u_j)\ket{\Psi(\bm{u}_j)} \right)} =
-  {\color{violet}\left(\bra{\Psi(\bm{v})}\mathcal{T}(u_j)\right)}\ket{\Psi(\bm{u}_j)} 
+We now introduce \(n+1\) scalar products between the on-shell and
+off-shell Bethe states
+\begin{equation}
+  \bm{\zeta}_j(\bm{u}_j, \bm{v}) \equiv  \bm{\zeta}_j
+  = \bracket{\Psi(\bm{v})}{\Psi(\bm{u}_j)}\qquad j =1, \dots, n+1\; .
+\end{equation}
+These partially on-shell scalar products are called \emph{Slavnov
+products}.
+
+Before procceding, let us also establish the class of models we are
+dealing with.  Let us consider a class of integrable models where the
+action of the transfer matrix on a generic off-shell bethe states can
+be expanded as
+\begin{subequations}
+\begin{equation}
+\label{eq:scalar-exp}
+  \mathcal{T}(u_j)\ket{\Psi(\bm{u}_j)}  = \sum_{k=1}^{n+1} L_{jk} \ket{\Psi(\bm{u}_k)} \; ,
+\end{equation}
+where \(L_{jk}\) are numerical coefficients. Observe that the terms
+\(L_{jk}\) with \(j\neq k\) contain the unwanted terms.; and these
+non-diagonal terms must vanish when the Bethe equations are
+satisfied. Therefore, since the diagonal coefficient survives, that is
+\(L_{jj}\), we conclude that these terms must be equal to the
+eigenvalue of the tranfer matrix, that is
+\begin{equation}
+  \mathcal{T}(u_j)\ket{\Psi(\bm{u}_j)} =  \Lambda(u_j; \bm{u}_j) \ket{\Psi(\bm{v})} + 
+  \sum_{\substack{k=1\\ k\neq j}}^{n+1} L_{jk} \ket{\Psi(\bm{u}_k)} \; . 
+\end{equation}
+\end{subequations}
+This class of models include a wide range of known integrable systems,
+including the ones discussed in the introduction. One important class
+of models that does not fall in this classification are with elliptic
+R-matrices, although some of these models have slavnov products with
+determinantal representations.
+
+\begin{proposition}
+The Slavnov products \(\bm{\zeta}_j\) satisfy a system of linear
+equations.
+\end{proposition}
+
+\paragraph{\emph{Proof}} Let us first use that
+\begin{equation}
+\label{eq:scalar-prod}
+  \bra{\Psi(\bm{v})} \left(\mathcal{T}(u_j)\ket{\Psi(\bm{u}_j)} \right) =
+  \left(\bra{\Psi(\bm{v})}\mathcal{T}(u_j)\right)\ket{\Psi(\bm{u}_j)}
   \qquad j =1, \dots, n+1\; .
@@
 \begin{equation}
-  {\color{violet}\left(\bra{\Psi(\bm{v})}\mathcal{T}(u_j)\right)}\ket{\Psi(\bm{u}_j)}  =
+  \left(\bra{\Psi(\bm{v})}\mathcal{T}(u_j)\right)\ket{\Psi(\bm{u}_j)}  =
 \Lambda(u_j; \bm{v}) \bracket{\Psi(\bm{v})}{\Psi(\bm{u}_j)} = 
@@
 
-In order to simmplify the left-hand side, we expand the action of the transfer matrix on
-the off-shell as
-\todo{\tiny This point seems to be the most delicate. It does not work for
-  elliptic cases}
-\begin{equation}
-  \mathcal{T}(u_j)\ket{\Psi(\bm{u}_j)}  = \sum_{k=1}^{n+1} L_{jk} \ket{\Psi(\bm{u}_k)} \; ,
-\end{equation}
-where \(L_{jk}\) are numerical coefficients. Observe that the terms \(L_{jk}\) with
-\(j\neq k\) contain the unwanted terms. In the particular case where the algebraic
-Bethe equations are satisfied, these unwanted terms vanish and only the diagonal
-coefficient survives, that is \(L_{jj}\), and it is equal to the eigenvalue of the
-tranfer matrix.
-
-Therefore, we have
-\begin{equation}
-  \bra{\Psi(\bm{v})} {\color{violet}\left(\mathcal{T}(u_j)\ket{\Psi(\bm{u}_j)} \right)} =
+Let us now use the expansion~(\ref{eq:scalar-exp}) on the left-hand
+side of~(\ref{eq:scalar-prod}). Therefore, we have
+\begin{equation}
+  \bra{\Psi(\bm{v})} \left(\mathcal{T}(u_j)\ket{\Psi(\bm{u}_j)} \right) =
   \sum_{k=1}^{n+1} L_{jk} \bm{\zeta}_k \; .
@@
 \end{equation}
-Here is the system we were looking for. We can write this system in
-a matrix form as 
-\begin{equation}
-  \left(\bm{L} - \bm{\Lambda} \right) \cdot \bm{\zeta} = \bm{0}\; ,
+And this expression shows that the Slavnov products satisfy a linear system.
+We can write this system in a matrix form as 
+\begin{equation}
+\bm{M} \bm{\zeta} = 
+  \left(\bm{L} - \bm{\Lambda} \right) \bm{\zeta} = \bm{0}\; ,
 \end{equation}
@@
 \end{equation}
-where we have written \( \Lambda_j \equiv \Lambda(u_j; \bm{v})\), and also
+with \(\Lambda_j \equiv \Lambda(u_j; \bm{v})\), and also
 \begin{equation}
@@
 \end{subequations}
-
-The whole point now is that if this system has a solution,
-it will be written as minors of the matrix \(M\).
+ \qed
+
+There are two important consequences for us now. First of all, if we
+assume that this system has a non-trivial solution, it will be written
+as minors of the matrix \(\bm{M}\).
+
+Moreover, since the system is homogeneous, the solutions are
+determined up to multiplicative terms, that we can fix them by
+requiring that the final result gives the required tau function. In
+the original works of Foda and collaborators, e.g.~\cite{Foda:2009zz,
+  Wheeler:2010vmq}, the authors perform a series of redefinitions to
+reach the same goal.
+
+Evidently being a determinant is not enough to guarantee that the
+Slavnov product is a tau function.  In order to accomplish this
+result, we need to specify the models. Following the original
+work~\cite{Belliard:2019bfz}, we will only discuss the rational models
+-- we will see that the calculations are massive even in this simples
+case. The generalization for open boundary conditions and for
+trigonometric models is immediate, see~\cite{Slavnov:2019aba}
+for more details on the generalization.
 
@@
 
-We will now consider some concrete models. In the original
-work~\cite{Belliard:2019bfz}, the authors consider solutions with a
-rational R-mnatrix with periodic boundary conditions. Here we want to
-review the main results of this work. 
-\todo{\tiny Extend these results to the trigonometric case}
-
+We will now consider some concrete models.
 We start with an R-matrix of the form
@@
 \end{equation}
-
-Let us write the \(p\) functions \(\sigma_p\) in terms of a linearly
-\todo{Not sure if I need this!!!}
-independent basis \(\{\phi_j\}_{j=1}^n\). In this case, we have that the functions
-\(\mathcal{Y}_j(z)\) are also linearly independent and have the expansion
-\begin{equation}
-  \mathcal{Y}_j(z) = \sum_{k=1}^n \rho_k(\bm{v}_j) \phi_k(z)\; ,
-\end{equation}
-where the coefficients \( \rho_k(\bm{v}_j)\) depend on the Bethe roots \(\bm{v}_j\). 
-The functional structure of the coefficients \(\rho_k\), when written, in terms of the
-Bethe roots are the same.
-
-For example, in the case of the XXX model, \(\alpha_p(z)\sim z^{2n} + \cdots\), so
-that one can take \(\phi_j \sim z^{2j} + \cdots\), and the coefficients depend on the
-Bethe roots and inhomogeneities.
 
@@
 \item[\faCheck]  Write some explicit expressions for \(N=2\) and \(N=3\). 
+\item Discuss the Toda hierarchy case. 
 \item See the Limit \(L \to \infty\) and \(N \to \infty\) but sufficiently slower than \(L\). 

### 2025-04-29 draft.tex
finish tau function section

@@
 work~\cite{Belliard:2019bfz}, we will only discuss the rational models
--- we will see that the calculations are massive even in this simples
-case. The generalization for open boundary conditions and for
-trigonometric models is immediate, see~\cite{Slavnov:2019aba}
-for more details on the generalization.
+-- we will see that the calculations are overwhelming even in this
+simple case. The generalization for open boundary conditions and for
+trigonometric models is immediate, see~\cite{Slavnov:2019aba} for more
+details on the generalization.
 
@@
 
-We will now consider some concrete models.
-We start with an R-matrix of the form
+Let us startwith an R-matrix of the form
 \begin{equation}
@@
 \end{equation}
-where \(c\) is a constant. Moreover \(\mathbb{1}\) is the identity operator and
-\(\mathcal{P}\) is the permutation operator.
+where \(c\) is a constant, the identity operator is denoted by
+\(\mathbb{1}\) and \(\mathcal{P}\) is the permutation operator.
 
@@
 Bethe roots \(\bm{v}\), and linearly depends on every
-\(v_j\). Generically, it is written as
+\(v_j\).
+
+Generically, it is written as
 \begin{equation}
@@
 these functions all \(\alpha_p(z)\) are polynomials of degree \(2n\).
-The important point for us is that \(\alpha_p(z)\) is not
-singular when we consider the limit \(z \to v_j \in \bm{v}\),
-so does the function \(\mathcal{Y}(z; \bm{v})\).
-
-Furthermore, we have
+The important point for us is that the functions \(\alpha_p(z)\) are
+not singular when we consider the limit \(z \to v_j \in \bm{v}\), and
+that also means that \(\mathcal{Y}(z; \bm{v})\) is also regular in
+this limit.
+
+Let us also define the following product 
 \begin{equation}
@@
 \end{equation}
-and that means that each Bethe root \( v_i \in \bm{v}\) of this expression
-is a pole of \(g(z;\bm{v})\). Therefore, if \(\gamma_j\) is a contour
-containing the point \(v_j\), we have 
-\begin{equation}
-  \frac{1}{2 \pi i}\oint_{\gamma_j} \mathrm{d}z g(z; \bm{v}) = \prod_{v_i \in \bm{v}\setminus \{u_j\}} g(z, v_i)\; .
-\end{equation}
-
-The coefficients \(L_{jk}\) are given by \todo{\tiny Check references
-  1, 2 of the paper to see the trigonometric case.}
+and that means that each Bethe root \( v_i \in \bm{v}\) 
+is a pole of \(g(z;\bm{v})\). Therefore, if \(\Gamma\) is a contour
+containing all the Bethe roots \(\{v_j\}_{j=1}^n\), we have 
+\begin{equation}
+  \frac{1}{2 \pi i}\oint_{\Gamma} \mathrm{d}z g(z; \bm{v}) = \sum_{j=1}^n  \prod_{v_i \in \bm{v}\setminus \{u_j\}} g(z, v_i)\; .
+\end{equation}
+Furthermore, the coefficients \(L_{jk}\) are given by
 \begin{equation}
@@
 and from this expression one can calculate the matrix \(\bm{M}\).
-Finally, the authors also show that if \(\det (\bm{M}) = 0 \) and
-\(\mathrm{rank}(\bm{M}) = n\), then, the Slavnov products are given by
+
+It has also been shown~\cite{Belliard:2019bfz} that if \(\det
+(\bm{M}) = 0 \) and \(\mathrm{rank}(\bm{M}) = n\), then, the Slavnov
+products are given by
 \begin{equation}
@@
 \end{equation}
-where \(\phi(\bm{v})\) is a function of the Bethe roots, and also
-\begin{equation}
-  \tilde{\Delta}(\bm{u}_\ell) = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{c}{u_j - u_k}\; . 
-\end{equation}
-Therefore, we can absorb the product of the constant \(c\) into
-a unique constant \(c_0\) so that 
-\begin{equation}
+where \(\phi(\bm{v})\) is a function of the Bethe roots and
+\begin{equation}
+  \tilde{\Delta}(\bm{u}_\ell) = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{c}{u_j - u_k}\quad \Rightarrow \quad
 \frac{\tilde{\Delta}(\bm{u}_\ell)}{c_0} = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{1}{u_j - u_k}\; , 
 \end{equation}
-that is the inverse of the Vandermonde determinant
+where we have absorbed the product of \(c\) into a new constant \(c_0\). 
+All in all, \(\tilde{\Delta}(\bm{u}_\ell)/c_0\) is the inverse of the Vandermonde determinant
 \(\Delta(\bm{u}_\ell) = \prod_{j>k}(u_j - u_k)\).
-Finally, we have  that \(\hat{\Omega}_\ell\) are minors of the matrix \(\bm{\Omega}\) with the \(\ell\)-th
-column excluded, that is 
+
+Additionally, the matrices \(\hat{\Omega}_\ell\) are minors of
+\(\bm{\Omega}\) with the \(\ell\)-th column excluded, in other words,
 \begin{equation}
@@
 \begin{equation}
-  \Omega_{jk} = g(u_k, v_j) \mathcal{Y}(u_k; \{u_k, \bm{v}_j\})
-  \qquad j= 1, \dots, n\; , \quad k =1, \dots, n+1
-\end{equation}
-
-All in all, we have an expression of the
-form
-\begin{equation}
+  \Omega_{jk}(u_k; \bm{v}) = g(u_k, v_j) \mathcal{Y}(u_k; \{u_k, \bm{v}_j\})\; ,
+  \quad j= 1, \dots, n\; , \quad k =1, \dots, n+1\; .
+\end{equation}
+
+All in all, we have an expression of the form
+\begin{equation}
+  \label{eq:slavnov-tau}
   \bm{\tau}_\ell(\bm{u}_\ell; \bm{v}) \equiv \frac{1}{c_0}\frac{\bm{\zeta}_\ell}{\phi(\bm{v})}
-  = \frac{\det_{k\neq \ell} \Omega_{jk}}{\Delta(\bm{u}_\ell)}
-\end{equation}
-
-Let us now simplify these thing a little bit. First of all, we need to
-observe that we can define \(n\) functions \(\Omega_j(z)\) of the form 
+  = \frac{\hat{\Omega}_{\ell}}{\Delta(\bm{u}_\ell)} \; .
+\end{equation}
+This is the most important result for us, and our goal now is to show
+that it is a tau-function of the KP-hierarchy.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Tau functions}
+
+In order to proceed, let us simplify the notation and organize the
+results we described before. First of all, we need to observe
+that we can define \(n\) functions \(\Omega_j(z)\) of the form
 \begin{equation}
@@
 \begin{equation}
-  \sigma_p^{(n)}(\{z,\bm{v}_j\}) = \sigma_p^{(n-1)}(\bm{v}_j) + z \sigma_{p-1}^{(n-1)}(\bm{v}_j) \; , 
-\end{equation}
-Therefore,
+  \sigma_p^{(n)}(\{z,\bm{v}_j\}) = \sigma_p^{(n-1)}(\bm{v}_j) + z \sigma_{p-1}^{(n-1)}(\bm{v}_j) \; . 
+\end{equation}
+
+Let us also denote the functions
 \begin{equation}
   \label{eq:y-functions-alpha}
-  \mathcal{Y}_j(z)  = 
+  \mathcal{Y}_j(z)  \equiv  \mathcal{Y}(z; \{z,\bm{v}_j\})  = 
 \sum_{p=0}^{n} \alpha_p(z)
-  \left(\sigma_p^{(n-1)}(\bm{v}_j) + z \sigma_{p-1}^{(n-1)}(\bm{v}_j) \right) 
-\end{equation}
-where we have denoted \( \mathcal{Y}(z; \{z,\bm{v}_j\}) \equiv \mathcal{Y}_j(z)\). 
-Observe that what defines the functions \(\mathcal{Y}_j(z)\) is the absence of the
-\(j\)-th Bethe root \(v_j\).
-
+  \left(\sigma_p^{(n-1)}(\bm{v}_j) + z \sigma_{p-1}^{(n-1)}(\bm{v}_j) \right) \; .
+\end{equation}
+Observe that the defining property of these functions
+\(\mathcal{Y}_j(z)\) is the absence of the \(j\)-th Bethe root
+\(v_j\).
 Using that the elementary symmetric polynomials also satisfy \(\sigma_n^{(n-1)}(\bm{v}_j)=0\)
@@
   \sum_{p=0}^{n-1} 
-   \left(\alpha_p(z) + z \alpha_{p+1}(z) \right) \sigma_p^{(n-1)}(\bm{v}_j) 
-\end{equation}
-
-We finally have 
-\begin{equation}
-  \Omega_{j}(z; \bm{v}) = -\frac{c}{v_j - z} \mathcal{Y}_j(z) \; .
-\end{equation}
-where we have denoted \( \mathcal{Y}(z; \{z,\bm{v}_j\}) \equiv \mathcal{Y}_j(z)\).
-It is also convenient to consider \(c=1\).
-
-%Finally, let us now consider this function in the neighborhood of the Bether root \(v_j\). We find 
-%\begin{equation}
-%  \Omega_j(z; \bm{v}) \simeq \frac{c}{z - v_j}
-%\mathcal{Y}(v_j; \bm{v})\qquad j =1, \dots, n\; .
-%\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Tau functions}
-
-Therefore, we can write the matrix \(\bm{\Omega}\) as 
+   \left(\alpha_p(z) + z \alpha_{p+1}(z) \right) \sigma_p^{(n-1)}(\bm{v}_j) \; .
+\end{equation}
+
+Putting all these facts together, we have the functions
+\begin{equation}
+  \Omega_{j}(z; \bm{v}) = \frac{c}{z - v_j} \mathcal{Y}_j(z) \; .
+\end{equation}
+It is also convenient to consider \(c=1\), consequently \(c_0=1\).
+
+\subsection{Alternant expression for the Slavnov products}
+
+The matrix \(\bm{\Omega}\) can be written as
 \begin{equation}
@@
     \vdots & \vdots & \vdots & \vdots \\
-    \Omega_n(u_1) & \dots & \Omega_n(u_n) & \Omega_n(u_{n+1})
+    \Omega_n(u_1) & \dots & \Omega_n(u_n) & \Omega_n(u_{n+1})\; .
   \end{pmatrix}
 \end{equation}
-and we also define the \(n\times n\) matrices \(\bm\Omega^{(\ell)}(\bm{u}_\ell; \bm{v})\),
+From this expression, we can also define a set of \(n\) square matrices
+\(\bm\Omega^{(\ell)}(\bm{u}_\ell; \bm{v})\),
 \(\ell = 1, \dots, n+1\), removing the \(\ell\)-th column of
@@
     \vdots & \dots & \vdots & \vdots & \dots & \vdots \\
-    \Omega_n(u_1) & \dots & \Omega_n(u_{\ell-1}) & \Omega_n(u_{\ell+1})&\dots & \Omega_n(u_{n+1})\; .
-  \end{pmatrix}
-\end{equation}
-
-Putting these facts together, we write the functions
+    \Omega_n(u_1) & \dots & \Omega_n(u_{\ell-1}) & \Omega_n(u_{\ell+1})&\dots & \Omega_n(u_{n+1})
+  \end{pmatrix}\; .
+\end{equation}
+
+Finaly, we can write~(\ref{eq:slavnov-tau}) as 
 \begin{equation}
@@
 \end{equation}
-where \((\bm{u}_\ell)_k \) is the k-th component of the vector
-\(\bm{u}_\ell\). These functions are tau functions of the KP
-hierarchy.  We have also omitted the dependence on the Bethe roots
-\(\bm{v}\). The most important aspect now is that the poles of this
-tau function are exactly the Bethe roots of the integrable model.
-
-It is well documented that the functions defined as
-in~(\ref{eq:slavnov-tau-functions}) are tau functions of the
-KP-hierachy, see~\cite{Araujo:2021ghu} and references therein, in
-particular~\cite{Kharchev:1991cy}.
-
-In fact, we can focus all our attention on a particular function. Therefore,
-for a fixed \(\ell\), we define the vector \( \bm{z} \equiv \bm{u}_\ell\).
-Consequently, 
-\begin{equation}
-\begin{split}
-\label{eq:tau-function}
+where \((\bm{u}_\ell)_k \) is the \(k\)-th component of the vector
+\(\bm{u}_\ell\).  Therefore, for a fixed \(\ell\), we define the
+vector \( \bm{z} \equiv \bm{u}_\ell\).  Consequently,
+\begin{equation}
+\begin{split}
+\label{eq:slav-tau-function}
   \bm{\tau}(\bm{z}, \bm{v})
@@
 All these tau functions have the form of an \emph{alternant
-determinant}.  Henceforth, we will only refer to the matrix
+determinant} devided by the Vandermonde determinant.
+
+It is well documented that the functions defined as
+in~(\ref{eq:slav-tau-function}) are tau functions of the
+KP-hierachy, see~\cite{Araujo:2021ghu} and references therein, in
+particular~\cite{Kharchev:1991cy}. Consequently, these functions are
+tau functions.
+
+Henceforth, we will only refer to the matrix
 \(\bm{\Omega}\) defined by the components
@@
 
-\subsection{Pole structure}
-
-We now want to analyse the pole structure of
-\(\Delta(\bm{z})\tau(\bm{z}, \bm{v})\).  First of all, one should
-observe that the Bethe roots \(\bm{v}\) appear as poles of the
-coefficients \(\bm{z}\). Moreover, lets us consideer here that the
+\subsection{Tau functions expansion of the Slavnov product}
+
+We can immediately observe that the poles of the tau
+function~(\ref{eq:slav-tau-function}) are exactly the Bethe roots of
+the integrable model.  We now want to analyse this pole structure of
+\(\Delta(\bm{z})\tau(\bm{z}, \bm{v})\).  Let us consider that the
 Bethe roots are not degenerate, that is, if \(j \neq k\), then \(v_j
@@
 \begin{equation}
+\label{eq:minor-expansion}
 \begin{split}
@@
 \end{equation}
-where \(\hat{\Omega}_{j,l} \) is the \((j, l)\) minor of \(\bm{\Omega}\).
-
-Now, we can extract the residue of the tau function for \(z_l\) at the point \(v_j\), that is
+where \(\hat{\Omega}_{j,l} \) is the \((j, l)\) minor of
+\(\bm{\Omega}\).  Now, we can extract the residue of the tau function
+for \(z_l\) at the point \(v_j\), that is
 \begin{equation}
@@
 
+\begin{subequations}
 Let us now decompose the Vandermonde determinant as
@@
 \end{equation}
-where \(\bm{z}_l = \bm{z}\setminus \{z_l\} = (z_1, \dots, z_{l-1}, z_{l+1}, \dots, z_n) \).
-\todo[inline]{I wand to verify that this is correct}
-We can define the function
+where \(\bm{z}_l = \bm{z}\setminus \{z_l\} = (z_1, \dots, z_{l-1},
+z_{l+1}, \dots, z_n) \), and we also define the function
 \begin{equation}
@@
 \end{equation}
-
-Let us now write
-\begin{equation}
+\end{subequations}
+
+Inserting this decomposition into~(\ref{eq:minor-expansion}), we find
+\begin{equation}
+\label{eq:minor-expansion-2}
   \bm{\tau}(\bm{z}, \bm{v})
@@
 
-When we define the set of functions
+When we define the \(n\) sets of functions
 \begin{equation}
@@
     \hat{\bm{\Omega}}_{(j)}(z) & = \left(\Omega_1(z), \dots, \Omega_{j-1}(z), \Omega_{j+1}(z), \dots, \Omega_n(z) \right)\; ,
-  \end{split}
-\end{equation}
-we can simplify the tau function expansion even further. Then
+    \quad j =1, \dots, n\; ,
+  \end{split}
+\end{equation}
+so that we can simplify the minor
+expansion~(\ref{eq:minor-expansion-2}) even further; that is
 \begin{equation}
@@
 \end{equation}
-where 
+where \(\hat{\bm{\Omega}}_{(j)r}\) is the \(r\)-th component of
+\(\hat{\bm{\Omega}}_{(j)}\) and \(\hat{z}_{(l)s}\) is the \(s\)-th
+component of \(\bm{z}_{(l)}\). Moreover, in the second line we have
+defined the object
 \begin{equation}
@@
 close to \(v_k \in \bm{v}_j\).
+
+Therefore, we have the interesting result that the rresidues of the
+tau function \(\tau(\bm{z}, \bm{v})\) for \(z_j\) approaching the
+Bethe root \(v_j\) is proportional to a tau function.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Homogeneous limit and Wronskian formula}
+
+We the previous section we have discussed the limit where the
+parameters \(\bm{z}\) approach the Bethe roots \(\bm{v}\).  We now
+want to consider the limit where \(\bm{z}\) tend to a single variable,
+say \(z_k\to z_1\), \(k=2,\dots, n\).
+
+Let us first consider the case
+\(z_2 \to z_1\), then
+\begin{subequations}
+\begin{equation}
+  \bm{\tau}(\bm{z}, \bm{v}) = \frac{1}{\Delta(\bm{z})}
+  \det
+  \begin{pmatrix}
+    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}  & \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1} + (z_2 - z_1) \frac{\mathcal{Y}_1^{(1)}(z_1)}{z_1 - v_1}
+    + \mathcal{O}(\delta^2) &
+    \frac{\mathcal{Y}_1(z_3)}{z_3 - v_1} & \dots & \frac{\mathcal{Y}_1(z_n)}{z_n - v_1}\\
+    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} & \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} + (z_2 - z_1) \frac{\mathcal{Y}_2^{(1)}(z_1)}{z_1 - v_2} 
+    + \mathcal{O}(\delta^2) &
+    \frac{\mathcal{Y}_2(z_3)}{z_3 - v_2} &  \dots & \frac{\mathcal{Y}_2(z_n)}{z_n - v_2}\\
+    &  \vdots & & \\
+    \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} & \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} + (z_2 - z_1) \frac{\mathcal{Y}_n^{(1)}(z_1)}{z_1 - v_n} 
+    + \mathcal{O}(\delta^2) &
+    \frac{\mathcal{Y}_n(z_3)}{z_3 - v_n} &  \dots & \frac{\mathcal{Y}_n(z_n)}{z_n - v_n}
+  \end{pmatrix}
+\end{equation}
+where we have written \(z_2 - z_1 = \delta \to 0\). Moreover, we write
+\(\mathcal{Y}^{(n)}(z)\) as the nth derivative with respect its
+argument. Now one can immediatelly see that the second column is the
+first column plus terms multiplied by the factor \(\delta = z_2 -
+z_1\). Using elementary operations on the column, we find
+\begin{equation}
+  \bm{\tau}_h(\bm{z}, \bm{v}) = \lim_{z_2 \to z_1}\frac{(z_2 - z_1)}{\Delta(\bm{z})}
+  \det
+  \begin{pmatrix}
+    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}  & \frac{\mathcal{Y}_1^{(1)}(z_1)}{z_1 - v_1} &
+    \frac{\mathcal{Y}_1(z_3)}{z_3 - v_1} & \dots & \frac{\mathcal{Y}_1(z_n)}{z_n - v_1}\\
+    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} & \frac{\mathcal{Y}_2^{(1)}(z_1)}{z_1 - v_2} &
+    \frac{\mathcal{Y}_2(z_3)}{z_3 - v_2} &  \dots & \frac{\mathcal{Y}_2(z_n)}{z_n - v_2}\\
+    &  \vdots & & \\
+    \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} & \frac{\mathcal{Y}_n^{(1)}(z_1)}{z_1 - v_n} &
+    \frac{\mathcal{Y}_n(z_3)}{z_3 - v_n} &  \dots & \frac{\mathcal{Y}_n(z_n)}{z_n - v_n}
+  \end{pmatrix}\; .
+\end{equation}
+We can now repeat the same ideas for \(z_3\to z_1=z_2\). We find that
+the third column is the first plus the second and the derivatives
+multiplied by the factor \(\delta^2\sim (z_3 - z_2)(z_3 - z_1)\). All in all, we have
+\begin{equation}
+  \bm{\tau}_h(\bm{z}, \bm{v}) = \lim_{z_2, z_3 \to z_1}\frac{(z_2 - z_1)(z_3 - z_1)(z_3 - z_2)}{\Delta(\bm{z})}
+  \det
+  \begin{pmatrix}
+    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}  & \frac{\mathcal{Y}_1^{(1)}(z_1)}{z_1 - v_1} &
+    \frac{\mathcal{Y}^{(2)}_1(z_1)}{z_1 - v_1} & \dots & \frac{\mathcal{Y}_1(z_n)}{z_n - v_1}\\
+    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} & \frac{\mathcal{Y}_2^{(1)}(z_1)}{z_1 - v_2} &
+    \frac{\mathcal{Y}_2^{(2)}(z_1)}{z_1 - v_2} &  \dots & \frac{\mathcal{Y}_2(z_n)}{z_n - v_2}\\
+    &  \vdots & & \\
+    \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} & \frac{\mathcal{Y}_n^{(1)}(z_1)}{z_1 - v_n} &
+    \frac{\mathcal{Y}_n^{(2)}(z_1)}{z_1 - v_n} &  \dots & \frac{\mathcal{Y}_n(z_n)}{z_n - v_n}
+  \end{pmatrix}\; .
+\end{equation}
+Repeating the same idea for all columns, we get that the multiplicative factor cancels out, and
+that the homogeneous limit gives 
+\begin{equation}
+  \bm{\tau}_h(z_1, \bm{v}) =
+  \det
+  \begin{pmatrix}
+    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}  & \frac{\mathcal{Y}_1^{(1)}(z_1)}{z_1 - v_1} &
+    \frac{\mathcal{Y}^{(2)}_1(z_1)}{z_1 - v_1} & \dots & \frac{\mathcal{Y}_1^{(n-1)}(z_1)}{z_1 - v_1}\\
+    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} & \frac{\mathcal{Y}_2^{(1)}(z_1)}{z_1 - v_2} &
+    \frac{\mathcal{Y}_2^{(2)}(z_1)}{z_1 - v_2} &  \dots & \frac{\mathcal{Y}_2^{(n-1)}(z_1)}{z_1 - v_2}\\
+    &  \vdots & & \\
+    \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} & \frac{\mathcal{Y}_n^{(1)}(z_1)}{z_1 - v_n} &
+    \frac{\mathcal{Y}_n^{(2)}(z_1)}{z_1 - v_n} &  \dots & \frac{\mathcal{Y}^{(n-1)}_n(z_1)}{z_1 - v_n}
+  \end{pmatrix}\; .
+\end{equation}
+
+Finally, let we write \(z_1 \equiv w\) and using elementary row operations we find
+\begin{equation}
+  \bm{\tau}_h(w, \bm{v}) =
+  \frac{1}{\prod_{k=1}^n(w - v_k)}
+  \mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2, \dots, \mathcal{Y}_n](w)
+  \; .
+\end{equation}
+that agrees with the results we obtained above. 
+\end{subequations}
 
@@
 \end{equation}
-
-\subsubsection{Homogeneous limit and Wronskian formula}
-
-We now want to consider the limit where \(z_k\to z_1\), \(k=2,\dots, n\). 
-Let us first consider the case \(z_2 \to z_1\), then
-\begin{subequations}
-\begin{equation}
-  \bm{\tau}(\bm{z}, \bm{v}) = \frac{1}{\Delta(\bm{z})}
-  \det
-  \begin{pmatrix}
-    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}  & \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1} + (z_2 - z_1) \frac{\mathcal{Y}_1^{(1)}(z_1)}{z_1 - v_1}
-    + \mathcal{O}(\delta^2) &
-    \frac{\mathcal{Y}_1(z_3)}{z_3 - v_1} & \dots & \frac{\mathcal{Y}_1(z_n)}{z_n - v_1}\\
-    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} & \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} + (z_2 - z_1) \frac{\mathcal{Y}_2^{(1)}(z_1)}{z_1 - v_2} 
-    + \mathcal{O}(\delta^2) &
-    \frac{\mathcal{Y}_2(z_3)}{z_3 - v_2} &  \dots & \frac{\mathcal{Y}_2(z_n)}{z_n - v_2}\\
-    &  \vdots & & \\
-    \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} & \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} + (z_2 - z_1) \frac{\mathcal{Y}_n^{(1)}(z_1)}{z_1 - v_n} 
-    + \mathcal{O}(\delta^2) &
-    \frac{\mathcal{Y}_n(z_3)}{z_3 - v_n} &  \dots & \frac{\mathcal{Y}_n(z_n)}{z_n - v_n}
-  \end{pmatrix}
-\end{equation}
-where we have written \(z_2 - z_1 = \delta \to 0\). Moreover, we write
-\(\mathcal{Y}^{(n)}(z)\) as the nth derivative with respect its
-argument. Now one can immediatelly see that the second column is the
-first column plus terms multiplied by the factor \(\delta = z_2 -
-z_1\). Using elementary operations on the column, we find
-\begin{equation}
-  \bm{\tau}_h(\bm{z}, \bm{v}) = \lim_{z_2 \to z_1}\frac{(z_2 - z_1)}{\Delta(\bm{z})}
-  \det
-  \begin{pmatrix}
-    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}  & \frac{\mathcal{Y}_1^{(1)}(z_1)}{z_1 - v_1} &
-    \frac{\mathcal{Y}_1(z_3)}{z_3 - v_1} & \dots & \frac{\mathcal{Y}_1(z_n)}{z_n - v_1}\\
-    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} & \frac{\mathcal{Y}_2^{(1)}(z_1)}{z_1 - v_2} &
-    \frac{\mathcal{Y}_2(z_3)}{z_3 - v_2} &  \dots & \frac{\mathcal{Y}_2(z_n)}{z_n - v_2}\\
-    &  \vdots & & \\
-    \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} & \frac{\mathcal{Y}_n^{(1)}(z_1)}{z_1 - v_n} &
-    \frac{\mathcal{Y}_n(z_3)}{z_3 - v_n} &  \dots & \frac{\mathcal{Y}_n(z_n)}{z_n - v_n}
-  \end{pmatrix}\; .
-\end{equation}
-We can now repeat the same ideas for \(z_3\to z_1=z_2\). We find that
-the third column is the first plus the second and the derivatives
-multiplied by the factor \(\delta^2\sim (z_3 - z_2)(z_3 - z_1)\). All in all, we have
-\begin{equation}
-  \bm{\tau}_h(\bm{z}, \bm{v}) = \lim_{z_2, z_3 \to z_1}\frac{(z_2 - z_1)(z_3 - z_1)(z_3 - z_2)}{\Delta(\bm{z})}
-  \det
-  \begin{pmatrix}
-    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}  & \frac{\mathcal{Y}_1^{(1)}(z_1)}{z_1 - v_1} &
-    \frac{\mathcal{Y}^{(2)}_1(z_1)}{z_1 - v_1} & \dots & \frac{\mathcal{Y}_1(z_n)}{z_n - v_1}\\
-    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} & \frac{\mathcal{Y}_2^{(1)}(z_1)}{z_1 - v_2} &
-    \frac{\mathcal{Y}_2^{(2)}(z_1)}{z_1 - v_2} &  \dots & \frac{\mathcal{Y}_2(z_n)}{z_n - v_2}\\
-    &  \vdots & & \\
-    \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} & \frac{\mathcal{Y}_n^{(1)}(z_1)}{z_1 - v_n} &
-    \frac{\mathcal{Y}_n^{(2)}(z_1)}{z_1 - v_n} &  \dots & \frac{\mathcal{Y}_n(z_n)}{z_n - v_n}
-  \end{pmatrix}\; .
-\end{equation}
-Repeating the same idea for all columns, we get that the multiplicative factor cancels out, and
-that the homogeneous limit gives 
-\begin{equation}
-  \bm{\tau}_h(z_1, \bm{v}) =
-  \det
-  \begin{pmatrix}
-    \frac{\mathcal{Y}_1(z_1)}{z_1 - v_1}  & \frac{\mathcal{Y}_1^{(1)}(z_1)}{z_1 - v_1} &
-    \frac{\mathcal{Y}^{(2)}_1(z_1)}{z_1 - v_1} & \dots & \frac{\mathcal{Y}_1^{(n-1)}(z_1)}{z_1 - v_1}\\
-    \frac{\mathcal{Y}_2(z_1)}{z_1 - v_2} & \frac{\mathcal{Y}_2^{(1)}(z_1)}{z_1 - v_2} &
-    \frac{\mathcal{Y}_2^{(2)}(z_1)}{z_1 - v_2} &  \dots & \frac{\mathcal{Y}_2^{(n-1)}(z_1)}{z_1 - v_2}\\
-    &  \vdots & & \\
-    \frac{\mathcal{Y}_n(z_1)}{z_1 - v_n} & \frac{\mathcal{Y}_n^{(1)}(z_1)}{z_1 - v_n} &
-    \frac{\mathcal{Y}_n^{(2)}(z_1)}{z_1 - v_n} &  \dots & \frac{\mathcal{Y}^{(n-1)}_n(z_1)}{z_1 - v_n}
-  \end{pmatrix}\; .
-\end{equation}
-
-Finally, let we write \(z_1 \equiv w\) and using elementary row operations we find
-\begin{equation}
-  \bm{\tau}_h(w, \bm{v}) =
-  \frac{1}{\prod_{k=1}^n(w - v_k)}
-  \mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2, \dots, \mathcal{Y}_n](w)
-  \; .
-\end{equation}
-that agrees with the results we obtained above. 
-\end{subequations}
 

### 2025-04-30 draft.tex
finish homogeneous limit and examples

@@
 \begin{abstract}
-  ...
+One important ingredient in the Algebraic Bethe Ansatz is the scalar
+product of Bethe states.  There are many important results on this
+topic and references therein, but here we turn our attention to the
+well known fact that scalars products in the algebraic Bethe ansatz
+can be written as determinants.  More specifically, we will
+investigate a particular type of correlation functions in quantum
+integrable spin chains, the so called \emph{Slavnov product} These
+objects can be seen as building blocks of more sofisticated
+correlation functions and are instrumental in the study of norms of
+Bethe wave functions But more importantly for our present discussion,
+Slavnov products seem to be a bridge connecting quantum and classical
+integrable system.
 \end{abstract}
@@
 
-\setcounter{tocdepth}{1}
+\setcounter{tocdepth}{2}
 \tableofcontents
@@
 
-\section{Homogeneous limit and Wronskian formula}
-
-We the previous section we have discussed the limit where the
+\section{Homogeneous limit}
+
+In the previous section we have discussed the limit where the
 parameters \(\bm{z}\) approach the Bethe roots \(\bm{v}\).  We now
@@
 
-Let us first consider the case
-\(z_2 \to z_1\), then
+\subsection{Wronskian formula}
+
+Let us first consider the case where \(z_2 \to z_1\). We consider a
+series expansion about \(z_1\), and the second column of~(\ref{eq:slav-tau-function}) becomes
 \begin{subequations}
@@
 \end{equation}
-where we have written \(z_2 - z_1 = \delta \to 0\). Moreover, we write
-\(\mathcal{Y}^{(n)}(z)\) as the nth derivative with respect its
-argument. Now one can immediatelly see that the second column is the
-first column plus terms multiplied by the factor \(\delta = z_2 -
+where we have written \(z_2 - z_1 = \delta \to 0\), and we denote by
+\(\mathcal{Y}^{(n)}(z)\) the \(n\)-th derivative of a
+\(\mathcal{Y}(z)\) with respect its argument.
+
+Now one can immediatelly see that the second column is the first
+column plus terms multiplied by the factor \(\delta = z_2 -
 z_1\). Using elementary operations on the column, we find
@@
 We can now repeat the same ideas for \(z_3\to z_1=z_2\). We find that
-the third column is the first plus the second and the derivatives
-multiplied by the factor \(\delta^2\sim (z_3 - z_2)(z_3 - z_1)\). All in all, we have
+the third column is the sum of the first and second columns, and
+derivatives multiplied by the factor \(\delta^2\sim (z_3 - z_2)(z_3 -
+z_1)\). All in all, we have
 \begin{equation}
@@
 \end{equation}
-Repeating the same idea for all columns, we get that the multiplicative factor cancels out, and
+
+Repeating the same idea for all columns, we get that the
+multiplicative factor cancels out the Vandermonde determinant, and
 that the homogeneous limit gives
@@
 \end{equation}
-that agrees with the results we obtained above. 
 \end{subequations}
-
-\subsection{Examples} Let us now consider the cases \(n=2, 3\) (the case \(n=1\) is trivial)
+The interesting aspect of this expression is that the poles of this
+function are exactly the Bethe roots, and they are easily built from
+the Algebraic Bethe ansatz. Additionally, the functions
+\(\{\mathcal{Y}_j(w)\}_{j=1}^n\) are linearly independent if and only
+if the Bethe roots are non-degenerate.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Examples} Let us now consider the cases \(n=2, 3\) (the case \(n=1\) is trivial)
 to gain some understanding of the problem.
 
-\subsubsection{n=2} In this case, we have \(\mathcal{Y}_j\) for \(j=1,2\) and two Bethe roots
+\subsection{n=2} In this case, we have \(\mathcal{Y}_j\) for \(j=1,2\) and two Bethe roots
 \(\bm{v} = (v_1, v_2)\). Moreover, we have the two sets \(\bm{v}_1 =
@@
 \end{equation}
-Thefore, we find
-\begin{equation}
-  \bm{\tau}(z_1, z_2; v_1 , v_2) = \frac{1}{z_2 - z_1}
-  \left(\frac{\mathcal{Y}_1(z_1) \mathcal{Y}_2(z_2)}{(z_1 - v_1)(z_2 - v_2)} - 
-  \frac{\mathcal{Y}_1(z_2) \mathcal{Y}_2(z_1)}{(z_1 - v_2)(z_2 - v_1)} 
-  \right)
+Consequently, we find
+\begin{equation}
+\begin{split}
+  \bm{\tau}(z_1, z_2; v_1 , v_2)
+  & = \frac{1}{z_2 - z_1} \left(\frac{\mathcal{Y}_1(z_1) \mathcal{Y}_2(z_2)}{(z_1 - v_1)(z_2 - v_2)} - 
+  \frac{\mathcal{Y}_1(z_2) \mathcal{Y}_2(z_1)}{(z_1 - v_2)(z_2 - v_1)} \right)\\
+  & = \frac{1}{z_2 - z_1}
+  \left(
+  \frac{\mathcal{Y}_1(z_1)}{(z_1 - v_1)} \widetilde{\bm{\tau}}_1(z_2, v_1, v_2) - 
+  \frac{\mathcal{Y}_2(z_1)}{(z_1 - v_2)} \widetilde{\bm{\tau}}_2(z_2, v_1, v_2) \right)
+\end{split}
+\end{equation}
+where 
+\begin{equation}
+ \widetilde{\bm{\tau}}_1(z_2, v_1, v_2) = \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} \quad \textrm{and}  \qquad 
+ \widetilde{\bm{\tau}}_2(z_2, v_1, v_2) = \frac{\mathcal{Y}_1(z_2)}{(z_2 - v_1)}  \; .
 \end{equation}
 \end{subequations}
-One interesting case happens for \(z_2 \to z_1\equiv w\), in this case
-it is easy to show that
+From this expression, it is easy to extract the residues of \(z_1\)
+about one of the Bethe roots.
+
+It is easy to see that the homogeneous limit, that is \(z_2 \to z_1\equiv
+w\) gives
 \begin{equation}
@@
 \end{equation}
-where \(\mathcal{W}[\mathcal{Y}_1, \dots, \mathcal{Y}_n](w)\) denotes the
-Wronskian of the functions \(\{\mathcal{Y}_j(w)\}_{j=1}^n\), in our
-case, we have \(n=2\). In this case, one can observe that these
-functions are linearly independent as long as \(v_2 \neq v_1\), what
-is guaranteed by the hypothesis that the Bethe roots are different.
-
-\subsubsection{n=3} Now we have \(\mathcal{Y}_j\) for \(j=1,2,3\) and three Bethe roots
+It is also elementary to see that the functions \(\{\mathcal{Y}_1,
+\mathcal{Y}_2\}\) are linearly independent as long as \(v_2 \neq
+v_1\), what is guaranteed by the hypothesis that the Bethe roots are
+different.
+
+\subsection{n=3} Now we have \(\mathcal{Y}_j\) for \(j=1,2,3\) and three Bethe roots
 \(\bm{v} = (v_1, v_2, v_3)\). Moreover, we have the sets \(\bm{v}_1 = (v_2, v_3)\), \(\bm{v}_2 = (v_1, v_3)\)
@@
   & = (\alpha_0(z) + z \alpha_1(z))\sigma_0^{(2)}(\bm{v}_j)   + (\alpha_1(z) + z \alpha_2(z))\sigma_1^{(2)}(\bm{v}_j)  + \\
-  & \quad + (\alpha_2(z) + z \alpha_3(z))\sigma_2^{(2)}(\bm{v}_j) 
-\end{split}
-\end{equation}
-Moreover, one can also use the explicit expressions 
+  & \quad + (\alpha_2(z) + z \alpha_3(z))\sigma_2^{(2)}(\bm{v}_j) \; ,
+\end{split}
+\end{equation}
+with the explicit expressions 
 \begin{equation}
@@
   \sigma_1^{(2)}(x, y) = x + y\; ,\qquad 
-  \sigma_2^{(2)}(x, y) = x^2 + xy  + y^2\; , 
-\end{equation}
-to determine the functions \(\mathcal{Y}_j(z)\) for \(j=1,2,3\).
+  \sigma_2^{(2)}(x, y) = x^2 + xy  + y^2\; . 
+\end{equation}
 
@@
         \end{bmatrix} 
-  \right]
-  \end{split}
-\end{equation}
-That we can organize as
+  \right] \; .
+  \end{split}
+\end{equation}
+We organize this expression as
 \begin{equation}
@@
 
-Finally, we conclude that
+Finally, we conclude that that basis tau functions are
 \begin{subequations}
@@
         \frac{\mathcal{Y}_2(z_2)}{(z_2 - v_2)} & \frac{\mathcal{Y}_2(z_3)}{(z_3 - v_2)}
-        \end{bmatrix} 
+        \end{bmatrix} \; .
   \end{equation}
@@
   \tilde{\bm{\tau}}_3(w; v_1 , v_2, v_3) & = \frac{1}{(w - v_1)(w - v_2)}\mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2](w)
-  \end{split}\; .
+  \; .
+  \end{split}
 \end{equation}
@@
 \begin{equation}
-  \bm{\tau}(w; v_1 , v_2, v_3)
+  \bm{\tau}(w; v_1 , v_2, v_3) = 
   \frac{1}{(w - v_1)(w - v_2)(w - v_3)} \mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2, \mathcal{Y}_3](w)\; .
@@
 
+Of course we can keep the calculations for other cases, but now it is obvious that
+this explicit analysis become cumbersome very early. It also explains why we
+keep our analysis restricted to the Rational cases.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We now want to write the Slavnov products we defined above in terms of the following 
-coordinates
+This section deals with the properties of the Baker-Akhiezer functions
+associated to the above tau functions. There are some interesting
+aspects of these tau functions that deserve further analysis, and here
+we just touch some of these aspects.
+
+Let us first start with some rewriting of the tau functions above.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Integral representation of the tau functions}
+
+We now want to write the Slavnov products we defined above in terms of
+the following coordinates
 \begin{equation}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Integral representation of the tau functions}
-
-It is easy to show, see~\cite{Araujo:2021ghu} and references therein,
-that that the tau function~(\ref{eq:tau-function}) admits an integral
-representation of the form
+\begin{proposition}
+The tau function~(\ref{eq:tau-function}) admits an integral
+representation, see ~\cite{Araujo:2021ghu} and references therein,
+of the form
 \begin{subequations}
@@
 encloses all poles except the Bethe root \(v_k\).
-
-In terms of the \(z\)-coordinates, we have
+\end{subequations}
+
+In terms of the \(z\)-coordinates, the tau functions becomes
 \begin{equation}
@@
 \end{equation}
-\end{subequations}
 Now, it is easy to see that \(w =0\) is not a pole.
@@
 \(n\to \infty\).
-
+\end{proposition}
+
+\paragraph{\emph{Proof}}
 There are some minor differences between our calculations and the
-original references. First, we need to be carefull with the
-integration contour \(\gamma_k\). For this reason, we want to
-show explicitly this result.
+original references; namely, the integration contour \(\gamma_k\) and
+sign conventions. For this reason, we want to show
+explicitly this result.
 
@@
 \end{subequations}
-
 Putting all these facts together, we finally see that 
-\(\bm{\tau}(\bm{z}, \bm{v}) = \det\bm{\mathcal{K}}\).
+\(\bm{\tau}(\bm{z}, \bm{v}) = \det\bm{\mathcal{K}}\). \qed
 

### 2025-05-02 draft.tex
finish paper

@@
 
-\paragraph{\emph{Proof}} Let us first use that
+\paragraph{\textbf{\emph{Proof}}} Let us first use that
 \begin{equation}
@@
 
-This section deals with the properties of the Baker-Akhiezer functions
-associated to the above tau functions. There are some interesting
-aspects of these tau functions that deserve further analysis, and here
-we just touch some of these aspects.
-
-Let us first start with some rewriting of the tau functions above.
+This section deals with some properties of the Baker-Akhiezer
+functions associated to the tau functions we found above.  Many
+aspects of these functions deserve a thorough examination, but here we
+investigagte just the most immediate aspects.
 
@@
 \end{equation}
-the so called, Miwa coordinates.
-
-Let us also define
+the so called Miwa coordinates.
+
+We define
+\begin{equation}
+  \xi(\bm{t}, \lambda) = \sum_{p=1}^\infty t_p \lambda^p\; , 
+\end{equation}
+where \(\lambda\) is a complex parameter. Therefore
 \begin{equation}
@@
     = \exp\left( - \sum_{j=1}^n \ln( 1 -  z_j \lambda ) \right) \\
-    & =  \prod_{j=1}^n \frac{1}{1 -  z_j \lambda} 
-  \end{split}
-\end{equation}
-where \(\lambda\) is a complex parameter. 
-and we see that these functions have simple poles at \( \lambda = z_j^{-1}\).
-
+    & =  \prod_{j=1}^n \frac{1}{1 -  z_j \lambda} \; .
+  \end{split}
+\end{equation}
+It is easy to see that these functions have simple poles at \( \lambda
+= z_j^{-1}\).
+
+Let us now establish an important result,
+see ~\cite{Araujo:2021ghu} and references therein. 
 \begin{proposition}
-The tau function~(\ref{eq:tau-function}) admits an integral
-representation, see ~\cite{Araujo:2021ghu} and references therein,
-of the form
+The tau function~(\ref{eq:slav-tau-function}) admits the following integral
+representation 
 \begin{subequations}
@@
 \end{subequations}
-
+\end{proposition}
+
+\paragraph{\textbf{\emph{Proof}}}
 In terms of the \(z\)-coordinates, the tau functions becomes
@@
 \end{equation}
-Now, it is easy to see that \(w =0\) is not a pole.
-
-All in all, the integration curve \(\gamma_k\) encloses all poles
-\(\{z_j\}_{j=1}^n\).  One of the advantages of this representation is
-that now it makes sense to consider the limit of the infinite chain,
-\(n\to \infty\).
-\end{proposition}
-
-\paragraph{\emph{Proof}}
-There are some minor differences between our calculations and the
-original references; namely, the integration contour \(\gamma_k\) and
-sign conventions. For this reason, we want to show
-explicitly this result.
+Now, it is easy to see that \(w =0\) is not a pole.  All in all, the
+integration curve \(\gamma_k\) encloses points \(\{z_j\}_{j=1}^n\).
 
@@
 Putting all these facts together, we finally see that 
-\(\bm{\tau}(\bm{z}, \bm{v}) = \det\bm{\mathcal{K}}\). \qed
+\(\bm{\tau}(\bm{z}, \bm{v}) = \det\bm{\mathcal{K}}\), that
+is preciselly the expression~(\ref{eq:slav-tau-function}).\\
+\qed
+
+One of the advantages of this representation is
+that now it is easier to consider the limit of the infinite chain,
+\(n\to \infty\).
 
@@
 
-The Baker-Akhiezer funcion is defined in terms of the Japanese formula~\cite{Zabrodin2018}
+The Baker-Akhiezer (BA) funcion is defined in terms of the Japanese formula~\cite{Zabrodin2018}
 \begin{equation}
@@
 
+\subsubsection{BA in \(z\)-coordinates}
 Using the expression~(\ref{eq:tau-function-miwa}), we can write the
 Baker-Akhiezer function in terms of the \(z\)-coordinates.
-Moreover, 
+Let us first write
 \begin{equation}
@@
 \end{equation}
-and we can write
+therefore
 \begin{equation}
@@
 \end{equation}
-From these expressions, it is easy to see that for \(j=n\), then \(w =
-0\) is a pole and we must pick this term in the integration curve
-\(\gamma_k\).
-
-Let us define the components
+From these expressions, it is easy to see that for \(j=n\) the point
+\(w = 0\) is a pole; and we must consider it in the integration curve \(\gamma_k\).
+
+It is convenient to define the components
 \begin{equation}
@@
 \end{equation}
-where \(\tilde{\gamma}_k\) is a contour that does not pick
+where \(\tilde{\gamma}_k\) is a deformation contour that does not pick
 the point \(w=0\); and
@@
 \; , \qquad 
- F_k(\lambda) = (-1)^n \frac{\widehat{\mathcal{Y}}_k(\lambda; 0)}{v_k }  \prod_{s=1}^n z_s^{-1} \; .
+ F_k(\lambda) = (-1)^{n+1} \frac{\widehat{\mathcal{Y}}_k(0; \lambda)}{v_k }  \prod_{s=1}^n z_s^{-1} \; .
 \end{equation}
@@
   \prod_{l=1}^n \left( 1 - \frac{1}{\lambda z_l} \right) = 1 + 
-  \sum_{p=1}^n (-1)^p \lambda^{-p} \sigma_p^{(n)}(\bm{z}^{-1})\; .
+  \sum_{p=1}^n (-1)^p \lambda^{-p} \sigma_p^{(n)}(\bm{z}^{-1})\; , 
 \end{equation}
@@
 We now want to consider the above calculations in the Miwa
-coordinates. This allows us to consider the infinite chain limit.
+coordinates.
 

### 2025-05-07 draft.tex
finish last section of the paper

@@
 \end{equation}
+Next section we find a better expression for the Baker-Akhiezer
+function.
 
@@
   \det \left( \mathbb{1} + 
-    \frac{1}{\lambda} \mathcal{T}
+    \frac{1}{\lambda} \mathcal{M}
+  \right)\; , 
+\end{equation}
+where \(\mathcal{M} = \mathcal{K}^{-1} \check{\mathcal{K}}\) is a
+finite dimensional matrix. Let us now use the elementary expression
+\begin{subequations}
+\begin{equation}
+  \begin{split}
+    \det \left( \mathbb{1} + \frac{1}{\lambda} \mathcal{M}\right)
+    & = \exp \left[ \Tr \log \left( \mathbb{1} + \frac{1}{\lambda} \mathcal{M} \right) \right]\\
+    & = \prod_{l=1}^n \left( 1 + \frac{\mu_l}{\lambda} \right) \; ,
+  \end{split}
+\end{equation}
+\end{subequations}
+where \(\bm{\mu} = \{\mu_l\}_{l=1}^n\) are the eigenvalues of the
+matrix \(\mathcal{M}\), and these obviously depend on the Bethe roots
+\(\bm{v}\) and parameters \(\bm{t}\). Therefore, we have
+\begin{equation}
+  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
+  \left(1 + \sum_{k=1}^n \frac{\xi_k(\bm{t})}{\lambda^k} 
   \right)\; . 
 \end{equation}
-where \(\mathcal{T} = \mathcal{K}^{-1} \check{\mathcal{K}}\).
-
-\subsection{Problems}
-Here are some important comments and problems to discuss.
+where \(\xi_k(\bm{t}) = \sigma_k^{(n)}(\mu_1, \dots, \mu_n)\) and \(\mu_j = \mu_j(\bm{t}, \bm{v})\).
+
+We can also write 
+\begin{equation}
+  \begin{split}
+    \det \left( \mathbb{1} + \frac{1}{\lambda} \mathcal{M}\right)
+    & = \prod_{l=1}^n \left( 1 + \frac{\mu_l}{\lambda} \right) \\ 
+  \end{split}
+\end{equation}
+
+In the limit \(n \to \infty\) with with \(n/L \to 0\), we have
+that the Baker-Akhiezer function can be written as
+\begin{equation}
+  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
+  \left( 1 + \sum_{k=1}^n \frac{(-1)^k}{\lambda^k} \sigma_k(\{\bm{p}\})
+  \right)\; . 
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Discussion}
 

### 2025-05-08 draft.tex
finish calculations, start conclusions

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Tau functions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Homogeneous limit}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Examples} Let us now consider the cases \(n=2, 3\) (the case \(n=1\) is trivial)
+\section{Examples}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Let us now consider the cases \(n=2, 3\) (the case \(n=1\) is trivial)
 to gain some understanding of the problem.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Baker-Akhiezer function}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Baker-Akhiezer function}
+\subsection{Baker-Akhiezer  in \(z\)-coordinates}
 
@@
 
-\subsubsection{BA in \(z\)-coordinates}
 Using the expression~(\ref{eq:tau-function-miwa}), we can write the
@@
 Next section we find a better expression for the Baker-Akhiezer
-function.
+function, but from this expression we can see that all the poles
+are at the point \(\lambda =0\).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fredholm determinant}
+\subsection{Baker-Akhiezer in \(t\)-coordinates}
 
@@
 \begin{equation}
+\label{eq:ba-fredholm}
   \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
@@
     \det \left( \mathbb{1} + \frac{1}{\lambda} \mathcal{M}\right)
-    & = \prod_{l=1}^n \left( 1 + \frac{\mu_l}{\lambda} \right) \\ 
-  \end{split}
-\end{equation}
-
-In the limit \(n \to \infty\) with with \(n/L \to 0\), we have
-that the Baker-Akhiezer function can be written as
-\begin{equation}
-  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
-  \left( 1 + \sum_{k=1}^n \frac{(-1)^k}{\lambda^k} \sigma_k(\{\bm{p}\})
-  \right)\; . 
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Discussion}
-
-It seems that we can consider a basis of functions \(\mathcal{Y}_j(z)\) for the Baker-Akhiezer
-functions. I think that this object might say something interesting. In particular, we can
-explicitly build solutions of the KP equation. In fact, the functions \(\mathcal{Y}_j\)
-above have poles at the Bethe roots, it is interesting. 
-\begin{itemize}
-\item[\faCheck] What is the pole and root structure of the tau and Baker-Akhiezer (BA) functions?
-  In particular, what happens at the Bethe roots?
-\item[\faCheck] Basis tau functions
-\item[\faCheck] Write the cases n=2 and n=3
-\item[\faCheck] What the general case for all \(z_k\) approaching to a single
-  value \(w\). 
-\item[\faCheck] Write these tau functions in terms of Miwa coordinates
-\item[\faCheck] I need to calculate the Baker-Akhiezer function for this model using the Japanese formula
-  in terms of tau functions.
-\item[\faCheck]  Write some explicit expressions for \(N=2\) and \(N=3\). 
-\item Discuss the Toda hierarchy case. 
-\item See the Limit \(L \to \infty\) and \(N \to \infty\) but sufficiently slower than \(L\). 
-  I think that the matrix \(\mathcal{T}\) is a trace class operator and we write the BA function
-  as a Fredholm determinant. 
-\item Better investigate these functions in Miwa coordinates. See Fredholm determinant. 
-  I think that this BA function will be similar to the soliton-like solution discussed in section 3.6.2 (page 41) of~\cite{Zabrodin2018}. 
-  My functions seem to have a pole of order \(N\) at infinity. And \(N\) zeros at the Bethe roots. 
-\item It turns out that the Baker-Akhiezer function is the appropriate object to discuss
-  the Bethe roots. 
-  \item I think that these tau functions come from algebro geometric tau functions. 
-  \item I can try to study the dynamics closer to the Bethe roots, I think that the
-    \(\Omega\)'s will have some interesting expansions, some of them might vanish. 
-  \item This might become a Riemann Hilbert problem
-  \item Are these tau functions associated to the Calogero-Moser model??
-  \item Elliptic case - see slavnov, zabrodin's paper
-\end{itemize}
+    & = \exp\left[ \sum_{l=1}^n \ln \left( 1 + \frac{\mu_l}{\lambda} \right)\right]
+    = \exp\left[ \sum_{l=1}^n \sum_{k=1}^\infty \frac{(-1)^{k-1}}{k} \left(\frac{\mu_l}{\lambda} \right)^k\right] \\ 
+    & = \exp\left[ \sum_{k=1}^\infty \frac{(-1)^{k-1}}{\lambda^k} \gamma_k\right] \; ,
+  \end{split}
+\end{equation}
+where we define the Miwa coordinates \(\gamma_k = \frac{1}{k}\sum_{l=1}^n \mu_l^k \). Consequently
+\begin{equation}
+    \det \left( \mathbb{1} + \frac{1}{\lambda} \mathcal{M}\right)
+     = 1 + \sum_{k\geq 1}\frac{1}{\lambda^k} \sigma_k(\bm{\gamma})\; .
+\end{equation}
+Putting all these facts together, we can write the functions
+\(\xi_k(\bm{t})\) in terms of \(\bm{\gamma}\).  Observe that now the
+parameter \(n\) is hidden in the definition of the coordinates
+\(\gamma_k\).  One advantgage of this expression is that now we seem
+ot have a better setting to consider the thermodynamic limit \(n \to
+\infty\) with with \(n/L \to 0\). In fact, the
+expression~(\ref{eq:ba-fredholm}) suggests that in this limit, the
+Baker-Akhiezer function in the thermodynamics limit can be written as
+a Fredholm determinant. We are currently exploring this question and
+hope to report new results soon.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In this paper we have discussed some properties of the Slavnov
+products and their relation with the tau functions of the KP
+hierarchy.
+
+An important initial observation is that the general form of this tau
+function is written in terms of some alternant matrix, and this form
+is known since (cite papers on the matrix models and so on). But the
+functions associated to the current paper is drastically different
+from those papers, and do not expand a point in the
+Grassmannian. Therefore, it is necessary to better understand some of
+these properties. In this paper we start exploring these results.
+
+....
+
+We have also started our exploration of the Baker-Akhiezer function since it seems to
+be the relevant object of our investigation.
+
+Soem future interesting directions. We might want to calculate the
+solutions of the KP equation to see what they really mean. Perhaps
+consider analitic and numerical calculations, since the calculation of
+the determinants become complicated even for small values of \(n\).
+
+More interestingly, one may try to consider the thermodynamic limit of
+the Slavnov product and explore what it means from the viewpoint of
+the Baker-Akhiezer function.  See the Limit \(L \to \infty\) and \(N
+\to \infty\) but sufficiently slower than \(L\).  I think that the
+matrix \(\mathcal{M}\) is a trace class operator and we write the BA
+function as a Fredholm determinant.
+
+I think that this BA function will be similar to the soliton-like
+solution discussed in section 3.6.2 (page 41) of~\cite{Zabrodin2018}.
+My functions seem to have a pole of order \(N\) at infinity. And \(N\)
+zeros at the Bethe roots.
+
+Finally, we can explore the elliptic case and see if one can see if
+there exists any similar relation on the elliptic case.  Elliptic case
+- see slavnov, zabrodin's paper
 

### 2025-05-12 draft.tex
fix small mistakes
write abstract, intro and improve section 2

@@
 
-\title{Slavnov products and KP tau functions}
+\title[Slavnov products, KP and BA functions]{
+  More on the Slavnov products of spin chains,
+  KP hierarchy tau and Baker-Akhiezer functions 
+}
 
@@
 \address{\noindent 
-Instituto de Ciências Exatas, Departamento de Física\\
-Universidade Federal Fluminense\\
+Institute of Exact Sciences, Department of Physics\\
+Fluminense Federal University\\
 Rua Des. Ellis Hermydio Figueira, 783, Aterrado\\
@@
 \begin{abstract}
-One important ingredient in the Algebraic Bethe Ansatz is the scalar
-product of Bethe states.  There are many important results on this
-topic and references therein, but here we turn our attention to the
-well known fact that scalars products in the algebraic Bethe ansatz
-can be written as determinants.  More specifically, we will
-investigate a particular type of correlation functions in quantum
-integrable spin chains, the so called \emph{Slavnov product} These
-objects can be seen as building blocks of more sofisticated
-correlation functions and are instrumental in the study of norms of
-Bethe wave functions But more importantly for our present discussion,
-Slavnov products seem to be a bridge connecting quantum and classical
-integrable system.
+Connections between classical and quantum integrable systems are
+analyzed from the viewpoint of the Slavnov products of Bethe
+states. It is well known that, modulo model-dependent aspects, the
+functional structure of the Slavnov products takes the form of
+determinants. Using new results on the general structure of rational
+and trigonometric models, we establish that, as long as the model
+satisfies certain conditions, its Slavnov product is a tau function of
+the KP hierarchy, thus generalizing some known results. We also show
+that the Slavnov products can be expanded in terms of other tau
+functions, and we prove that their homogeneous limit can be calculated
+as a Wronskian of functions related to the eigenvalues of the transfer
+matrices. Finally, we calculate the Baker–Akhiezer functions
+associated with these Slavnov products, and show that, modulo a
+multiplicative universal term, the Baker–Akhiezer functions have a
+closed determinantal formula.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 One important ingredient in the Algebraic Bethe Ansatz is the scalar
-product of Bethe states.  There are many important results on this
-topic, see~\cite{Korepin:1993kvr} and references therein, but here we
-turn our attention to the well known fact that scalars products in
-the algebraic Bethe ansatz can be written as determinants.
-
-More specifically, we will investigate a particular type of
-correlation functions in quantum integrable spin chains, the so called
-\emph{Slavnov product}~\cite{Slavnov1989}. These objects can be seen as building blocks
-of more sofisticated correlation functions and are instrumental in the
-study of norms of Bethe wave functions~\cite{Korepin:1993kvr}.  But
-more importantly for our present discussion, Slavnov products seem to
-be a bridge connecting quantum and classical integrable system.
-
-The study of connections between classical and quantum integrable
-systems is an old subject, and has been addressed from a wide range of
-perspectives~\cite{Wu:1975mw, Its:1992bj, korepin2000the, Foda2009,
+product of Bethe states. This object plays a central role in the
+analysis of quantum integrable systems. Many important results have
+been collected on this topic, see~\cite{Korepin:1993kvr} and
+references therein. In this text, we focus on a powerful and elegant
+aspect of these products: scalars products in the algebraic Bethe
+ansatz can be expressed in terms of determinants.
+
+More specifically, we investigate a very special type of correlation
+function in quantum integrable spin chains, the so called
+\emph{Slavnov product}~\cite{Slavnov1989}. These objects can be seen
+as building blocks of more sophisticated correlation functions and are
+instrumental in the study of norms of Bethe wave
+functions~\cite{Korepin:1993kvr}. But more importantly for the
+purposes of the present work, Slavnov products seem to be a bridge
+connecting quantum and classical integrable system. This is the
+problem we explore in this work.
+
+Connections between classical and quantum integrable systems are a
+long-standing research area, and have been addressed from a wide range
+of perspectives~\cite{Wu:1975mw, Its:1992bj, korepin2000the, Foda2009,
   Alexandrov:2011aa}.  In~\cite{Foda:2009zz}, the authors started the
 analysis of the connections between the Slavnov products of the
-Heisenberg XXZ spin chain, and the Kadomtsev–Petviashvili (KP)
-classical integrable hierarchy. This analysis has been extended to
-some directions and applications, for example~\cite{Wheeler:2010vmq,
-  Foda:2010, Takasaki:2010qm, Foda:2012wn, Foda:2012wf}.
-In~\cite{Araujo:2021ghu, Araujo:2024klz}, the author of the current
-paper also investigated some developments of this research field. In
-particular, the relation between integrable hierarchies and quantum
-integrable systems such as the Q-Boson integrable system and in the
-Temperley-Lieb open spin chains.
-
-Although the specific details of he Slavnov product are radically
-different, In all these cases discussed in the previous paragraph, the
-general functional structure of the Slavnov products of different
-models are basically the same. More specifically, module some
-multiplicative terms, all these expressions are determinant, and it is
-the fact that allows us to manipulate these objects to show that thesy
-are KP and Toda tau functions.
-
-Belliard and Slavnov~\cite{Belliard:2019bfz} have addressed precisely
-this property: \emph{Why scalar products in the algebraic Bethe ansatz
-have determinant representations}.  Using their results, we now want
-to understand \emph{why and how (some) scalar products in the
-algebraic Bethe ansatz are KP and Toda tau functions}. In the current
-show that as long as the integrable system satisfies the conditions
-established in~\cite{Belliard:2019bfz} -- and some additional
-restrictions -- the Slavnov product is guaranteed to satisfy the KP
-integrable hiearchy. Moreover, we also discuss some immediate
-consequences of this result.
-
-In section 2 we review the main aspects of the
-work~\cite{Belliard:2019bfz} and fix the main notation we use in the
-remainder of this work. (...)
-
+Heisenberg XXZ spin chain and the Kadomtsev–Petviashvili (KP)
+classical integrable hierarchy. Their analysis has been extended in
+several different directions and applications, for
+example~\cite{Wheeler:2010vmq, Foda:2010, Takasaki:2010qm,
+  Foda:2012wn, Foda:2012wf}.  In~\cite{Araujo:2021ghu,
+  Araujo:2024klz}. The author of the current paper also investigated
+some aspects of this research problem. In particular, the relation
+between integrable hierarchies and quantum integrable systems such as
+the Q-Boson integrable system and the Temperley-Lieb open spin chains.
+
+The main ingredients for the Slavnov product are the Bethe
+wavefunctions themselves. As such, the specific details of these
+objects depend on the model, symmetries and their representations, and
+on the boundary conditions. Nevertheless, the general
+\textbf{functional structure} of Slavnov products across radically
+different models is basically the same. More specifically, modulo some
+multiplicative factors, all these expressions take the form of
+determinants, and it is this basic property that allows us to
+manipulate these objects and prove that they are KP and/or Toda tau
+functions.
+
+Belliard and Slavnov~\cite{Belliard:2019bfz} have thoroughly
+investigated this property for spin chains with rational and
+trigonometric \(R\)-matrices, and basically answered ``\emph{why
+scalar products in the Algebraic Bethe Ansatz have determinant
+representations}''. Using their results, we now want to understand
+``\emph{why and how (some) scalar products in the Algebraic Bethe
+Ansatz are KP and Toda tau functions}''. We prove that, as long as the
+integrable system satisfies the conditions established
+in~\cite{Belliard:2019bfz} -- along with some additional restrictions
+-- the Slavnov product is guaranteed to satisfy the KP integrable
+hierarchy. Additionally, we discuss some immediate consequences of
+this result.
+
+In Section 2, we review the main aspects of the
+work~\cite{Belliard:2019bfz}. This section also fixes some of the
+notation we use in the remainder of this work and in future
+investigations. Section 3 presents two new results. First, we rewrite
+relevant formulas established in~\cite{Belliard:2019bfz} and prove
+that these Slavnov products are KP tau functions expressed in terms of
+alternant determinants. We also discuss some contrasts between this
+formula and certain results that have previously appeared in matrix
+theory investigations.
+
+These tau functions are written in terms of two sets of
+parameters. The first set is given by arbitrary complex numbers, and
+the second set is given by the Bethe roots of the spin chain.  In
+Section 3, we also find a basis for the Slavnov products, and this
+basis is itself formed by tau functions. The results of Section 3
+allow us to investigate the case where the complex parameters are
+close to the Bethe roots.
+
+Section 4 discusses the homogeneous limit of the Slavnov product.  In
+this case, all complex parameters condense to a single value, and we
+show that Slavnov products have a Wronskian expression written in
+terms of functions related to the eigenvalues of the transfer matrix.
+Section 5 presents some explicit examples for small spin chains, and
+we see that even in those cases the expressions for the tau functions
+become overwhelming very quickly.
+
+Finally, in Section 6, we use the Japanese formula to investigate the
+Baker–Akhiezer function associated with these tau functions. Using
+known integral formulas for the tau functions, we write them in terms
+of Miwa coordinates. The most important result in this section is the
+explicit expressions for the Baker–Akhiezer functions. We discuss some
+interesting consequences and open problems in Section 7.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In order to make the paper as self-contained as possible, this section
-reviews the main arguments in~\cite{Belliard:2019bfz}. Let us start
-with a set of arbitrary complex numbers \(\bm{u} =
-\{u_j\}_{j=1}^{n+1}\), and we set \(n+1\) sets
-\(\bm{u}_j=\bm{u}\setminus \{u_j\}\). In the algebraic Bethe ansatz
-setting~\cite{Korepin:1993kvr}, we can now define \(n+1\) off-shell
-Bethe vectors \(\ket{\Psi(\bm{u}_j)}\), i.e. Bethe states where the
-algebraic Bethe equations are not imposed on
-\(\bm{u}_j\). Additionally, we also consider a set of Bethe roots
-\(\bm{v} = \{ v_k \}_{k=1}^n\), and the on-shell Bethe vectors
-\(\ket{\Psi(\bm{v})}\).
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To ensure the paper is as self-contained as possible, this section
+reviews the main arguments of the work of Belliard and
+Slavnov~\cite{Belliard:2019bfz}. Let us start with a set of arbitrary
+complex parameters \(\bm{u} = \{u_j\}_{j=1}^{n+1}\), and define
+\(n+1\) sets \(\bm{u}_j=\bm{u}\setminus \{u_j\}\). In the Algebraic
+Bethe Ansatz context~\cite{Korepin:1993kvr, Slavnov:2019aba}, we can
+now define \(n+1\) off-shell Bethe vectors \(\ket{\Psi(\bm{u}_j)}\),
+i.e., Bethe states where the algebraic Bethe equations are not imposed
+on the parameters \(\bm{u}_j\). Additionally, we must also consider a
+set of Bethe roots \(\bm{v} = \{ v_k \}_{k=1}^n\), that is, parameters
+\(\bm{v}\) that satisfy the algebraic Bethe equations. Finally, we
+define the on-shell Bethe vectors \(\ket{\Psi(\bm{v})}\).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Determinant representation}
 The action of the transfer matrix \(\mathcal{T}(z)\), that is an
-Hermitian operator, on the dual Bethe vector is given by
+Hermitian operator, on the dual on-shell Bethe vector is given by
 \begin{equation}
@@
 \end{equation}
-where \(\Lambda(z; \bm{v}) \) is the eigenvalue of the transfer matrix.
-
-We now introduce \(n+1\) scalar products between the on-shell and
-off-shell Bethe states
-\begin{equation}
-  \bm{\zeta}_j(\bm{u}_j, \bm{v}) \equiv  \bm{\zeta}_j
-  = \bracket{\Psi(\bm{v})}{\Psi(\bm{u}_j)}\qquad j =1, \dots, n+1\; .
+where \(\Lambda(z; \bm{v}) \) is the transfer matrix eigenvalue.
+
+We construct \(n+1\) functions obtained from products between the
+on-shell and each off-shell Bethe states
+\begin{equation}
+  \bm{\zeta}_j(\bm{u}_j, \bm{v}) 
+  = \bracket{\Psi(\bm{v})}{\Psi(\bm{u}_j)}\; ,\qquad j =1, \dots, n+1\; .
 \end{equation}
 These partially on-shell scalar products are called \emph{Slavnov
-products}.
-
-Before procceding, let us also establish the class of models we are
-dealing with.  Let us consider a class of integrable models where the
-action of the transfer matrix on a generic off-shell bethe states can
-be expanded as
+products}.  Henceforth, the functional dependence of these functions
+will be omitted, that is \(\bm{\zeta}_j\equiv \bm{\zeta}_j(\bm{u}_j,
+\bm{v})\).
+
+In this work we only consider integrable models where the action of
+the transfer matrix on a generic off-shell bethe states can be
+expanded as
 \begin{subequations}
@@
 \end{equation}
-where \(L_{jk}\) are numerical coefficients. Observe that the terms
-\(L_{jk}\) with \(j\neq k\) contain the unwanted terms.; and these
-non-diagonal terms must vanish when the Bethe equations are
-satisfied. Therefore, since the diagonal coefficient survives, that is
-\(L_{jj}\), we conclude that these terms must be equal to the
-eigenvalue of the tranfer matrix, that is
+where \(L_{jk}\) are coefficients, and the off-diagonal elements
+\(L_{jk}\) with \(j\neq k\) contain the unwanted
+terms~\cite{Slavnov:2019aba}. From the Algebraic Bethe Ansatz
+construction, the non-diagonal terms must vanish when the Bethe
+equations are satisfied, and this is basically the definition of the
+algebraic bethe equations. Consequently, only the diagonal
+coefficients \(L_{jj}\) survive, and we conclude that these terms must
+be equal to the eigenvalue of the tranfer matrix.  Therefore
 \begin{equation}
@@
 \end{subequations}
-This class of models include a wide range of known integrable systems,
-including the ones discussed in the introduction. One important class
-of models that does not fall in this classification are with elliptic
-R-matrices, although some of these models have slavnov products with
-determinantal representations.
+
+This class of models includes many of the most familiar spin chains
+with rational and trigonometric \(R\)-matrices -- including those
+models discussed in the introduction. One important class of models
+that does not fall into this classification is defined by
+elliptic \(R\)-matrices, although some of these models still have slavnov
+products with determinantal representations.
 
@@
 The Slavnov products \(\bm{\zeta}_j\) satisfy a system of linear
-equations.
+equations~\cite{Slavnov:2019aba}.
 \end{proposition}
-
-\paragraph{\textbf{\emph{Proof}}} Let us first use that
+\paragraph{\textbf{\emph{Proof}}} Let us first use that the
+transfer matrix can act on the on-shell bra \(\bra{\Psi(\bm{v})}\)
+on on the off-shell ket \(\ket{\Psi(\bm{u}_j)}\), then  
 \begin{equation}
@@
 
-Puttting all these facts together, we get
+Puttting all these facts together, we can write the
+expression~(\ref{eq:scalar-prod}) as
 \begin{equation}
@@
 \end{equation}
-where
+where we have defined the coefficients
 \begin{equation}
@@
 \end{equation}
-And this expression shows that the Slavnov products satisfy a linear system.
-We can write this system in a matrix form as 
+In simple terms, this expression shows that the Slavnov products
+satisfy a linear system.  We can write this system in a matrix form as
 \begin{equation}
@@
 \end{equation}
-with \(\Lambda_j \equiv \Lambda(u_j; \bm{v})\), and also
+with \(\Lambda_j \equiv \Lambda(u_j; \bm{v})\), and
 \begin{equation}
@@
 \end{subequations}
+This completes the proof of their proposition. 
  \qed
@@
 
-Soem future interesting directions. We might want to calculate the
+Some future interesting directions. We might want to calculate the
 solutions of the KP equation to see what they really mean. Perhaps

### 2025-05-13 draft.tex
improve section 2 of the draft

@@
 There are two important consequences for us now. First of all, if we
-assume that this system has a non-trivial solution, it will be written
-as minors of the matrix \(\bm{M}\).
+assume that this system has a nontrivial solution, it will be
+expressed in terms of minors of the matrix \(\bm{M}\).
 
 Moreover, since the system is homogeneous, the solutions are
-determined up to multiplicative terms, that we can fix them by
-requiring that the final result gives the required tau function. In
-the original works of Foda and collaborators, e.g.~\cite{Foda:2009zz,
+determined up to multiplicative factors, which we can fix by
+requiring that the final result yields a KP tau function. In the
+original works of Foda and collaborators, e.g.,~\cite{Foda:2009zz,
   Wheeler:2010vmq}, the authors perform a series of redefinitions to
-reach the same goal.
-
-Evidently being a determinant is not enough to guarantee that the
-Slavnov product is a tau function.  In order to accomplish this
+achieve the same goal.
+
+Evidently, being a determinant is not enough to guarantee that the
+Slavnov product is a tau function.  In order to establish this
 result, we need to specify the models. Following the original
-work~\cite{Belliard:2019bfz}, we will only discuss the rational models
+work~\cite{Belliard:2019bfz}, we will restrict the current analysis to rational models
 -- we will see that the calculations are overwhelming even in this
-simple case. The generalization for open boundary conditions and for
-trigonometric models is immediate, see~\cite{Slavnov:2019aba} for more
-details on the generalization.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+simple case. The generalization to open boundary conditions and for
+trigonometric models is straightforward, see~\cite{Slavnov:2019aba} for more
+details.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Rational models}
 
-Let us startwith an R-matrix of the form
+Let us start with an R-matrix of the form
 \begin{equation}
@@
 \end{equation}
-where \(c\) is a constant, the identity operator is denoted by
-\(\mathbb{1}\) and \(\mathcal{P}\) is the permutation operator.
-
-In the models with rational R-matrix, the eigenvalues of the transfer matrix
-have the form 
+where \(c\) is a constant, \(\mathbb{1}\) is the identity and
+\(\mathcal{P}\) is the permutation operator~\cite{Slavnov:2019aba}.
+The eigenvalues of the transfer matrix have the form
 \begin{equation}
@@
 where the function \(\mathcal{Y}(z; \bm{v})\) is symmetric over the
-Bethe roots \(\bm{v}\), and linearly depends on every
+Bethe roots \(\bm{v}\), and has a linear dependence on each Bethe root
 \(v_j\).
 
-Generically, it is written as
+Generically, we write the \(\mathcal{Y}\)-functions as 
 \begin{equation}
@@
 where \(\sigma_p^{(n)}(\bm{v})\) are elementary symmetric polynomials
-in \(\bm{v}\) and where \(\alpha_p(z)\) are free functional
-parameters. In fact, in the XXX discussed in~\cite{Belliard:2019bfz},
-these functions all \(\alpha_p(z)\) are polynomials of degree \(2n\).
-The important point for us is that the functions \(\alpha_p(z)\) are
-not singular when we consider the limit \(z \to v_j \in \bm{v}\), and
-that also means that \(\mathcal{Y}(z; \bm{v})\) is also regular in
-this limit.
-
-Let us also define the following product 
-\begin{equation}
-  g(z, \bm{v}) = \prod_{v_i\in \bm{v}} g(z; v_i)\; , 
-\end{equation}
-and that means that each Bethe root \( v_i \in \bm{v}\) 
-is a pole of \(g(z;\bm{v})\). Therefore, if \(\Gamma\) is a contour
+in \(\bm{v}\), and \(\alpha_p(z)\) are free functional parameters.
+The most important point for us is that the functions \(\alpha_p(z)\), 
+and consequently the \(\mathcal{Y}\)-function, are regular in the limit
+\(z \to v_j \in \bm{v}\). The XXX spin chain has been discussed
+in~\cite{Belliard:2019bfz}, and the authors show that \(\alpha_p(z)\)
+are polynomials of degree \(2n\).
+
+Let us also define the product 
+\begin{equation}
+  g(z, \bm{v}) = \prod_{v_i\in \bm{v}} g(z; v_i)\; . 
+\end{equation}
+Now, it is easy to see that each Bethe root \( v_i \in \bm{v}\) is a
+pole of \(g(z;\bm{v})\). Therefore, if \(\Gamma\) is a contour
 containing all the Bethe roots \(\{v_j\}_{j=1}^n\), we have
 \begin{equation}
-  \frac{1}{2 \pi i}\oint_{\Gamma} \mathrm{d}z g(z; \bm{v}) = \sum_{j=1}^n  \prod_{v_i \in \bm{v}\setminus \{u_j\}} g(z, v_i)\; .
-\end{equation}
-Furthermore, the coefficients \(L_{jk}\) are given by
-\begin{equation}
-  L_{jk} = g(u_k, \bm{u}_k) \mathcal{Y}(u_k; \bm{u}_j)
+  \frac{1}{2 \pi i}\oint_{\Gamma} \mathrm{d}z g(z; \bm{v}) = \sum_{j=1}^n
+  \prod_{v_i \in \bm{v}\setminus \{v_j\}} g(z, v_i)\; .
+\end{equation}
+Putting all these facts together, the coefficients \(L_{jk}\) are given by
+\begin{equation}
+  L_{jk} = g(u_k, \bm{u}_k) \mathcal{Y}(u_k; \bm{u}_j)\; ,
 \end{equation}
@@
 
-It has also been shown~\cite{Belliard:2019bfz} that if \(\det
-(\bm{M}) = 0 \) and \(\mathrm{rank}(\bm{M}) = n\), then, the Slavnov
-products are given by
-\begin{equation}
- \bm{\zeta}_\ell = \phi(\bm{v}) \tilde{\Delta}(\bm{u}_\ell)\hat{\Omega}_\ell\; ,
-\end{equation}
-where \(\phi(\bm{v})\) is a function of the Bethe roots and
-\begin{equation}
-  \tilde{\Delta}(\bm{u}_\ell) = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{c}{u_j - u_k}\quad \Rightarrow \quad
-\frac{\tilde{\Delta}(\bm{u}_\ell)}{c_0} = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{1}{u_j - u_k}\; , 
-\end{equation}
-where we have absorbed the product of \(c\) into a new constant \(c_0\). 
-All in all, \(\tilde{\Delta}(\bm{u}_\ell)/c_0\) is the inverse of the Vandermonde determinant
-\(\Delta(\bm{u}_\ell) = \prod_{j>k}(u_j - u_k)\).
+It has also been shown~\cite{Belliard:2019bfz} that if \(\det (\bm{M})
+= 0 \) and \(\mathrm{rank}(\bm{M}) = n\), the Slavnov products are
+given by
+\begin{equation}
+ \bm{\zeta}_\ell = \phi(\bm{v}) \tilde{\Delta}(\bm{u}_\ell)\hat{\Omega}_\ell\; . 
+\end{equation}
+Let us now explain the different terms in this expression. 
+First of all, \(\phi(\bm{v})\) is a function of the Bethe roots and
+\begin{equation}
+  \tilde{\Delta}(\bm{u}_\ell) = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{c}{u_j - u_k}\; .
+\end{equation}
+We can absorbed the product of \(c\) into a new constant
+\(c_0\), and it is easy to see that \(\tilde{\Delta}(\bm{u}_\ell)/c_0\) is the
+inverse of the Vandermonde determinant \(\Delta(\bm{u}_\ell) =
+\prod_{j>k}(u_j - u_k)\).
 

### 2025-05-13 draft.tex
finish section 2

@@
 
-It has also been shown~\cite{Belliard:2019bfz} that if \(\det (\bm{M})
-= 0 \) and \(\mathrm{rank}(\bm{M}) = n\), the Slavnov products are
+It has also been shown~\cite{Belliard:2019bfz} that for \(\det(\bm{M})
+= 0\) and \(\mathrm{rank}(\bm{M}) = n\), the Slavnov products are
 given by
 \begin{equation}
- \bm{\zeta}_\ell = \phi(\bm{v}) \tilde{\Delta}(\bm{u}_\ell)\hat{\Omega}_\ell\; . 
-\end{equation}
-Let us now explain the different terms in this expression. 
-First of all, \(\phi(\bm{v})\) is a function of the Bethe roots and
+ \bm{\zeta}_\ell = \phi(\bm{v}) \tilde{\Delta}(\bm{u}_\ell)\hat{\Omega}_\ell\; , \qquad \ell = 1, \dots, n+1\; .
+\end{equation}
+Let us now explain the different terms in this expression.  First of
+all, \(\phi(\bm{v})\) is a function of the Bethe roots and its
+particular form is not important in out analysis. Moreover, we have
 \begin{equation}
@@
 \end{equation}
-We can absorbed the product of \(c\) into a new constant
+We can also absorb the product of \(c\) into a new constant
 \(c_0\), and it is easy to see that \(\tilde{\Delta}(\bm{u}_\ell)/c_0\) is the
@@
 
-Additionally, the matrices \(\hat{\Omega}_\ell\) are minors of
-\(\bm{\Omega}\) with the \(\ell\)-th column excluded, in other words,
-\begin{equation}
- \hat{\Omega}_\ell = \det_{k\neq \ell} \Omega_{jk}\; ,
-\end{equation}
-where
+We now define the matrix \(\bm{\Omega}\) by specifying its components
 \begin{equation}
@@
 \end{equation}
-
-All in all, we have an expression of the form
+The matrices \(\hat{\Omega}_\ell\) are minors of
+\(\bm{\Omega}\) with the \(\ell\)-th column excluded, in other words,
+\begin{equation}
+ \hat{\Omega}_\ell = \det_{k\neq \ell} \Omega_{jk}\; . 
+\end{equation}
+
+All in all, we use these objects to define the \(n+1\) functions below
 \begin{equation}
@@
 \end{equation}
-This is the most important result for us, and our goal now is to show
-that it is a tau-function of the KP-hierarchy.
+This is the most important result for our discussion; and our goal now
+is to show that it is a tau-function of the KP-hierarchy.
 

### 2025-05-15 draft.tex
work on section 3 of the paper

@@
 \begin{equation}
+\label{eq:yfunc-exp}
   \mathcal{Y}(z; \bm{v}) = \sum_{p=0}^n \alpha_p(z) \sigma_p^{(n)}(\bm{v})\; , 
@@
 
-We now define the matrix \(\bm{\Omega}\) by specifying its components
-\begin{equation}
+We now define the \(n\times (n+1)\) matrix \(\bm{\Omega}\) by specifying its components
+\begin{equation}
+  \label{eq:omega-matrix-def}
   \Omega_{jk}(u_k; \bm{v}) = g(u_k, v_j) \mathcal{Y}(u_k; \{u_k, \bm{v}_j\})\; ,
@@
 \end{equation}
-
-All in all, we use these objects to define the \(n+1\) functions below
+All in all, we use these determinants to define \(n+1\)
+\emph{normalized Slavnov products} as follows
 \begin{equation}
   \label{eq:slavnov-tau}
-  \bm{\tau}_\ell(\bm{u}_\ell; \bm{v}) \equiv \frac{1}{c_0}\frac{\bm{\zeta}_\ell}{\phi(\bm{v})}
-  = \frac{\hat{\Omega}_{\ell}}{\Delta(\bm{u}_\ell)} \; .
+  \bm{\tau}^{(\ell)}(\bm{u}_\ell; \bm{v}) \equiv \frac{1}{c_0}\frac{\bm{\zeta}_\ell}{\phi(\bm{v})}
+  = \frac{\hat{\Omega}_{\ell}}{\Delta(\bm{u}_\ell)}\; , \quad \ell = 1, \dots, n+1 \; .
 \end{equation}
 This is the most important result for our discussion; and our goal now
-is to show that it is a tau-function of the KP-hierarchy.
-
+is to show that each \(\bm{\tau}^{(\ell)}(\bm{u}_\ell; \bm{v})\) is a
+tau-function of the KP-hierarchy.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 In order to proceed, let us simplify the notation and organize the
-results we described before. First of all, we need to observe
-that we can define \(n\) functions \(\Omega_j(z)\) of the form
-\begin{equation}
-\begin{split}
-  \Omega_{j}(z; \bm{v}) & = g(z, v_j) \mathcal{Y}(z; \{z, \bm{v}_j\})\qquad j =1, \dots, n\\
-   & = \frac{c}{z - v_j} \mathcal{Y}(z; \{z, \bm{v}_j\})\; .
-\end{split}
-\end{equation}
-Moreover, we have the expansion 
-\begin{equation}
-  \mathcal{Y}(z; \{z,\bm{v}_j\}) = \sum_{p=0}^n \alpha_p(z) \sigma_p^{(n)}(\{z,\bm{v}_j\})\; , 
-\end{equation}
-and using that the elementary symmetric polynomials decompose as
+results described above. First of all, observe that we can define
+\(n\) functions \(\Omega_j(z)\) of the form
+\begin{equation}
+\begin{split}
+  \Omega_{j}(z) \equiv
+  \Omega_{j}(z; \bm{v}) & = g(z, v_j) \mathcal{Y}(z; \{z, \bm{v}_j\})\\
+   & = \frac{c}{z - v_j} \mathcal{Y}(z; \{z, \bm{v}_j\})\; , \qquad j =1, \dots, n \; .
+\end{split}
+\end{equation}
+Let us also denote \(\mathcal{Y}(z; \{z, \bm{v}_j\}) \equiv
+\mathcal{Y}_j(z)\), and note that we have \(n\) functions
+\(\mathcal{Y}_j(z)\) whose defining property is the absence of the
+\(j\)-th Bethe root \(v_j\).  It is also convenient to consider
+\(c=1\), consequently \(c_0=1\).
+
+Moreover, the expansion of the
+\(\mathcal{Y}\)-functions~(\ref{eq:yfunc-exp}) yields
+\begin{equation}
+  \mathcal{Y}(z; \{z,\bm{v}_j\}) = \sum_{p=0}^n \alpha_p(z) \sigma_p^{(n)}(\{z,\bm{v}_j\})\; . 
+\end{equation}
+Using that the elementary symmetric polynomials satisfies the
+relations
 \begin{equation}
@@
 \end{equation}
-
-Let us also denote the functions
+we write
 \begin{equation}
   \label{eq:y-functions-alpha}
-  \mathcal{Y}_j(z)  \equiv  \mathcal{Y}(z; \{z,\bm{v}_j\})  = 
+  \mathcal{Y}(z; \{z,\bm{v}_j\})  = 
 \sum_{p=0}^{n} \alpha_p(z)
@@
 \end{equation}
-Observe that the defining property of these functions
-\(\mathcal{Y}_j(z)\) is the absence of the \(j\)-th Bethe root
-\(v_j\).
-Using that the elementary symmetric polynomials also satisfy \(\sigma_n^{(n-1)}(\bm{v}_j)=0\)
-and \(\sigma_{-1}^{(n)}(\bm{v}_j)= 0\), we can write
+The elementary symmetric polynomials also satisfy
+\(\sigma_n^{(n-1)}(\bm{v}_j)=0\) and \(\sigma_{-1}^{(n)}(\bm{v}_j)=
+0\), and it yields
 \begin{equation}
@@
   \mathcal{Y}_j(z)  = 
-  \sum_{p=0}^{n-1} 
-   \left(\alpha_p(z) + z \alpha_{p+1}(z) \right) \sigma_p^{(n-1)}(\bm{v}_j) \; .
-\end{equation}
-
-Putting all these facts together, we have the functions
-\begin{equation}
-  \Omega_{j}(z; \bm{v}) = \frac{c}{z - v_j} \mathcal{Y}_j(z) \; .
-\end{equation}
-It is also convenient to consider \(c=1\), consequently \(c_0=1\).
-
-\subsection{Alternant expression for the Slavnov products}
-
-The matrix \(\bm{\Omega}\) can be written as
+  \sum_{p=0}^{n-1} \beta_p(z) \sigma_p^{(n-1)}(\bm{v}_j) \; , \qquad 
+\beta_p(z) = \alpha_p(z) + z \alpha_{p+1}(z) \; .
+\end{equation}
+
+Putting all these facts together, we have
+\begin{equation}
+\begin{split}
+  \Omega_{j}(z; \bm{v}) & = \frac{\mathcal{Y}_j(z) }{z - v_j} \\ 
+& = \frac{1}{z - v_j} \sum_{p=0}^{n-1} \beta_p(z) \sigma_p^{(n-1)}(\bm{v}_j) \; .
+\end{split}
+\end{equation}
+The factor \((z - v_j)^{-1}\) introduces the dependence on the Bethe root \(v_j\).  
+Moreover, one can observe that
+\begin{equation}
+\Res_{z=v_k} \left( \Omega_j(z)\right) =  \delta_{jk}\mathcal{Y}_j(v_j)\; .
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Alternant determinant expression for the Slavnov products}
+
+Let us now write the matrix \(\bm{\Omega}\) defined
+in~(\ref{eq:omega-matrix-def}) as
 \begin{equation}
@@
   \begin{pmatrix}
-    \Omega_1(u_1) & \dots & \Omega_1(u_n) & \Omega_1(u_{n+1}) \\
-    \Omega_2(u_1) & \dots & \Omega_2(u_n) & \Omega_2(u_{n+1}) \\
-    \vdots & \vdots & \vdots & \vdots \\
-    \Omega_n(u_1) & \dots & \Omega_n(u_n) & \Omega_n(u_{n+1})\; .
-  \end{pmatrix}
-\end{equation}
-From this expression, we can also define a set of \(n\) square matrices
-\(\bm\Omega^{(\ell)}(\bm{u}_\ell; \bm{v})\),
-\(\ell = 1, \dots, n+1\), removing the \(\ell\)-th column of
-\(\bm{\Omega}\), that is
+    \Omega_1(u_1) & \dots & \Omega_1(u_\ell) & \dots  & \Omega_1(u_n) & \Omega_1(u_{n+1}) \\
+    \Omega_2(u_1) & \dots & \Omega_2(u_\ell) & \dots  & \Omega_2(u_n) & \Omega_2(u_{n+1}) \\
+          \vdots &       &   \vdots    &    &     \vdots       & \vdots   \\
+    \Omega_n(u_1) & \dots & \Omega_n(u_\ell)& \dots  & \Omega_n(u_n) & \Omega_n(u_{n+1})
+  \end{pmatrix}\; .
+\end{equation}
+From this expression, we can also define \(n+1\) square matrices
+\(\bm\Omega^{(\ell)}(\bm{u}_\ell) \equiv \bm\Omega^{(\ell)}(\bm{u}_\ell; \bm{v})\), for
+\(\ell = 1, \dots, n+1\), by deleting the \(\ell\)-th column of
+\(\bm{\Omega}\). That is
 \begin{equation}
@@
     \Omega_1(u_1) & \dots & \Omega_1(u_{\ell-1}) & \Omega_1(u_{\ell+1})&\dots & \Omega_1(u_{n+1}) \\
-    \vdots & \dots & \vdots & \vdots & \dots & \vdots \\
+    \vdots &  & \vdots & \vdots & & \vdots \\
     \Omega_n(u_1) & \dots & \Omega_n(u_{\ell-1}) & \Omega_n(u_{\ell+1})&\dots & \Omega_n(u_{n+1})
@@
 \end{equation}
-
-Finaly, we can write~(\ref{eq:slavnov-tau}) as 
-\begin{equation}
-\label{eq:slavnov-tau-functions}
-  \bm{\tau}_\ell(\bm{u}_\ell; \bm{v}) = \frac{\det [\Omega_j((\bm{u}_\ell)_k)]|_{j,k=1}^n }{\Delta(\bm{u}_\ell)} 
-\end{equation}
-where \((\bm{u}_\ell)_k \) is the \(k\)-th component of the vector
-\(\bm{u}_\ell\).  Therefore, for a fixed \(\ell\), we define the
-vector \( \bm{z} \equiv \bm{u}_\ell\).  Consequently,
-\begin{equation}
-\begin{split}
-\label{eq:slav-tau-function}
-  \bm{\tau}(\bm{z}, \bm{v})
-  & = \frac{1}{\Delta(\bm{z})} \det[\Omega_j(z_k) ]_{j,k=1}^n \\
-  & = \frac{1}{\Delta(\bm{z})} \det\left[\frac{\mathcal{Y}_j(z_k)}{z_k - v_j} \right]_{j,k=1}^n  \; .
-\end{split}
-\end{equation}
-All these tau functions have the form of an \emph{alternant
-determinant} devided by the Vandermonde determinant.
-
-It is well documented that the functions defined as
-in~(\ref{eq:slav-tau-function}) are tau functions of the
-KP-hierachy, see~\cite{Araujo:2021ghu} and references therein, in
-particular~\cite{Kharchev:1991cy}. Consequently, these functions are
-tau functions.
-
 Henceforth, we will only refer to the matrix
@@
 
+Finally, we can write~(\ref{eq:slavnov-tau}) as 
+\begin{equation}
+\label{eq:slavnov-tau-functions}
+  \bm{\tau}^{(\ell)}(\bm{u}_\ell; \bm{v}) = \frac{\det [\Omega_j((\bm{u}_\ell)_k)]|_{j,k=1}^n }{\Delta(\bm{u}_\ell)} \; ,
+\end{equation}
+where \((\bm{u}_\ell)_k \) is the \(k\)-th component of the vector
+\(\bm{u}_\ell\).  More explicitly, remember that \(\bm{u} = (u_1,
+\dots, u_{n+1})\) and that \(\bm{u}_\ell = \bm{u}_\ell\setminus
+\{u_\ell\} = (u_1, \dots, u_{\ell-1}, u_{\ell+ 1}, \dots, u_{n+1})\),
+we have
+\begin{equation}
+  (\bm{u}_\ell)_k =
+  \left\{ 
+  \begin{matrix}
+    u_k & \text{if} & k < \ell\\
+    u_{k+1} & \text{if} & k > \ell
+  \end{matrix}
+  \right. \; .
+\end{equation}
+It is convenient to write \(\bm{z}^{(\ell)} = (z^{(\ell)}_1,
+z^{(\ell)}_2, \dots, z^{(\ell)}_n) = \bm{u}_{\ell}\). Moreover, it is
+worth noting that the normalized Slavnov product
+\(\bm{\tau}^{(\ell)}\) is completely independent of the parameter
+\(u_\ell\). On the other hand, these functions are not independent from each
+other, since \(\bm{z}^{(\ell)} \cap \bm{z}^{(\ell')} = \bm{u} \setminus
+\{ u_\ell, u_{\ell'}\} \).
+
+Consequently, we write the normalized Slavnov products as 
+\begin{equation}
+\begin{split}
+\label{eq:slav-tau-function}
+  \bm{\tau}^{(\ell)}(\bm{z}^{(\ell)}, \bm{v})
+  & = \frac{1}{\Delta(\bm{z^{(\ell)}})} \det[\Omega_j(z^{(\ell)}_k) ]_{j,k=1}^n \\
+  & = \frac{1}{\Delta(\bm{z}^{(\ell)})} \det\left[\frac{\mathcal{Y}_j(z^{(\ell)}_k)}{z^{(\ell)}_k - v_j} \right]_{j,k=1}^n
+  \; \quad \ell = 1, \dots, n+1 \; .
+\end{split}
+\end{equation}
+This is the first result of out work.
+
+All the normalized Slavnov products~(\ref{eq:slav-tau-function}) take
+the form of \emph{alternant determinants} of the functions
+\(\{\Omega_j\}_{j=1}^n\) divided by Vandermonde determinants.  This
+result establishes that the normalized slavnov
+products~(\ref{eq:slav-tau-function}) are tau functions of the KP
+hierarchy. Indeed, it is well documented that, given a set of generic
+functions \(\{\phi_j\}_{j=1}^n\), expressions of the type
+\begin{equation}
+\tau(\bm{w}) =
+\frac{\det_{i,j} \phi_i(w_j)}{\Delta(\bm{w})}\; ,
+\end{equation}
+where \(\{w_j\}_{j=1}^n\) are complex parameters, satisfy the Hirota
+bilinear equation. Consequently, they are tau functions of the KP
+hierarchy.  This proposition has been extensively discussed in the
+literature, for example~\cite{Segal:1985aga, Kharchev:1991cy,
+  Araujo:2021ghu} and references therein.
+
+\todo{15/05}
+\begin{remark}
+  In~\cite{Segal:1985aga, Kharchev:1991cy, Alexandrov:2014cwa}, the
+  authors have explored a family of functions \(\{ \phi_i\}_{i=1}^n\)
+  that forms a basis vector because they parametrize points in a
+  Grassmannian space. These functions are also useful in the
+  definition of the Baker-Akhiezer function. The important aspect for
+  us is that the functions \(\Omega_j\) relevant for our discussion do
+  not belong to the class discussed in the references above.
+  Therefore, we need to explore their properties and the
+  Baker-Akhiezer functions relevant to our present discussion.
+\end{remark}
+
+\begin{remark}
+  Reduction of a multicomponent KP Hierarchy
+  It is interesting to observe that we have an array of tau functions ...
+\end{remark}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Tau functions expansion of the Slavnov product}
-
 We can immediately observe that the poles of the tau

### 2025-05-16 draft.tex
finish section 3 dot 1

@@
 \begin{equation}
+\label{eq:linear-system}
 \bm{M} \bm{\zeta} = 
@@
 
-\todo{15/05}
-\begin{remark}
 In~\cite{Segal:1985aga, Kharchev:1991cy, Alexandrov:2014cwa}, the
-  authors have explored a family of functions \(\{ \phi_i\}_{i=1}^n\)
-  that forms a basis vector because they parametrize points in a
-  Grassmannian space. These functions are also useful in the
-  definition of the Baker-Akhiezer function. The important aspect for
-  us is that the functions \(\Omega_j\) relevant for our discussion do
-  not belong to the class discussed in the references above.
-  Therefore, we need to explore their properties and the
-  Baker-Akhiezer functions relevant to our present discussion.
-\end{remark}
-
-\begin{remark}
-  Reduction of a multicomponent KP Hierarchy
-  It is interesting to observe that we have an array of tau functions ...
-\end{remark}
+authors explored a family of functions \(\{ \phi_i\}_{i=1}^n\) that
+parametrize points in a Grassmannian space. These functions also play
+an important role in the definition of the Baker-Akhiezer
+functions. However, the asymptotic behavior of the functions
+\(\Omega_j\), which are relevant to our discussion, indicates that
+they do not belong to the class considered in the references above.
+Therefore, we must investigate their properties and the corresponding
+Baker-Akhiezer functions specific to our discussion.  We begin this
+analysis below.
+
+Given that each function \(\bm{\tau}^{(\ell)}(\bm{z}^{(\ell)}, \bm{v})\), for
+\(\ell = 1, \dots, n+1\), is a distinct but related tau function, one
+can define a vector
+\begin{equation}
+  \bm{T}(\bm{Z}, \bm{v}) = 
+\begin{bmatrix}
+\bm{\tau}^{(1)}(\bm{z}^{(1)}, \bm{v}) \\ 
+\bm{\tau}^{(2)}(\bm{z}^{(2)}, \bm{v}) \\ 
+\vdots \\ 
+\bm{\tau}^{(n+1)}(\bm{z}^{(n+1)}, \bm{v})
+\end{bmatrix}
+\end{equation}
+where \(\bm{Z} = (\bm{z}^{(1)}, \bm{z}^{(2)}, \dots,
+\bm{z}^{(n+1)})\). This is a vector of tau functions of the KP
+hierarchy. This observation suggests that there is, in fact, an
+underlying multicomponent KP hierarchy in this context, and that the
+linear system~(\ref{eq:linear-system}), which we can write as
+\begin{equation}
+\left( \bm{L} - \bm{\Lambda} \right) \bm{T} = \bm{0},
+\end{equation}
+defines a reduction of this multicomponent KP hierarchy. This
+reduction ultimately describes constraints that relate the different
+sets of parameters \(\bm{z}^{(\ell)}\).  We have not explored this
+idea in this work, but we hope to return to this problem in future
+publications.
+\todo{16/05}
 

### 2025-05-20 draft.tex
finish homogeneous limit

@@
 \date{\today}
-\keywords{Integrability, Bethe states, Schur, Hall-Littlewood, Toda, KP}
+\keywords{Integrability, spin chains, bethe, slavnov, kp}
 \subjclass[2020]{82B20, 82B23}
@@
 publications.
-\todo{16/05}
 
@@
 \subsection{Tau functions expansion of the Slavnov product}
-We can immediately observe that the poles of the tau
-function~(\ref{eq:slav-tau-function}) are exactly the Bethe roots of
-the integrable model.  We now want to analyse this pole structure of
-\(\Delta(\bm{z})\tau(\bm{z}, \bm{v})\).  Let us consider that the
-Bethe roots are not degenerate, that is, if \(j \neq k\), then \(v_j
-\neq v_k\). In that case, the poles \(v_j\) are simple poles.
-
-Let us now consider a particular coefficient \(\bm{z}\), say \(z_l\), and
-make a Laplace expansion in the column \(l\), that is
+
+Let us now fix a component \(\ell\) and omit this index in
+equation~(\ref{eq:slav-tau-function}). We also assume that the Bethe
+roots are non-degenerate; that is, for \(j \neq k\), we necessarily
+have \(v_j \neq v_k\). In other words, each Bether root \(v_j\)
+corresponds to a simple poles of the Slavnov product.
+
+Fix a particular coefficient of \(\bm{z}\), say \(z_l\), and consider a Laplace
+expansion of~(\ref{eq:slav-tau-function}) along the \(l\)-th column. That is
 \begin{equation}
@@
 \end{equation}
-where \(\hat{\Omega}_{j,l} \) is the \((j, l)\) minor of
-\(\bm{\Omega}\).  Now, we can extract the residue of the tau function
-for \(z_l\) at the point \(v_j\), that is
-\begin{equation}
-  \Res_{(z_l, v_j)}(\Delta(\bm{z})\tau(\bm{z}, \bm{v})) = (-1)^{j+l} \mathcal{Y}_j(v_j) \det[\hat{\Omega}_{j, l}]
+where \(\det[\hat{\Omega}_{j,l}]\) denotes the \((j, l)\)-minor of
+\(\bm{\Omega}\). We can now extract the residue of the tau function
+with respect to \(z_l\) at the point \(v_j\); that is
+\begin{equation}
+  \Res_{z_l=v_j}(\Delta(\bm{z})\tau(\bm{z}, \bm{v})) = (-1)^{j+l} \mathcal{Y}_j(v_j) \det[\hat{\Omega}_{j, l}]\;. 
 \end{equation}
@@
 \begin{subequations}
-Let us now decompose the Vandermonde determinant as
+Additionally, decompose the Vandermonde determinant as
 \begin{equation}
@@
 
-When we define the \(n\) sets of functions
+By defining the \(n\) sets of functions
 \begin{equation}
@@
 \end{equation}
-so that we can simplify the minor
-expansion~(\ref{eq:minor-expansion-2}) even further; that is
-\begin{equation}
+we can further simplify the minor
+expansion~(\ref{eq:minor-expansion-2}); that is
+\begin{equation}
+  \label{eq:slavnov-tauexp}
 \begin{split}
@@
     \tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v}) = 
-\frac{1}{\Delta(\bm{z}_l)} \det[\hat{\bm{\Omega}}_{(j)}(\bm{z}_{(l)} ]\; .
-\end{equation}
-The curious aspect of this expression is that it easy to see that each term  
-\(\tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v})\) is a tau function itself, and that
-it acts as a basis for the Slavnov's product. 
-Additionally, these basis tau functions \(\tilde{\tau}_j(\bm{z}_l,
-\bm{v})\) are, by construction, completely independent of \(z_l\).
-
+\frac{1}{\Delta(\bm{z}_l)} \det[\hat{\bm{\Omega}}_{(j)}(\bm{z}_{(l)})]\; .
+\end{equation}
 Finally, we have
 \begin{equation}
-  \Res_{(z_l, v_j)}(\tau(\bm{z}, \bm{v}))
+  \Res_{z_l = v_j}(\tau(\bm{z}, \bm{v}))
   = \frac{(-1)^{j + l} \mathcal{Y}_j(v_j)}{\Xi_l(v_j, \bm{z}_l)}
-  \tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v})
-\end{equation}
-
-In order to avoid cluttering, let us order the parameters \(\bm{z}\) and
-consider these points close to the corresponding \(\bm{v}\), that is,
-we consider just the residues \(z_j \to v_j\), then
+  \tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v})\; .
+\end{equation}
+
+We can also organize the parameters \(\bm{z}\) and consider these
+points close to the corresponding Bethe roots \(\bm{v}\). Therefore 
 \begin{subequations}
 \begin{equation}
-  \Res_{(z_j, v_j)}(\tau(\bm{z}, \bm{v}))
+  \Res_{z_j = v_j}(\tau(\bm{z}, \bm{v}))
   = \frac{\mathcal{Y}_j(v_j)}{\Xi_j(v_j, \bm{z}_j)}
-  \tilde{\bm{\tau}}_j(\bm{z}_j, \bm{v})
+  \tilde{\bm{\tau}}_j(\bm{z}_j, \bm{v})\; ,
 \end{equation}
@@
   = \frac{\Xi_j(v_j, \bm{z}_j)}{\mathcal{Y}_j(v_j)}
-  \Res_{(z_j, v_j)}(\tau(\bm{z}, \bm{v}))
+  \Res_{z_j = v_j}(\tau(\bm{z}, \bm{v}))\; .
 \end{equation}
 \end{subequations}
-Evidently, one can repeat the same ideas and take \(z_k \in \bm{z}_j\)
-close to \(v_k \in \bm{v}_j\).
-
-Therefore, we have the interesting result that the rresidues of the
-tau function \(\tau(\bm{z}, \bm{v})\) for \(z_j\) approaching the
-Bethe root \(v_j\) is proportional to a tau function.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Homogeneous limit}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In the previous section we have discussed the limit where the
+
+Expression~(\ref{eq:slavnov-tauexp}) is one of the main results in
+this work.  It is easy to see that each term
+\(\tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v})\) is a tau function itself,
+and serves as a basis for the Slavnov's product. Additionally, these
+basis tau functions \(\tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v})\) are, by
+construction, completely independent of \(z_l\). This result
+essentially shows that, given a \(\mathcal{Y}\)-function (which is
+related to the eigenvalue of the transfer matrix), one can construct a
+basis of tau functions that span the Slavnov products in the
+corresponding integrable system. Moreover, this expansion ensures that
+the resulting Slavnov product is also a tau function of the KP
+hierarchy.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Homogeneous limit: Wronskian formula}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In the previous section, we discussed the limit in which the
 parameters \(\bm{z}\) approach the Bethe roots \(\bm{v}\).  We now
-want to consider the limit where \(\bm{z}\) tend to a single variable,
-say \(z_k\to z_1\), \(k=2,\dots, n\).
-
-\subsection{Wronskian formula}
-
-Let us first consider the case where \(z_2 \to z_1\). We consider a
-series expansion about \(z_1\), and the second column of~(\ref{eq:slav-tau-function}) becomes
+consider a different limit, where all variables in the set \(\bm{z}\)
+tend to a single variable -- that is, \(z_k\to z_1\) for \(k=2,\dots,
+n\).
+
+Let us first consider the case \(z_2 \to z_1\). We perform a series
+expansion around \(z_1\), in which the second column
+of~(\ref{eq:slav-tau-function}) becomes
 \begin{subequations}
@@
     \frac{\mathcal{Y}_n(z_3)}{z_3 - v_n} &  \dots & \frac{\mathcal{Y}_n(z_n)}{z_n - v_n}
-  \end{pmatrix}
-\end{equation}
-where we have written \(z_2 - z_1 = \delta \to 0\), and we denote by
-\(\mathcal{Y}^{(n)}(z)\) the \(n\)-th derivative of a
+  \end{pmatrix}\; ,
+\end{equation}
+where we have written \(z_2 - z_1 = \delta \to 0\). Moreover, let us
+denote by \(\mathcal{Y}^{(n)}(z)\) the \(n\)-th derivative of
 \(\mathcal{Y}(z)\) with respect its argument.
 
-Now one can immediatelly see that the second column is the first
-column plus terms multiplied by the factor \(\delta = z_2 -
-z_1\). Using elementary operations on the column, we find
+One can immediately see that the second column is equal to the first
+column plus terms proportional to the factor \(\delta = z_2 -
+z_1\)​. Using elementary column operations, we find
 \begin{equation}
@@
 \end{equation}
-We can now repeat the same ideas for \(z_3\to z_1=z_2\). We find that
-the third column is the sum of the first and second columns, and
-derivatives multiplied by the factor \(\delta^2\sim (z_3 - z_2)(z_3 -
-z_1)\). All in all, we have
+We can now repeat the same reasoning for \(z_3\to z_1=z_2\). We find
+that the third column becomes a linear combination of the first and
+second columns, along with terms involving derivatives multiplied by
+the factor \(\delta^2 = (z_3 - z_2)(z_3 - z_1)\). All in all, we have
 \begin{equation}
@@
 
-Repeating the same idea for all columns, we get that the
-multiplicative factor cancels out the Vandermonde determinant, and
-that the homogeneous limit gives
+By applying this procedure iteratively to each column, we find that
+the multiplicative factors cancel the Vandermonde determinant, and the
+homogeneous limit becomes
 \begin{equation}
@@
 \end{equation}
-
-Finally, let we write \(z_1 \equiv w\) and using elementary row operations we find
+Finally, we write \(z_1 \equiv w\) and using elementary row operations
+we find
 \begin{equation}
@@
 \end{subequations}
-The interesting aspect of this expression is that the poles of this
-function are exactly the Bethe roots, and they are easily built from
-the Algebraic Bethe ansatz. Additionally, the functions
+An interesting aspect of this expression is that its poles coincide
+precisely with the Bethe roots \(\bm{v}\). Moreover, the homogeneous
+limit can be readily constructed from the Algebraic Bethe Ansatz,
+since it depends only on the transfer matrix
+eigenvalues. Additionally, the functions
 \(\{\mathcal{Y}_j(w)\}_{j=1}^n\) are linearly independent if and only

### 2025-05-21 draft.tex
start ba function

@@
 tend to a single variable -- that is, \(z_k\to z_1\) for \(k=2,\dots,
-n\).
+n\). The analysis follows the ideas of~\cite{Izergin:1991rs}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Examples}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Let us now consider the cases \(n=2, 3\) (the case \(n=1\) is trivial)
-to gain some understanding of the problem.
-
-\subsection{n=2} In this case, we have \(\mathcal{Y}_j\) for \(j=1,2\) and two Bethe roots
-\(\bm{v} = (v_1, v_2)\). Moreover, we have the two sets \(\bm{v}_1 =
-\{v_2\}\) and \(\bm{v}_2 = \{v_1\}\). From (\ref{eq:y-functions}), we have
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Let us now consider the cases \(n = 2\) and \(n = 3\) to gain further
+insight into the problem.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Case n=2}
+In this case, we have \(\mathcal{Y}_j\) for \(j = 1, 2\) and two Bethe
+roots \(\bm{v} = (v_1, v_2)\). Moreover, we define the two sets
+\(\bm{v}_1 = \{v_2\}\) and \(\bm{v}_2 = \{v_1\}\). From
+equation~(\ref{eq:y-functions}), we have
 \begin{subequations}
@@
     \alpha_1(z)( \sigma_1^{(1)}(\bm{v}_j) + z \sigma_0^{(1)}(\bm{v}_j)) +
-    \alpha_2(z) z \sigma_1^{(1)}(\bm{v}_j) \; , 
-  \end{split}
-\end{equation}
-finally, the explicit formulas for the elementary symmetric polynomials are \(\sigma_0^{(1)}(x) =1\)
-and \(\sigma_1^{(1)}(x) = x\).
-
-Therefore
+    \alpha_2(z) z \sigma_1^{(1)}(\bm{v}_j) \; . 
+  \end{split}
+\end{equation}
+Furthermore, the explicit formulas for the elementary symmetric
+polynomials are \(\sigma_0^{(1)}(x) = 1\) and \(\sigma_1^{(1)}(x) =
+x\). Therefore
 \begin{equation}
@@
     \mathcal{Y}_1(z) & = \alpha_0(z) + z \alpha_1(z)  + v_2 \left( \alpha_1(z) + z \alpha_2(z) \right) \\ 
-    \mathcal{Y}_2(z) & = \alpha_0(z) + z \alpha_1(z)  + v_1 \left( \alpha_1(z) + z \alpha_2(z) \right) ; .
-  \end{split}
-\end{equation}
-Consequently, we find
+    \mathcal{Y}_2(z) & = \alpha_0(z) + z \alpha_1(z)  + v_1 \left( \alpha_1(z) + z \alpha_2(z) \right) \; .
+  \end{split}
+\end{equation}
+Consequently, the normalized Slavnov product becomes
 \begin{equation}
@@
   \frac{\mathcal{Y}_1(z_1)}{(z_1 - v_1)} \widetilde{\bm{\tau}}_1(z_2, v_1, v_2) - 
-  \frac{\mathcal{Y}_2(z_1)}{(z_1 - v_2)} \widetilde{\bm{\tau}}_2(z_2, v_1, v_2) \right)
+  \frac{\mathcal{Y}_2(z_1)}{(z_1 - v_2)} \widetilde{\bm{\tau}}_2(z_2, v_1, v_2) \right)\; ,
 \end{split}
@@
 \end{subequations}
-From this expression, it is easy to extract the residues of \(z_1\)
-about one of the Bethe roots.
-
-It is easy to see that the homogeneous limit, that is \(z_2 \to z_1\equiv
-w\) gives
+
+From this expression, it is easy to extract the residues of \(z_1\) at
+one of the Bethe roots. It is also straightforward to see that the
+homogeneous limit, that is, \(z_2 \to z_1 \equiv w\), yields
 \begin{equation}
   \bm{\tau}(w; v_1 , v_2) =
-  \frac{1}{(w- v_1)(w- v_2)}\mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2](w)\; , 
+  \frac{1}{(w- v_1)(w- v_2)}\mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2](w)\; . 
 \end{equation}
@@
 \mathcal{Y}_2\}\) are linearly independent as long as \(v_2 \neq
-v_1\), what is guaranteed by the hypothesis that the Bethe roots are
-different.
-
-\subsection{n=3} Now we have \(\mathcal{Y}_j\) for \(j=1,2,3\) and three Bethe roots
-\(\bm{v} = (v_1, v_2, v_3)\). Moreover, we have the sets \(\bm{v}_1 = (v_2, v_3)\), \(\bm{v}_2 = (v_1, v_3)\)
-and \(\bm{v}_3 = (v_1, v_2)\). Then, it is easy to see that
+v_1\), which is guaranteed by the assumption that the Bethe roots are
+distinct.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Case n=3}
+Now we have \(\mathcal{Y}_j\) for \(j=1,2,3\), and three Bethe roots
+\(\bm{v} = (v_1, v_2, v_3)\). Moreover, we define the sets \(\bm{v}_1
+= (v_2, v_3)\), \(\bm{v}_2 = (v_1, v_3)\), and \(\bm{v}_3 = (v_1,
+v_2)\). Then, it is easy to see that
 \begin{equation}
@@
 \end{equation}
-with the explicit expressions 
+with
 \begin{equation}
@@
 
-Then, we have
+Hence
 \begin{subequations}
@@
 \end{equation}
-We organize this expression as
+We reorganize this expression as follows:
 \begin{equation}
@@
 
-Finally, we conclude that that basis tau functions are
+Finally, we conclude that the basis tau functions are
 \begin{subequations}
@@
 
-With these expressions, we can consider the case where \(z_1, z_2 z_3
-\to w\). Consider first the case \(z_3 \to z_2 = w\), then  
-we know that 
+With these expressions, we can consider the homogeneous limit \(z_1,
+z_2, z_3 \to w\). Consider first the case \(z_3 \to z_2 = w\), then we
+know that
 \begin{equation}
@@
 \end{equation}
-and now, it is easy to see that if we also take the limit \(z_1\to w\), we have
+It is immediate to see that the basis tau functions correspond to
+Slavnov products for the case \(n=2\). We also take the limit \(z_1\to
+w\); then
 \begin{equation}
@@
 
-Of course we can keep the calculations for other cases, but now it is obvious that
-this explicit analysis become cumbersome very early. It also explains why we
-keep our analysis restricted to the Rational cases.
-
+Of course, we could continue the calculations for other cases, but it
+is now clear that this explicit analysis becomes cumbersome quite
+quickly. This also explains why we restrict our analysis to the
+rational cases.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This section deals with some properties of the Baker-Akhiezer
-functions associated to the tau functions we found above.  Many
-aspects of these functions deserve a thorough examination, but here we
-investigagte just the most immediate aspects.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This section addresses some properties of the Baker-Akhiezer functions
+associated with the tau functions derived above. While many aspects of
+these functions deserve thorough examination, here we focus on their
+most essential properties.
 
@@
 
-We now want to write the Slavnov products we defined above in terms of
+We now aim to express the Slavnov products defined above in terms of
 the following coordinates
@@
 \end{equation}
-the so called Miwa coordinates.
-
-We define
+the so-called Miwa coordinates. Let us also define the function
 \begin{equation}
@@
 \end{equation}
-where \(\lambda\) is a complex parameter. Therefore
+where \(\lambda\) is a complex parameter.
+
+Therefore
 \begin{equation}
@@
 \end{equation}
-It is easy to see that these functions have simple poles at \( \lambda
-= z_j^{-1}\).
-
-Let us now establish an important result,
-see ~\cite{Araujo:2021ghu} and references therein. 
+It is easy to see that these functions have simple poles at \( \lambda = z_j^{-1}\).
+
 \begin{proposition}
-The tau function~(\ref{eq:slav-tau-function}) admits the following integral
+It has been established that tau functions in the alternant
+form~(\ref{eq:slav-tau-function}) admits the following integral
 representation
@@
 \paragraph{\textbf{\emph{Proof}}}
+
+As far as we know, this result was first established
+in~\cite{ZinnJustin:2002cr, ZinnJustin:2002pk}; see
+also~\cite{Zinnjustin2009, Araujo:2021ghu} for further
+discussions. Here, we present a proof of this result for pedagogical
+reasons and to address some differences that arise due to our
+conventions.
+\todo{21/05}
+
 In terms of the \(z\)-coordinates, the tau functions becomes

### 2025-05-23 draft.tex
finish section on the ba function

@@
 \end{equation}
-Putting all these facts together, the coefficients \(L_{jk}\) are given by
+Consequently, the coefficients \(L_{jk}\) are given by
 \begin{equation}
@@
 \begin{proposition}
+\label{prop:integral-rep}
 It has been established that tau functions in the alternant
@@
 conventions.
-\todo{21/05}
-
-In terms of the \(z\)-coordinates, the tau functions becomes
+
+In terms of the \(z\)-coordinates, the integral~(\ref{eq:tau-function-miwa}) becomes
 \begin{equation}
@@
 \end{equation}
-Now, it is easy to see that \(w =0\) is not a pole.  All in all, the
-integration curve \(\gamma_k\) encloses points \(\{z_j\}_{j=1}^n\).
-
-Let us define the invertible matrix \(\bm{\mathcal{K}}^T\) by its components
-\begin{equation}
+Since \(n \geq j\), the point \(w = 0\) is not a pole of the
+integrand. All in all, the integration contour \(\gamma_k\) encloses
+the points \(\{z_j\}_{j=1}^n\).
+
+Let us define the matrix\footnote{
+The choice of the transposition is an aesthetic one. We want 
+to derive a result expressed as a matrix product with the components \(\Omega_{kl}\) on the left.}
+\(\bm{\mathcal{K}}^T\) by its components as follows:
+\begin{equation}
+\label{eq:k-matrix}
     \mathcal{K}_{kj} = 
-\oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{z}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k}\;. 
-\end{equation}
-Explicitly, we have 
+\oint_{\gamma_k} \frac{d w}{2\pi i} e^{\xi(\bm{z}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k}\; .
+\end{equation}
+We can now carry out the integration
 \begin{equation}
@@
     \frac{\mathcal{Y}_k(z_\ell)}{z_\ell - v_k}\\
-    & = \sum_{\ell = 1}^n  \Omega_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
+    & = \sum_{\ell = 1}^n  \Omega_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)\; ,
   \end{split}
@@
 
-It is easy to see that
+We can now see that the matrix \(\bm{\mathcal{K}}\) can be understood
+as the product of two other matrices. Consequently, we have
 \begin{equation}
@@
 \end{subequations}
-Putting all these facts together, we finally see that 
-\(\bm{\tau}(\bm{z}, \bm{v}) = \det\bm{\mathcal{K}}\), that
-is preciselly the expression~(\ref{eq:slav-tau-function}).\\
-\qed
-
-One of the advantages of this representation is
-that now it is easier to consider the limit of the infinite chain,
-\(n\to \infty\).
+Combining all these expressions, we finally see that
+\begin{equation}
+  \det \bm{\mathcal{K}} = \frac{\det \bm{\Omega}}{\Delta(\bm{z})}\; ,
+\end{equation}
+then \(\bm{\tau}(\bm{z}, \bm{v}) = \det\bm{\mathcal{K}}\), that is
+preciselly the expression~(\ref{eq:slav-tau-function}) for a fixed
+\(\ell\). \\ \qed
+
+\begin{lemma}
+\label{lemma:k-invert}
+The matrix \(\bm{\mathcal{K}}\) defined via~(\ref{eq:k-matrix}) is
+invertible. This follows immediately from the relation
+\(\bm{\tau}(\bm{z}, \bm{v}) = \det \bm{\mathcal{K}}\).
+\end{lemma}
+
+One advantage of the integral
+representation~(\ref{eq:tau-function-miwa}) is that it makes it easier
+to consider the limit of the infinite chain, \(n\to \infty\).
 
@@
 
-The Baker-Akhiezer (BA) funcion is defined in terms of the Japanese formula~\cite{Zabrodin2018}
-\begin{equation}
+The Baker-Akhiezer (BA) function is defined through the
+Japanese formula~\cite{Babelon:2003qtg, Harnad:2021tau, Zabrodin2018}.
+\begin{equation}
+\label{eq:ba-function}
   \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
-  \frac{\bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v})}{\bm{\tau}(\bm{t}, \bm{v})}
+  \frac{\bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v})}{\bm{\tau}(\bm{t}, \bm{v})}\; ,
 \end{equation}
@@
 \end{equation}
-
-Using the expression~(\ref{eq:tau-function-miwa}), we can write the
-Baker-Akhiezer function in terms of the \(z\)-coordinates.
-Let us first write
-\begin{equation}
-  t_p - \lambda^{-p}/p = \frac{1}{p} \sum_{j=1}^n z_j^ p - \lambda^{-p}/p \; , 
+We can write these components as
+\begin{equation}
+  t_p - \frac{\lambda^{-p}}{p} = \frac{1}{p} \sum_{j=1}^n z_j^ p - \frac{\lambda^{-p}}{p} \; , 
 \end{equation}
@@
       = \left( 1 - \frac{1}{\lambda w}\right)  \prod_{j=1}^n \frac{1}{1 -  z_j /w} \\
-    & = \frac{w^{n-1}}{\lambda } \left( \lambda w - 1 \right)  \prod_{j=1}^n \frac{1}{w -  z_j} \\
-  \end{split}
-\end{equation}
-
-Using these expressions, we can write 
+    & = \frac{w^{n-1}}{\lambda } \left( \lambda w - 1 \right)  \prod_{j=1}^n \frac{1}{w -  z_j} \; .
+  \end{split}
+\end{equation}
+
+Finally, we express the shifted tau functions
+\begin{subequations}
 \begin{equation}
@@
   \oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{- j -1} ( \lambda w - 1) \mathcal{Y}_k(w)}{\lambda(w - v_k)} 
-  \right]\; .
-\end{equation}
-that in terms of the \(z\)-coordinates becomes
-\begin{equation}
-\begin{split}
-  \bm{\tau}(\bm{t} - [\lambda^{-1}], \bm{v})
-  & = \det_{j,k}\left[\oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}  
-    \frac{( \lambda w - 1) w^{n-j-1}\mathcal{Y}_k(w)}{\lambda(w - v_k)} \right]\\
+  \right]
+\end{equation}
+in terms of the \(z\)-coordinates as
+\begin{equation}
+\begin{split}
+  \bm{\tau}(\bm{z}, \bm{v}; \lambda^{-1})
+  & = \det_{j,k}\left[\oint_{\gamma_k} \frac{dw}{2\pi i} 
+    \frac{( \lambda w - 1) w^{n-j-1}\mathcal{Y}_k(w)}{\lambda(w - v_k)} \prod_{s=1}^n \frac{1}{w - z_s} \right]\\
   & = \det_{j,k}\left[
-    \oint_{\gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}  
-    \frac{w^{n-j-1}\widehat{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}
-    \right]
-\end{split}
-\end{equation}
-where we have defined the function 
+    \oint_{\gamma_k} \frac{dw}{2\pi i}  
+    \frac{w^{n-j-1}\widehat{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)} \prod_{s=1}^n \frac{1}{w - z_s} 
+    \right]\; ,
+\end{split}
+\end{equation}
+\end{subequations}
+where we have defined the functions
 \begin{equation}
   \widehat{\mathcal{Y}}_k(w; \lambda)
-  = \frac{( \lambda w - 1)}{\lambda} \mathcal{Y}_k(w) \; ,
-\end{equation}
-From these expressions, it is easy to see that for \(j=n\) the point
-\(w = 0\) is a pole; and we must consider it in the integration curve \(\gamma_k\).
-
-It is convenient to define the components
-\begin{equation}
+  = \frac{( \lambda w - 1)}{\lambda} \mathcal{Y}_k(w) \; , \qquad k =1, \dots, n\;. 
+\end{equation}
+From these expressions, it is easy to see that for \(j = n\), the
+point \(w = 0\) is a pole, and we must include it in the integration
+contour \(\gamma_k\).
+
+Define the matrix \(\widetilde{\bm{\mathcal{K}}}^T\) by its components
+\begin{equation}
+\label{eq:k-tilde}
   \begin{split}
     \widetilde{\mathcal{K}}_{kj} = &
-    \oint_{\tilde \gamma_k} \frac{dw}{2\pi i} \prod_{s=1}^n \frac{1}{w - z_s}
-    \frac{w^{n-j-1}\widehat{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)}
+\oint_{\gamma_k} \frac{dw}{2\pi i} e^{\xi(\bm{t}, w^{-1})} \frac{w^{- j -1} ( \lambda w - 1) \mathcal{Y}_k(w)}{\lambda(w - v_k)}
+    \\
+    = & \oint_{\gamma_k} \frac{dw}{2\pi i}  
+    \frac{( \lambda w - 1) w^{n-j-1}\mathcal{Y}_k(w)}{\lambda(w - v_k)} \prod_{s=1}^n \frac{1}{w - z_s}  \\
+    = &
+    \oint_{\tilde \gamma_k} \frac{dw}{2\pi i}
+    \frac{w^{n-j-1}\widehat{\mathcal{Y}}_k(w; \lambda)}{(w - v_k)} \prod_{s=1}^n \frac{1}{w - z_s} 
     + \delta_{nj} F_k(\lambda) \\
-    & = \sum_{\ell = 1}^n  \widehat{\Omega}_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
+    = & \sum_{\ell = 1}^n  \widehat{\Omega}_{k \ell} \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
     + F_k(\lambda)\delta_{nj}  \\
@@
 \end{equation}
-where \(\tilde{\gamma}_k\) is a deformation contour that does not pick
-the point \(w=0\); and
-\begin{equation}
+where \(\tilde{\gamma}_k\) is a deformed contour that does not enclose
+the point \(w = 0\), and
+\begin{equation}
+\label{eq:omehat-comp}
   \widehat{\Omega}_{k\ell}
-  = \frac{1}{z_\ell} \frac{\widetilde{\mathcal{Y}}_k(\lambda, z_\ell)}{z_\ell - v_k}
+  = \frac{1}{z_\ell} \frac{\widehat{\mathcal{Y}}_k(z_\ell, \lambda)}{z_\ell - v_k}
   = \frac{(\lambda z_\ell -1)}{\lambda z_\ell} {\Omega}_{k\ell} 
@@
 \end{equation}
-
-In order to simplify our analysis, let us define one more matrix
-\(\widehat{\mathcal{K}}\) by its components
+Moreover, it is also convenient to define the matrix
+\(\widehat{\bm{\Omega}}\) formed by the components
+\(\widehat{\Omega}_{ij}\) and
+the vector \(\bm{F} = (F_1, \dots , F_n)\), 
+with the components defined above in~(\ref{eq:omehat-comp}).
+
+Additionally, let us define yet another matrix,
+\(\widehat{\bm{\mathcal{K}}}^T\), by
 \begin{equation}
@@
     \sum_{\ell = 1}^n  \widehat{\Omega}_{k \ell}
-    \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right)
-    \; .
-\end{equation}
-We conclude that \(\widetilde{\mathcal{K}}\) can be obtained from 
-\(\widehat{\mathcal{K}}\) by adding to each component of the \(n\)-th row
-the corresponding component of the vector \(\bm{F} = (F_1, \dots , F_n)\). 
-Let us write this operation as 
-\begin{equation}
-  \widetilde{\mathcal{K}} = \widehat{\mathcal{K}} + \bm{0}_{[ \bm{F} \to n-row]}\; . 
-\end{equation}
-Where we use the notation \(\mathcal{A}_{[ \bm{F} \to j-row]} \) to
-denote the replacement of the \(j-th\) row of the matrix with the
-vector \(\bm{F}\).  Above we have considered this operation with the
-zero matrix \(\bm{0}\).
-
-By the multilinearity of the determinant, we can write
-\begin{equation}
-  \det \widetilde{\mathcal{K}} = 
-    \det \widehat{\mathcal{K}} + 
-    \det \widehat{\mathcal{K}}_{[\bm{F} \to n-row]}\; .
-\end{equation}
-
-It is now easy to see that \(\det \widehat{\mathcal{K}}\) is
-proportional to the tau functions (Slavnov products), that is
-\begin{equation}
-    \det \widehat{\mathcal{K}}  = 
-    \det(\widehat{\Omega})
+    \left( \frac{z_\ell^{n-j}}{\prod_{s\neq \ell} (z_\ell - z_s)} \right) \; .
+\end{equation}
+
+We conclude that \(\widetilde{\bm{\mathcal{K}}}\) can be derived from
+\(\widehat{\bm{\mathcal{K}}}\) by adding, component-wise, the vector
+\(\bm{F} = (F_1, \dots , F_n)\) to the \(n\)-th row.  We write this
+operation as
+\begin{equation}
+  \widetilde{\bm{\mathcal{K}}} = \widehat{\bm{\mathcal{K}}} + \bm{0}_{[ \bm{F} \to n\text{-row}]}\; . 
+\end{equation}
+Here we use the notation \(\mathcal{\bm{A}}_{[ \bm{F} \to j\text{-row}]}\) 
+to denote the replacement of the \(j\)-th row of the matrix 
+\(\mathcal{\bm{A}}\) with the vector \(\bm{F}\). In the expression above, 
+we have considered this operation with the null matrix \(\bm{0}\).
+By the multilinearity of the determinant, we finally have
+\begin{equation}
+  \det \widetilde{\bm{\mathcal{K}}} = 
+    \det \widehat{\bm{\mathcal{K}}} + 
+    \det \widehat{\bm{\mathcal{K}}}_{[\bm{F} \to n\text{-row}]}\; .
+\end{equation}
+
+It is now easy to see that \(\det \widehat{\bm{\mathcal{K}}}\) is
+proportional to the Slavnov product, that is,
+\begin{equation}
+    \det \widehat{\bm{\mathcal{K}}}  = 
+    \det(\widehat{\bm{\Omega}})
     \det_{l,j}
     \left( \frac{z_l^{n-j}}{\prod_{s\neq l} (z_l - z_s)} \right)\\
-    = \frac{\det(\widehat{\Omega})}{\Delta(\bm{z})}
-\end{equation}
-where \(\widehat{\Omega}\) is the matrix formed by the components
-\(\widehat{\Omega}_{i,j}\). The above determinant is itself a tau function,
-but we can also write is as
+    = \frac{\det(\widehat{\bm{\Omega}})}{\Delta(\bm{z})}\;. 
+\end{equation}
+The above determinant is itself a tau function, but we can also write
+it as
 \begin{equation}
@@
 \end{equation}
-
-Finally, using the elementary symmetric polynomials \(\sigma_p^{(n)}\), we write
+Furthermore, we can simplify this expression using the elementary
+symmetric polynomials \(\sigma_p^{(n)}\); that is,
 \begin{equation}
@@
 
-Putting all these facts together, we write the Baker-Akhiezer function
-as 
+Collecting all these facts, we finally write the Baker-Akhiezer
+function as
 \begin{equation}
@@
     + \frac{1}{\bm{\tau}(\bm{z}, \bm{v})}
-    \det \widehat{\mathcal{K}}_{[\bm{F} \to n-row]}
+    \det \widehat{\bm{\mathcal{K}}}_{[\bm{F} \to n\text{-row}]}
   \right]\; .
 \end{equation}
-Next section we find a better expression for the Baker-Akhiezer
-function, but from this expression we can see that all the poles
-are at the point \(\lambda =0\).
-
-%%% Maybe I should calculate some examples
-%\subsection{Examples} Let us now consider the cases \(n=2, 3\).
-%We have calculated the tau functions for these objets. The
-%elementary symmetric polynomials are also known. Therefore,
-%the only detail we need to complete now is the calculation of
-%the matrix \(\widehat{\mathcal{K}}\). 
-%
-%\subsubsection{n=2} We
-%we have \(\mathcal{Y}_j\) for \(j=1,2\) and two Bethe roots
+From this expression we can see that all the poles are located at the
+point \(\lambda = 0\).
 
@@
 
-We now want to consider the above calculations in the Miwa
-coordinates.
-
-We define the matrix \(\check{\mathcal{K}}(\lambda)\) by its components
-\begin{equation}
-    \check{\mathcal{K}}_{jk} = -
-    \oint_{\gamma_k} \frac{dw}{2\pi i}
+In this section, we find a better expression for the Baker-Akhiezer
+function. Our main goal now is to reconsider the above calculations
+using the Miwa coordinates.
+
+Let us begin our exploration with the definitions~(\ref{eq:k-matrix})
+and~(\ref{eq:k-tilde}). Let us write
+\begin{equation}
+\label{eq:ktilde-split}
+  \widetilde{\mathcal{K}}_{kj} = \mathcal{K}_{kj}
+  - \frac{1}{\lambda} \oint_{\gamma_k} \frac{dw}{2\pi i}
     e^{\xi(\bm{t}, w^{- 1})} \frac{w^{-j -1 }\mathcal{Y}_k(w)}{w - v_k} \; .
 \end{equation}
-
-Therefore, we have that 
+Therefore, let us define one more matrix,
+\(\check{\bm{\mathcal{K}}}^T\), with components given by
+\begin{equation}
+  \check{\mathcal{K}}_{jk} =
+  - \oint_{\gamma_k} \frac{dw}{2\pi i}
+    e^{\xi(\bm{t}, w^{- 1})} \frac{w^{-j -1 }\mathcal{Y}_k(w)}{w - v_k} \; .
+\end{equation}
+Therefore,~(\ref{eq:ktilde-split}) becomes
 \begin{equation}
@@
   \mathcal{K}_{kj}  + \frac{1}{\lambda}
-  \check{\mathcal{K}}_{kj}
-  \ \Leftrightarrow \
-  \widetilde{\mathcal{K}} = 
-  \mathcal{K} + \frac{1}{\lambda}
-  \check{\mathcal{K}}\; , 
-\end{equation}
-and since \(\mathcal{K}\) is invertible, we get
-\begin{equation}
-  \widetilde{\mathcal{K}} = 
-  \mathcal{K}\left( \mathbb{1} + 
-  \frac{1}{\lambda}\mathcal{K}^{-1}\check{\mathcal{K}} \right)\; .
-\end{equation}
-
-Putting all these facts together, we find that the shifted
-tau-functions are
+  \check{\mathcal{K}}_{kj} \; , 
+\end{equation}
+that yields
+\begin{equation}
+  \widetilde{\bm{\mathcal{K}}} = 
+  \bm{\mathcal{K}} + \frac{1}{\lambda}
+  \check{\bm{\mathcal{K}}}\; .
+\end{equation}
+Moreover, by Lemma~\ref{lemma:k-invert}, \(\bm{\mathcal{K}}\) is
+invertible; therefore,
+\begin{equation}
+  \widetilde{\bm{\mathcal{K}}} = 
+  \bm{\mathcal{K}}\left( \mathbb{1} + 
+  \frac{1}{\lambda}\bm{\mathcal{K}}^{-1}\check{\bm{\mathcal{K}}} \right)\; .
+\end{equation}
+
+Combining these results, we find that the shifted tau-functions are
 \begin{equation}
@@
   \det \left( \mathbb{1} + \frac{1}{\lambda}
-  \mathcal{K}^{-1} \check{\mathcal{K}} \right)\; .
-\end{equation}
-
-We finally conclude that the Bakher-Akhiezer function can be written as
+  \bm{\mathcal{K}}^{-1} \check{\bm{\mathcal{K}}} \right)\; .
+\end{equation}
+We finally conclude that the Bakher-Akhiezer
+function~(\ref{eq:ba-function}) can be written as
 \begin{equation}
@@
   \det \left( \mathbb{1} + 
-    \frac{1}{\lambda} \mathcal{M}
+    \frac{1}{\lambda} \bm{\mathcal{M}}
   \right)\; , 
 \end{equation}
-where \(\mathcal{M} = \mathcal{K}^{-1} \check{\mathcal{K}}\) is a
-finite dimensional matrix. Let us now use the elementary expression
+where \(\bm{\mathcal{M}} =
+\bm{\mathcal{K}}^{-1}\check{\bm{\mathcal{K}}}\) is a
+finite-dimensional matrix depending on the coordinates
+\(\bm{t}\).
+
+Let us now use the elementary property
 \begin{subequations}
@@
   \begin{split}
-    \det \left( \mathbb{1} + \frac{1}{\lambda} \mathcal{M}\right)
-    & = \exp \left[ \Tr \log \left( \mathbb{1} + \frac{1}{\lambda} \mathcal{M} \right) \right]\\
+    \det \left( \mathbb{1} + \frac{1}{\lambda} \bm{\mathcal{M}}\right)
+    & = \exp \left[ \Tr \ln \left( \mathbb{1} + \frac{1}{\lambda} \bm{\mathcal{M}} \right) \right]
+    = \exp\left[ \sum_{l=1}^n \ln \left( 1 + \frac{\mu_l}{\lambda} \right)\right]\\
     & = \prod_{l=1}^n \left( 1 + \frac{\mu_l}{\lambda} \right) \; ,
@@
 where \(\bm{\mu} = \{\mu_l\}_{l=1}^n\) are the eigenvalues of the
-matrix \(\mathcal{M}\), and these obviously depend on the Bethe roots
-\(\bm{v}\) and parameters \(\bm{t}\). Therefore, we have
+matrix \(\bm{\mathcal{M}}\), and these obviously depend on the Bethe
+roots \(\bm{v}\) and parameters \(\bm{t}\).  Therefore, we have
 \begin{equation}
@@
   \left(1 + \sum_{k=1}^n \frac{\xi_k(\bm{t})}{\lambda^k} 
-  \right)\; . 
-\end{equation}
-where \(\xi_k(\bm{t}) = \sigma_k^{(n)}(\mu_1, \dots, \mu_n)\) and \(\mu_j = \mu_j(\bm{t}, \bm{v})\).
-
-We can also write 
-\begin{equation}
-  \begin{split}
-    \det \left( \mathbb{1} + \frac{1}{\lambda} \mathcal{M}\right)
+  \right)\; \qquad \xi_k(\bm{t}) = \sigma_k^{(n)}(\bm{\mu})\; .
+\end{equation}
+
+Alternatively, we can also express the determinant as
+\begin{equation}
+  \begin{split}
+    \det \left( \mathbb{1} + \frac{1}{\lambda} \bm{\mathcal{M}}\right)
     & = \exp\left[ \sum_{l=1}^n \ln \left( 1 + \frac{\mu_l}{\lambda} \right)\right]
@@
 \end{equation}
-where we define the Miwa coordinates \(\gamma_k = \frac{1}{k}\sum_{l=1}^n \mu_l^k \). Consequently
-\begin{equation}
-    \det \left( \mathbb{1} + \frac{1}{\lambda} \mathcal{M}\right)
-     = 1 + \sum_{k\geq 1}\frac{1}{\lambda^k} \sigma_k(\bm{\gamma})\; .
-\end{equation}
-Putting all these facts together, we can write the functions
-\(\xi_k(\bm{t})\) in terms of \(\bm{\gamma}\).  Observe that now the
-parameter \(n\) is hidden in the definition of the coordinates
-\(\gamma_k\).  One advantgage of this expression is that now we seem
-ot have a better setting to consider the thermodynamic limit \(n \to
-\infty\) with with \(n/L \to 0\). In fact, the
-expression~(\ref{eq:ba-fredholm}) suggests that in this limit, the
-Baker-Akhiezer function in the thermodynamics limit can be written as
-a Fredholm determinant. We are currently exploring this question and
+where we define the coordinates as 
+\begin{equation}
+\gamma_k = \frac{1}{k} \sum_{l=1}^n \mu_l^k\; .
+\end{equation}
+
+Then, we write the Baker-Akhiezer as 
+\begin{equation}
+  \psi(\bm{t},\bm{v}; \lambda) = e^{\xi(\bm{t}, \lambda)}
+  \left(1 + \sum_{k\geq 1} \frac{\sigma_k(\bm{\gamma})}{\lambda^k} 
+  \right)\; .
+\end{equation}
+Notice that this second expression does not explicitly depend on the
+size \(n\) of the Slavnov product. Consequently, the functions
+\(\xi_k(\bm{t})\) can be expressed in terms of the coordinates
+\(\bm{\gamma}\), where the parameter \(n\) is now implicitly contained
+in their definition.
+
+An advantage of this formulation is that it provides a more suitable
+framework to consider the thermodynamic limit \(n \to \infty\) with
+\(n/L \to 0\). In fact, expression~(\ref{eq:ba-fredholm}) suggests
+that in this limit the Baker-Akhiezer function can be represented as a
+Fredholm determinant. We are currently investigating this question and
 hope to report new results soon.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2025-05-23 draft.tex
finish paper

@@
  Connections between classical and quantum integrable systems are
-analyzed from the viewpoint of the Slavnov products of Bethe
-states. It is well known that, modulo model-dependent aspects, the
-functional structure of the Slavnov products takes the form of
-determinants. Using new results on the general structure of rational
-and trigonometric models, we establish that, as long as the model
-satisfies certain conditions, its Slavnov product is a tau function of
-the KP hierarchy, thus generalizing some known results. We also show
-that the Slavnov products can be expanded in terms of other tau
-functions, and we prove that their homogeneous limit can be calculated
-as a Wronskian of functions related to the eigenvalues of the transfer
-matrices. Finally, we calculate the Baker–Akhiezer functions
-associated with these Slavnov products, and show that, modulo a
-multiplicative universal term, the Baker–Akhiezer functions have a
-closed determinantal formula.
+ analyzed from the viewpoint of Slavnov products of Bethe states. It
+ is well known that, modulo model dependent aspects, the functional
+ structure of Slavnov products generally takes the form of
+ determinants. Building on recent results on the structure of rational
+ and trigonometric models, we show that, provided certain conditions
+ are satisfied, the Slavnov product of a given model can be
+ interpreted as a tau function of the KP hierarchy, thus extending
+ known results in a more general setting. Moreover, we show that
+ Slavnov products can be expanded in terms of other tau functions. We
+ also prove that their homogeneous limit can be systematically
+ expressed as a Wronskian of functions related to the eigenvalues of
+ the transfer matrices.  Finally, we compute the Baker–Akhiezer
+ functions associated with these Slavnov products and show that, apart
+ from a universal multiplicative factor, they admit a closed
+ determinantal representation.
 \end{abstract}
@@
 
-\setcounter{tocdepth}{2}
+\setcounter{tocdepth}{1}
 \tableofcontents
@@
 on the boundary conditions. Nevertheless, the general
-\textbf{functional structure} of Slavnov products across radically
+functional structure of Slavnov products across radically
 different models is basically the same. More specifically, modulo some
@@
 
-In Section 2, we review the main aspects of the
-work~\cite{Belliard:2019bfz}. This section also fixes some of the
-notation we use in the remainder of this work and in future
-investigations. Section 3 presents two new results. First, we rewrite
+Let us now provide a brief overview of the content and structure of
+our work. In Section 2, we offer a review of the main findings
+presented in the work of Belliard and
+Slavnov~\cite{Belliard:2019bfz}. In addition, we use this section to
+carefully establish and clarify the notation that will be employed
+throughout the remainder of this paper, as well as in related future
+investigations.
+
+Section 3 presents two new results and a conjecture. First, we rewrite
 relevant formulas established in~\cite{Belliard:2019bfz} and prove
@@
 formula and certain results that have previously appeared in matrix
-theory investigations.
-
-These tau functions are written in terms of two sets of
-parameters. The first set is given by arbitrary complex numbers, and
-the second set is given by the Bethe roots of the spin chain.  In
-Section 3, we also find a basis for the Slavnov products, and this
-basis is itself formed by tau functions. The results of Section 3
-allow us to investigate the case where the complex parameters are
-close to the Bethe roots.
+theory investigations.  These tau functions are written in terms of
+two sets of parameters. The first set consists of arbitrary complex
+numbers, and the second set consists of the Bethe roots of the spin
+chain. In Section 3, we also find a basis for the Slavnov products,
+and this basis is itself formed by tau functions. The results of
+Section 3 allow us to investigate the case where the complex
+parameters are close to the Bethe roots.
+
+In this section, we also conjecture (and only present some general
+evidence) that these tau functions indicate that we are, in fact,
+dealing with a multicomponent KP hierarchy, and that the linear
+equations discussed by Belliard and Slavnov~\cite{Belliard:2019bfz}
+describe a reduction of this larger integrable hierarchy.
 
@@
 \bm{z}^{(n+1)})\). This is a vector of tau functions of the KP
-hierarchy. This observation suggests that there is, in fact, an
+hierarchy.
+
+\begin{conjecture}
+This observation suggests that there is, in fact, an
 underlying multicomponent KP hierarchy in this context, and that the
@@
 publications.
+\end{conjecture}
 
@@
 
-In this paper we have discussed some properties of the Slavnov
-products and their relation with the tau functions of the KP
-hierarchy.
-
-An important initial observation is that the general form of this tau
-function is written in terms of some alternant matrix, and this form
-is known since (cite papers on the matrix models and so on). But the
-functions associated to the current paper is drastically different
-from those papers, and do not expand a point in the
-Grassmannian. Therefore, it is necessary to better understand some of
-these properties. In this paper we start exploring these results.
-
-....
-
-We have also started our exploration of the Baker-Akhiezer function since it seems to
-be the relevant object of our investigation.
-
-Some future interesting directions. We might want to calculate the
-solutions of the KP equation to see what they really mean. Perhaps
-consider analitic and numerical calculations, since the calculation of
-the determinants become complicated even for small values of \(n\).
-
-More interestingly, one may try to consider the thermodynamic limit of
-the Slavnov product and explore what it means from the viewpoint of
-the Baker-Akhiezer function.  See the Limit \(L \to \infty\) and \(N
-\to \infty\) but sufficiently slower than \(L\).  I think that the
-matrix \(\mathcal{M}\) is a trace class operator and we write the BA
-function as a Fredholm determinant.
-
-I think that this BA function will be similar to the soliton-like
-solution discussed in section 3.6.2 (page 41) of~\cite{Zabrodin2018}.
-My functions seem to have a pole of order \(N\) at infinity. And \(N\)
-zeros at the Bethe roots.
-
-Finally, we can explore the elliptic case and see if one can see if
-there exists any similar relation on the elliptic case.  Elliptic case
-- see slavnov, zabrodin's paper
-
-\subsubsection*{Acknowledgments}
-I would like to thank...
+In this work, we have discussed several properties of the Slavnov
+products arising in quantum integrable models and their deep
+connection with the tau functions of the KP hierarchy. We can
+summarize our main findings as follows. Our initial result
+demonstrates that the general structure of these tau functions can be
+expressed in terms of an alternant matrix. This general formulation
+firmly establishes the identification of the Slavnov product as a tau
+function within the framework of the KP classical integrable hierarchy.
+
+We have also proved that these Slavnov products admit a basis
+expansion in terms of other tau functions, thereby establishing that
+we are dealing with a particularly distinguished object within this
+framework. Moreover, we have discussed a conjecture suggesting the
+existence of a multicomponent KP hierarchy underlying all of our
+results.
+
+The behaviour of these functions near the Bethe roots of the quantum
+integrable systems, as well as the homogeneous limit of the Slavnov
+product, has also been discussed. Finally, we conclude our work with a
+brief analysis of the Baker-Akhiezer function. The most important
+result for us is that we have shown that the Baker-Akhiezer function,
+modulo a universal multiplicative factor, also admits a determinantal
+form.
+
+Evidently, there are many results that can be extended in this work,
+and several aspects that deserve further investigation. Let us list
+some of these problems, ranging from relatively straightforward
+applications to more substantial challenges.
+
+A simple problem to be discussed is the physical meaning of the
+solutions of the KP equation that can be constructed using the tau
+functions explored in this work. Perhaps one might consider both
+analytical and numerical approaches, since the calculation of the
+determinants becomes complicated even for relatively small values of
+\(n\).
+
+Another important aspect of this work is to achieve a better
+understanding of the Baker-Akhiezer functions associated with the
+Slavnov products. Here, we have only scratched the surface of these
+objects, and a full description of their properties is still
+lacking. We are currently investigating the thermodynamic limit of
+this system. In particular, we are studying the Slavnov product and
+its interpretation from the viewpoint of the Baker-Akhiezer
+function. For example, how to properly describe the limit \(L \to
+\infty\) and \(N \to \infty\), with \(N\) growing sufficiently
+slower than \(L\). I believe that the matrix \(\mathcal{M}\) is a
+trace-class operator, allowing us to express the Baker-Akhiezer
+function as a Fredholm determinant. We hope to report new results
+on this line of investigation soon.
+
+Finally, there is a more challenging problem to be addressed: the
+description of the elliptic case. While some determinantal formulas
+are known for the partially on-shell scalar product of Bethe states,
+it is not yet clear whether these objects are also related to tau
+functions of integrable hierarchies.  This characterization is another
+problem we are currently investigating, and we hope to have some
+results to report in the future.
+
+%\subsubsection*{Acknowledgments}
+%I would like to thank the Fluminense Federal University for
 

### 2025-05-26 draft.tex
finish first version of the paper

@@
 %% Extra packages 
-\usepackage{amsaddr}                % Affiliation in the first page
 \usepackage{slashed}                % Feynman slash notation
@@
 
-\title[Slavnov products, KP and BA functions]{
-  More on the Slavnov products of spin chains,
-  KP hierarchy tau and Baker-Akhiezer functions 
-}
+\title[Slavnov products, KP and BA functions]{More on Slavnov Products of Spin Chains and KP Hierarchy Tau Functions}
 
@@
 
-\address{\noindent 
-Institute of Exact Sciences, Department of Physics\\
-Fluminense Federal University\\
-Rua Des. Ellis Hermydio Figueira, 783, Aterrado\\
-27213-145 Volta Redonda, RJ, Brazil
+\address{
+Universidade Federal Fluminense, 
+Instituto de Ciências Exatas, Departamento de Física
+Volta Redonda, RJ, Brazil
 }
@@
 \date{\today}
-\keywords{Integrability, spin chains, bethe, slavnov, kp}
-\subjclass[2020]{82B20, 82B23}
+\keywords{Integrability, field theories, lattice models, correlation functions, bethe ansatz}
+\subjclass[2020]{81T40, 81U15, 82B20, 82B21, 82B23}
+%81T40 : Two-dimensional field theories, conformal field theories, etc. in quantum mechanics
+%81U15 : Exactly and quasi-solvable systems arising in quantum theory
+%82B20 : Lattice systems (Ising, dimer, Potts, etc.) and systems on graphs arising in equilibrium statistical mechanics
+%82B21 : Continuum models (systems of particles, etc.) arising in equilibrium statistical mechanics
+%82B23 : Exactly solvable models; Bethe ansatz
 
@@
 One can immediately see that the second column is equal to the first
-column plus terms proportional to the factor \(\delta = z_2 -
-z_1\)​. Using elementary column operations, we find
+column plus terms proportional to the factor
+\(\delta = z_2 - z_1\). Using elementary column operations, we find
 \begin{equation}

### 2025-05-27 draft.tex
remove today in date field -- new arxiv rules
arxiv v1

@@
 \input{definitions.tex}
-
-\bibliography{/home/thiago/Sync/wiki/database/bib-database.bib}
 
@@
 \begin{abstract}
- Connections between classical and quantum integrable systems are
- analyzed from the viewpoint of Slavnov products of Bethe states. It
- is well known that, modulo model dependent aspects, the functional
- structure of Slavnov products generally takes the form of
- determinants. Building on recent results on the structure of rational
- and trigonometric models, we show that, provided certain conditions
- are satisfied, the Slavnov product of a given model can be
- interpreted as a tau function of the KP hierarchy, thus extending
- known results in a more general setting. Moreover, we show that
- Slavnov products can be expanded in terms of other tau functions. We
- also prove that their homogeneous limit can be systematically
- expressed as a Wronskian of functions related to the eigenvalues of
- the transfer matrices.  Finally, we compute the Baker–Akhiezer
- functions associated with these Slavnov products and show that, apart
- from a universal multiplicative factor, they admit a closed
- determinantal representation.
+ Connections between classical and quantum integrable systems are analyzed from the viewpoint of Slavnov products of Bethe states.
+It is well known that, modulo model dependent aspects, the functional structure of Slavnov products generally takes the form of determinants.
+Building on recent results on the structure of rational and trigonometric models, we show that, provided certain conditions are satisfied, the Slavnov product of a given model can be interpreted as a tau function of the KP hierarchy, thus extending known results in a more general setting.
+Moreover, we show that Slavnov products can be expanded in terms of other tau functions.
+We also prove that their homogeneous limit can be systematically expressed as a Wronskian of functions related to the eigenvalues of the transfer matrices.
+Finally, we compute the Baker-Akhiezer functions associated with these Slavnov products and show that, apart from a universal multiplicative factor, they admit a closed determinantal representation.
 \end{abstract}
 
-\date{\today}
 \keywords{Integrability, field theories, lattice models, correlation functions, bethe ansatz}
@@
 
-%\subsubsection*{Acknowledgments}
-%I would like to thank the Fluminense Federal University for
-
-\printbibliography
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection*{Acknowledgments}
+
+I would like to express my sincere gratitude to the Department of
+Physics at Fluminense Federal University for providing an excellent
+research environment and for their support of this work.
+
+\bibliographystyle{utphys}
+\bibliography{bib-database.bib}
 
